### 2016-12-18 paper.tex
Copied russian text

\input{preamble.tex}
\input{macros/macros.tex}

\begin{document}

Latex math notes demo.

ITMO University.

\[
\bra{\vb{\psi}} \ket{\eps}
\]

\input{bundle.tex}
\end{document}

### 2016-12-18 preamble.tex
Copied russian text

\documentclass[12pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage[russian, english]{babel}

\usepackage{comment}

\usepackage{enumerate}
\usepackage{cite}
\usepackage{mathrsfs}
\usepackage{fullpage}
\usepackage{hyperref} % \url{url} \href{url}{displayed text}
\usepackage{tabularx}
\usepackage{indentfirst}
\usepackage{bm}
\usepackage{braket}

\usepackage{csquotes}
\MakeOuterQuote{"}
\usepackage[pdftex]{graphicx}
\graphicspath{{pic/}}
\usepackage{tikz}
\usepackage{xcolor} % \textcolor
\usepackage{mathtools} % xmapsto, \Vector
\usepackage{comment}
\usepackage{soul} % text striking
\usepackage{amsmath,amsfonts,amssymb,amsthm,amscd,amsxtra}
\usepackage{physics}
\usepackage[sharp]{easylist}
\usepackage[colorinlistoftodos,prependcaption,disable]{todonotes} % TODO: move to preamble!!
\presetkeys%
    {todonotes}%
    {inline,backgroundcolor=red}{}
\newcommand{\mtodo}[1]{\todo[linecolor=green!70!white, backgroundcolor=blue!20!white, bordercolor=red]{#1}}

### 2016-12-18 bundle.tex
Translated and simplified parts of paper

\subsection{The model}
% TODO http://tex.stackexchange.com/a/155317/5966 ?
\begin{figure}
\centering
\begin{tikzpicture}[scale=1.1] % TODO SCALE!!!
\input{pic/resonator_bundle.tex}
\end{tikzpicture}
\caption{Квантовый граф $\Gamma$, состоящий из полубесконечных ребер $\Omega_L, \Omega_R$ и рассеивателя $\Omega$, представляющего из себя $W$ идентичных ребер длины 1. В вершинах $V_a$, $V_b$ находятся $\delta$-образные потенциальные ямы глубины $a$ и $b$ соответственно.}\label{fig:res_bundle}
\end{figure}

Let's invastigate the model on \autoref{fig:res_bundle}. Schrodinger's operator is defined on edges of the graph as  $-\dv[2]{\psi}{x}$. At the vertices $V_a$ and $V_b$ we require the wavefunction and its derivatives to be continuous:

\begin{equation}\label{eq:bundle_system}
\begin{aligned}
   \forall i: \psi_i(0) &= \psi_L(0)
\\ \forall i: \psi_i(1) &= \psi_R(0)
\\ \psi'_L(0) - \sum\limits_{i = 1}^W \psi'_i(0) &= 0
\\ -\psi'_R(0) + \sum\limits_{i = 1}^W \psi'_i(1) &= 0
\end{aligned}
\end{equation}

\subsection{Calculation of $S$ matrix}
After solving \ref{eq:bundle_system} в сочетании с \ref{eq:wlwl}, we get:
\begin{equation*}
\det S(k) = \frac{2 i \, W \cos\left(k\right) - {\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}
\end{equation*}

\begin{equation}\label{eq:bundle_s}
s(k) = \abs{\det S(k)} = \abs{\frac{2 i \, W \cos\left(k\right) - {\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}}
\end{equation}

\mtodo{график S-матрицы?}

TODO: define contour

Let's fix $r$, and further, for the sake of readability, let's define $C = C(r)$ and $R = R(r)$. For each $r$, we estimate the integral and show that the sequence of estimates converges to zero.

Let's use Cauchy–Schwarz's inequality:
\[
\big| \langle u,v \rangle \big| \leq \left\|u\right\| \left\|v\right\|
\]
, to be precise, it's $\mcL^2[a, b]$ version:
\[
\abs{
\int\limits_{t=a}^{b} f(t) g^*(t) dt
}
\le
\sqrt{\int\limits_{t=a}^b \abs{f(t)}^2 dt }
\sqrt{\int\limits_{t=a}^b \abs{g(t)}^2 dt }
\]
% 
To use inequality, we are going to represent the integrand in (\ref{eq:critp}) as $f(t) g^*(t)$ as follows:
\begin{equation}\label{eq:split}
\begin{aligned}
a      &= 0 \\
b      &= 2 \pi \\
f(t)   &= \ln s(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
g^*(t) &= \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
\end{aligned}
\end{equation}
Next, we will show that $\norm{g}$ (that is, $\sqrt{\int \abs{g(t)}^2}$) is bounded by a constant which does not depend on $r$, and $\norm{f}$ goes to $0$ as $r$ goes to $1$, hence (\ref{eq:critp}) converges.

\subsubsection{Estimate of $\norm{g}$}

First, we evaluate the integrand:
\begin{align*}
\abs{g(t)}^2 = \abs{g^*(t)}^2
&=   \frac{\sqrt{R}^2}{\abs{R \cos t + \iu R \sin t + \iu C + i}^2} \\
&=   \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} \\
&= \frac{R}{R^2 \cos^2 t + R^2 \sin^2 t + (C + 1)^2  + 2 R (C + 1) \sin t} \\
&=   \frac{1}{R + \frac{(C + 1)^2}{R} + 2 (C + 1) \sin t} \\ 
\end{align*}

We have to integrate this function on interval $[0, 2 \pi]$. Integral of such type is well-known: (TODO REFERENCE)
\[
\int\limits_{0}^{2 \pi} \frac{dx}{a + b \sin x} = \frac{2 \pi}{\sqrt{a^2 - b^2}}
\]
, when $a > b$. In our case, $a = R + \frac{(C + 1)^2}{R}$, $b = 2 (C + 1)$).

First, we check that $a > b$:
\begin{align*}
   R + \frac{(C + 1)^2}{R} - 2 (C + 1)
   &= \frac{R^2 + C^2 + 2C + 1 - 2 RC - 2 R}{R}
\\ &= \frac{(C - R)^2 + 2(C - R) + 1}{R}
\\ &= \frac{(C - R + 1)^2 }{R}
\\ &> 0 && \text{,strictly greater since $C > R$} 
\end{align*}

Next, we compute en estimate for $\sqrt{a^2 - b^2}$:
\begin{align*}
a^2 - b^2
& =  (R + \frac{(C + 1)^2}{R})^2 - (2 (C + 1))^2\\
& =  R^2 + \frac{(C+1)^4}{R^2} + 2 (C+1)^2 - 4 (C + 1)^2 \\
& =  \left( \frac{(C + 1)^2}{R} - R \right)^2 \\
& =  \left( \frac{(C + 1)^2 - R^2}{R}\right)^2 \\
& =  \left( \frac{(C + 1 - R) (C + 1 + R)}{R}\right)^2 && \text{,since $C > R > 0$} \\
&\ge \left( \frac{(1) (R + R)}{R}\right)^2  \\
&\ge 4
\end{align*}

Finally, since $\frac{2 \pi}{\sqrt{a^2 - b^2}} \le \frac{2 \pi}{2} = \pi$, and we just proved that $\norm{g}$ is bounded by a constant.

\subsubsection{Оценка $\int \abs{f(t)}^2$}
Функция $s(k)$ (\ref{eq:bundle_s}) слишком сложна для прямого аналитического доказательства сходимости. Однако, так как $s(k)$ — модуль определителя $S$-матрицы, в верхней комплексной полуплоскости $0 \le s(k) \le 1$. Это означает, что $s(k)$ может быть заменена на некую оценку снизу $l(k)$, такую что $0 \le l(k) \le s(k)$. После этого, если будет доказана сходимость к нулю для этой нижней оценки, то так как $s(k) \le 1$, $\ln l(k) \le \ln s(k) \le 0$, мы будем иметь $\ln^2 s(k) \le \ln^2 l(k)$, и, следовательно, так как подынтегральное выражение неотрицательно, сходимость искомого интеграла. Мы часто будем опираться на этот факт и проводить подобные замены под знаком логарифма, заменяя сложные функции на кусочно-линейные, и используя известные оценки для логарифма чтобы оценить исходный интеграл.

\subsubsection{Упрощение функции $s(k)$}
Сначала мы дадим простую оценку для $s(k)$ по всей верней комплексной полуплоскости и сделаем ее независимой от вещественной части аргумента.

Легко видеть, что $s(k)$ периодична относительно вещественной части аргумента при неизменной комплексной части.
% Since $\sin k$ and $\cos k$ are periodic w.r.t the real axis, with the period of $2 \pi$, 
\mtodo{is this step really necessary?}

У функции $s(k)$ есть счетное число нулей, и для всех $\Im k = \atanh \frac{2 W}{W^2 + 1}$. Для краткости, дадим обозначения:

\begin{equation*}
\begin{aligned}
   V &= \frac{2 W}{W^2 + 1}
\\ Z &= \atanh V
\end{aligned}
\end{equation*}

Далее, заметим что для любого $x$, $s(x + \iu y) \le s(\iu y)$. \mtodo{How to prove? We could probably take a look at numerator and denominator in separate?} После всех вышеупомянутых замечаний, для $s(x + \iu y)$ можно дать довольно простую нижнюю оценку:
\begin{align*}
l(x + \iu y)
   &= \abs{\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}}
\\ &= \abs{\frac{\tanh y - V}{\tanh y + V}} && \text{(так как $\cosh y \ge 1$)}
\end{align*}

Легко понять, что у функции $l(k)$ будут нули вдоль линии $\Im k = Z$, что значит, что вдоль этой линии у функции $\ln l(k)$ будет несчетное множество особенностей. Интуитивно, это не должно испортить сходимость, так как контур интегрирования все равно мог пересечь сингулярность функции $\ln s(k)$. Действительно, далее мы покажем, что даже такое загрубление функции позволяет доказать сходимость. Далее, для краткости записи, будем опускать вещественную часть аргумента и обозначим $l(y) = l(x + \iu y)$, где $x$ может быть любым, так как $l$ от него все равно не зависит.
\mtodo{Plot?}

% Так как $\tanh y$ неотрицательна и растет при $y \ge 0$, мы можем избавиться от знака модуля:

% \todo{make the formula bigger}
% \todo{get rid of it??}
% \[
% l(x + \iu y)
%  = \begin{cases}
%  \frac{V - \tanh y}{\tanh y + V}, & 0 \le y \le Z \\
%  \frac{\tanh y - V}{\tanh y + V}, & y > Z 
%  \end{cases}
% \]

После построения нижней оценки можно упростить интеграл, который мы исследуем:
\begin{align*}
       \int\limits_{t=0}^{2 \pi} \abs{f(t)}^2 dt
   = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R \eexp{\iu t} + \iu C) \frac{R}{\norm{R \eexp{\iu t} + \iu C + i}^2} dt
\\ = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R \sin t + C) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dt
\end{align*}
% TODO f зависит только от Im k

Во-первых, заметим, что:

\begin{equation*}
\begin{aligned}
   \sin(-\pi/2 + t)   &= \sin(-\pi/2 - t) = - \cos t
\\ \cos^2(-\pi/2 + t) &= \cos^2(-\pi/2 = t) = \sin^2 t
\end{aligned}
\end{equation*}
, то есть подынтегральное выражение симметрично относительно оси $y$, и, следовательно, достаточно доказать сходимость интеграла на отрезке $-\pi/2 \le t \le \pi/2$.

Далее, заменим переменную интегрирования:
\begin{equation*}
\begin{aligned}
   y         &= R \sin t + C
\\ t         &= \asin \frac{y - C}{R}
\\ dt        &= \frac{1}{\sqrt{R^2 - (C - y)^2}} dy
\\ \cos t    &= \frac{\sqrt{R^2 - (C - y)^2}}{R}
\\ y(-\pi/2) &= C - R 
\\ y(\pi/2)  &= C + R 
\end{aligned}
\end{equation*}
, что после подстановки дает:
\begin{equation}\label{eq:int_f}
\resizebox{0.9\hsize}{!}{$
\begin{aligned}
    & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dy \\
=   & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 - (C - y)^2 + (y + 1)^2} \frac{1}{\sqrt{R^2 - (C - y)^2}} dy\\
=   & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}  dy\\
\end{aligned}
$}
\end{equation}

На пути интегрирования присутствуют особенности при $y = C - R$, $y = Z$, $y = C + R$, и подынтегральное выражение все еще достаточно сложно для непосредственной оценки. Разделим интеграл на несколько сегментов и оценим каждый.

\subsubsection{Случай 1: $C - R \le y \le Z$}
Очень важным свойством $s(k)$ является ее стремление к 1 при $\Im k$ стремящемся к нулю. Благодаря этому $\ln s(k)$ стремится к нулю, что в свою очередь необходимо чтобы компенсировать сингулярность функции $\frac{1}{R - C + y}$ при $y = C - R$. Интуитивно, контур интегрирования становится все ближе и ближе к $\bbR$ при увеличении радиуса и если бы $\ln s(k)$ не занулялась, сходимость бы пропала. Таким образом, разумная нижняя оценка на $s(k)$ также должна удовлетворять свойству сходимости к $1$ при $\Im k$ стремящемся к $0$.

Так как $l$ выпукла при $0 \le y \le Z$, она может быть оценена снизу с помощью первой производной в $0$. Однако, этого недостаточно, так как это нарушит неотрицательность выражения под знаком логарифма, следовательно, надо быть аккуратнее и оценить снизу функцию в точке $Z$ в том числа, после чего склеить эти две оценки в некой точке $Z_0$:
\begin{align*}
f(y)
& = 
\begin{cases}
l'(0) y + 1   &, 0 \le y < Z_0  \\
l'(Z) (y - Z) &, Z_0 \le y < Z \\
\end{cases}
\\
& =
\begin{cases}
\frac{-2}{V} y + 1   &, 0 \le y < Z_0  \\
\frac{1}{2 V}(V^2 - 1) (y - Z) &, Z_0 \le y < Z \\
\end{cases}
\end{align*}

Заметим, что в качестве $Z_0$ можно взять любое число в полуинтервале $[C-R, Z)$ (оценка снизу не обязана быть непрерывной функцией), главное чтобы $f(y)$ была неотрицательно определенной. Для простоты вычислений нам подойдет $Z_0 = \frac{V}{4}$. \mtodo{plot?}

Далее, отдельно рассматриваем интегралы на участках $[C - R, \frac{V}{4})$ и $[\frac{V}{4}, Z)$.

\subsubsection{$C - R \le y < \frac{V}{4}$}

Посчитаем верхнюю оценку на подынтегральное выражение (\ref{eq:int_f}). Заметим, что при $C - R \le y \le \frac{V}{4}$:
\begin{align*}
       & \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
\\ \le & \ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
% \\ \le & \ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\end{align*}
,воспользуемся неравенством $\frac{x}{1 + x} \le \ln (1 + x)$ для $x > -1$, где $x = -\frac{2}{V} y$. Так как выражение под логарифмом меньше единицы, получим что $\ln^2 (1 + x) \le \frac{x^2}{(1 + x)^2}$:
\begin{align*}
       & \dots 
\\ \le & \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V}y)^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
\\ \le & \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V} \frac{V}{4})^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
\end{align*}

Заметим, что подынтегральное выражение теперь имеет вид $\frac{y^2}{a + b y}$, где $a = R^2 - C^2 + 1, b = 2 (C + 1)$, и при достаточно больших $R$ и $C$, $a > 0$ и $b > 0$. Заметим, что при этом $\frac{y^2}{a + b y}$ неотрицательно при $y > 0$, и строго возрастает:
\[
  \left(\frac{y^2}{a + b y}\right)'
= \frac{2y}{a + by} + y^2 \frac{-b}{(a + by)^2}
= \frac{2y (a + by) - b y^2}{(a + by)^2}
= \frac{y (2a + by)}{(a + by)^2}
\ge 0
\]

Следовательно, функцию можно оценить сверху ее значением на правом конце интервала в точке $\frac{V}{4}$, и легко видеть, что:
\[
\frac{y^2}{a + b y} = \mcO\left(\frac{1}{R}\right)
\]

Оставшаяся часть интеграла имеет вид:
\[
\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} = 2 \sqrt{\frac{V}{4} - C + R} = \mcO(1)
\]
, и в итоге весь интеграл на участке $[C - R, \frac{V}{4})$ имеет порядок $\mcO\left(\frac{1}{R}\right)$.

\subsubsection{$\frac{V}{4} \le y < Z$}

Оценим сверху подынтегральное выражение (\ref{eq:int_f}). Заметим, что для $\frac{V}{4} \le y < Z$:
\begin{align*}
    & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}} 
\\ \le & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}}
\\ \le & \ln^2 \left( \frac{1}{2 V}(V^2 - 1) (y - Z) \right) \frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}}
\end{align*}

Функция $\ln^2(x)$ интегрируема в окрестности $x = 0$, и известно что: %  REFTODO

\[
\int\limits_{x=x_0}^b \ln^2(a (x - b)) dx = (b - x_0) (\ln^2(a (x_0 - b)) - 2 \ln(a (x_0 - b)) + 2)
\]

В нашем случае: $x_0 = \frac{V}{4}$, $b = Z$, следовательно, $x_0 - b \ne 0$ и определенный интеграл ограничен постоянной, не зависящей от $R$ и $C$. Таким образом, поведение интеграла зависит только от поведения множителя:

\[
\frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R - C + \frac{V}{4}}} \frac{1}{\sqrt{R + C - Z}}
\]

Очевидно, что при $r \to \infty$, $R \to \infty$, $C \to \infty$, $R - C \to 0$, и можно легко видеть, что выражение выше принадлежит классу $\mcO(\frac{1}{\sqrt{R}})$, и, следовательно, в пределе будет зануляться.

\subsubsection{Случай 2: $y > Z$}
При $y > Z$, 
\[
l(x + \iu y) 
 = \frac{\tanh y - V}{\tanh y + V}
 = 1 - 2 \frac{V}{\tanh y + V}
\]

% https://proofwiki.org/wiki/Inverse_of_Strictly_Increasing_Strictly_Concave_Real_Function_is_Strictly_Convex
\mtodo{proof? just take a look at second derivative?}
Так как $l$ вогнута, строго возрастает, и для фиксированного $r$, нас интересуют только $y \le C + R$, мы можем оценить функцию линейной: \mtodo{plot?}
\[
f(y) = \frac{l(C + R)}{C + R - Z} (y - Z)
\]
\mtodo{actually, even C + R is okay but whatever}
Заметим, что в точке $C + R$, для начиная с достаточно большого $r$, функция $l(y)$ с зажата константами, не зависящими от $C$ и $R$. Это легко понять так как $\tanh y$ на бесконечности уходит к $1$, соответственно, $l(y)$ в пределе будет равно $1 - \frac{2 V}{V + 1}$. Это является довольно важным свойством данного квантового графа, если бы $l$ на бесконечности устремлялась к нулю, эта часть доказательства не могла бы быть проведена (см. \autoref{sec:ring}).

В начале заметим, что на всем участке $Z \le y \le R + C$ у функции $\frac{1}{\sqrt{R - C + y}}$ нет сингулярности, и подынтегральное выражение (\ref{eq:int_f}) можно оценить как:
\begin{equation}\label{eq:int_f_up}
\begin{aligned}
       & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
\\ \le & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\end{aligned}
\end{equation}

Чтобы оценить это выражение, разделим интеграл на интервалы $[Z, Z + \frac{1}{R})$, $[Z + \frac{1}{R}, C)$, $[C, C + R]$.

\subsubsection{$Z \le y < Z + \frac{1}{R}$}

Оценим сверху выражение (\ref{eq:int_f_up}):
\begin{align*}
       & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}}
% \\  = & \ln^2 f(y) \mcO()
\end{align*}

\mtodo{reference?}
$\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy$ легко вычислить явно, используя:
\[
    \int\limits_b^{b + c} \ln^2 (a (x - b)) dx = c (\ln^2(a c) - 2 \ln (a c) + 2)
\]

Таким образом, $\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy = \frac{1}{R} ( \ln^2 (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) - 2 \ln (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) + 2)$. Так как $l(C + R)$ ограничена константами, не зависящими от $r$, раскрывая логарифмы, легко можно понять что выражение принадлежит классу $\mcO(\frac{\ln^2 R}{R})$. Учитывая что коэффициент перед интегралом:
\[
\frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}}
\]
, очевидно, имеет порядок $\mcO\left(\frac{1}{\sqrt{R}}\right)$, очевидно что интеграл на данном интервале стремится к нулю при $R, C \to \infty$.

\subsubsection{$Z + \frac{1}{R} \le y < C$}
Оценим сверху выражение (\ref{eq:int_f_up}):
\begin{align*}
       & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \ln^2 f(Z + \frac{1}{R}) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - C}} \frac{1}{\sqrt{R - C + Z}}
\end{align*}

Первообразная для функции подобного вида широко известна:
\[
\int \frac{1}{a x + b} = \frac{\ln (a x + b)}{a}
\]
, где в нашем случае $a = 2 (C + 1)$, $b = R^2 - C^2 + 1$. Применяя формулу Ньютона-Лейбница для интервала $(Z + \frac{1}{R}, C)$, получим:
\[
\frac{\ln \frac{2 (C + 1) C + R^2 - C^2 + 1}{2 (C + 1) (Z + \frac{1}{R}) + R^2 - C^2 + 1}}{2 (C + 1)} = \mcO\left( \frac{\ln R}{R} \right)
\]

При стремлении $R$ к бесконечности, $\ln^2 f(Z + \frac{1}{R})$ будет также стремиться к бесконечности, поэтому необходимо оценить порядок особенности. Так как $\ln f(Z + \frac{1}{R}) = \ln \left( \frac{l(C + R)}{C + R - Z} \frac{1}{R} \right) = \ln l(C + R) - \ln (C + R - Z) - \ln R$, легко видеть что $\ln^2 f(Z + \frac{1}{R}) = \mcO (\ln^2 R)$.

В результате, комбинируя все оценки, получаем: $\mcO (\ln^2 R) \mcO\left( \frac{\ln R}{R} \right) \frac{R}{\sqrt{R}} \frac{1}{\sqrt{R - C + Z}} = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)$, что означает что интеграл на этом участке стремится к $0$ с увеличением $r$.

\subsubsection{$C \le y \le C + R$}

Оценим сверху выражение (\ref{eq:int_f_up}):
\begin{align*}
       & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
% \\  = & \ln^2 f(y) \mcO()
\end{align*}

Интеграл $\frac{1}{\sqrt{R + C - y}}$ от $C$ до $C + R$ тривиален и равен $2 \sqrt{R}$. Функция $f$ в точке $C$ ограничена константами не зависящими от $R$ и $C$, следовательно, и квадрат ее логарифма. Очевидно, что в результате получим выражение $\mcO \left( \frac{1}{R} \right) \sqrt R = \mcO \left( \frac{1}{\sqrt{R}} \right)$.

\subsubsection{Оценка $\int \abs{f(t)}^2$: итог}
Итого, мы разбили интегрирование на пять различных участков, и в итоге имеем порядок интеграла:
\[
\mcO \left( \frac{1}{R} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)
\]
, что означает, что весь интеграл уходит в 0 при стремлении $r$ к 1 (соответственно, $R$ к бесконечности), что и требовалось доказать.

### 2016-12-19 bundle.tex
More

@@
 
-Let's invastigate the model on \autoref{fig:res_bundle}.
+Let's investigate the model on \autoref{fig:res_bundle}.
 Schrodinger's operator is defined on edges of the graph as  $-\dv[2]{\psi}{x}$.
@@
 
-\subsubsection{Оценка $\int \abs{f(t)}^2$}
-Функция $s(k)$ (\ref{eq:bundle_s}) слишком сложна для прямого аналитического доказательства сходимости.
-Однако, так как $s(k)$ — модуль определителя $S$-матрицы, в верхней комплексной полуплоскости $0 \le s(k) \le 1$.
-Это означает, что $s(k)$ может быть заменена на некую оценку снизу $l(k)$, такую что $0 \le l(k) \le s(k)$.
-После этого, если будет доказана сходимость к нулю для этой нижней оценки, то так как $s(k) \le 1$, $\ln l(k) \le \ln s(k) \le 0$, мы будем иметь $\ln^2 s(k) \le \ln^2 l(k)$, и, следовательно, так как подынтегральное выражение неотрицательно, сходимость искомого интеграла.
-Мы часто будем опираться на этот факт и проводить подобные замены под знаком логарифма, заменяя сложные функции на кусочно-линейные, и используя известные оценки для логарифма чтобы оценить исходный интеграл.
+\subsubsection{Estimating $\int \abs{f(t)}^2$}
+Function $s(k)$ (\ref{eq:bundle_s}) is too complex for direct proof of the convergence.
 
-\subsubsection{Упрощение функции $s(k)$}
-Сначала мы дадим простую оценку для $s(k)$ по всей верней комплексной полуплоскости и сделаем ее независимой от вещественной части аргумента.
+We proceed as follows:
 
-Легко видеть, что $s(k)$ периодична относительно вещественной части аргумента при неизменной комплексной части.
+\begin{itemize}
+\item Since $s(k)$ is an absolute value of the determinant of the $S$ matrix, in the upper complex plane $0 \le s(k) \le 1$ holds.
+From here, we immediately know that the integral is bounded from above since TODO blah blah
+\item We replace $s(k)$ with a lower bound $l(k)$ such that: $0 \le l(k) \le s(k) \le 1$.
+\item By appling logarithm to the expression above, we get $\ln l(k) \le \ln s(k) \le 0$, and therefore, $\ln^2 s(k) \le \ln^2 l(k)$.
+\item Now, if we prove convergence for $l(k)$, this immediately proves the convergence of the original integral.
+\end{itemize}
+
+We are going to use this fact in our proof and do such function changes under the integral sign, replacing complicated function with simpler (in particular, piecewise linear) lower bounds, and then using well known facts to estimate the integral.
+
+\subsubsection{Simplifying $s(k)$}
+We build a simple estimate for $s(k)$ over the upper complex plane. This function will be independent of the complex part of its argument which will make the analysis way easier.
+
+\begin{enumerate}
+\item
+  It is easy to spot that if we fix the complex part of the argument, $s(k)$ is periodic with respect to the real part of its argument.
 % Since $\sin k$ and $\cos k$ are periodic w.r.t the real axis, with the period of $2 \pi$, 
 \mtodo{is this step really necessary?}
-
-У функции $s(k)$ есть счетное число нулей, и для всех $\Im k = \atanh \frac{2 W}{W^2 + 1}$. Для краткости, дадим обозначения:
+\item 
+  Function $s(k)$ has countably infinite set of zeros, and each of them has $\Im k = \atanh \frac{2 W}{W^2 + 1}$. For brewity, we define:
 
@@
   \end{equation*}
+\item
+  Notice that for each $x$, $s(x + \iu y) \le s(\iu y)$. \mtodo{How to prove? We could probably take a look at numerator and denominator in separate?} 
+\end{enumerate}
 
-Далее, заметим что для любого $x$, $s(x + \iu y) \le s(\iu y)$.
-\mtodo{How to prove?
-We could probably take a look at numerator and denominator in separate?} После всех вышеупомянутых замечаний, для $s(x + \iu y)$ можно дать довольно простую нижнюю оценку:
+Given these fact, we can build a simple lower bound for $s(x + \iu y)$:
 \begin{align*}
@@
    &= \abs{\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}}
-\\ &= \abs{\frac{\tanh y - V}{\tanh y + V}} && \text{(так как $\cosh y \ge 1$)}
+\\ &= \abs{\frac{\tanh y - V}{\tanh y + V}} && \text{(since $\cosh y > 0$)}
 \end{align*}
 
-Легко понять, что у функции $l(k)$ будут нули вдоль линии $\Im k = Z$, что значит, что вдоль этой линии у функции $\ln l(k)$ будет несчетное множество особенностей.
-Интуитивно, это не должно испортить сходимость, так как контур интегрирования все равно мог пересечь сингулярность функции $\ln s(k)$.
-Действительно, далее мы покажем, что даже такое загрубление функции позволяет доказать сходимость.
-Далее, для краткости записи, будем опускать вещественную часть аргумента и обозначим $l(y) = l(x + \iu y)$, где $x$ может быть любым, так как $l$ от него все равно не зависит.
+It's pretty clear that $l(k)$ has a continuum of zeros over the line $\Im k = Z$, which implies that $\ln l(k)$ has continuum number of singularities over this line.
+Intuitively, it shouldn't spoil the convergence of integral since the contour of integration cound intersect the singularities of the original function anyway.
+And indeed, we will give a rigorous argument that we still can prove convergence in this case.
+Since the function is independent from the real part of the argument now, for brewity, we will omit it and defince $l(y) = l(\iu y)$.
 \mtodo{Plot?}
@@
 
-После построения нижней оценки можно упростить интеграл, который мы исследуем:
+Now, we will simplify the integral (TODO REF) using the bound we just built:
 \begin{align*}
@@
 
-Во-первых, заметим, что:
+First, notice that:
 
@@
 \end{equation*}
-, то есть подынтегральное выражение симметрично относительно оси $y$, и, следовательно, достаточно доказать сходимость интеграла на отрезке $-\pi/2 \le t \le \pi/2$.
+, that is, the integrand is symmetric with respect to $y$ and for proving convergence it is enough to prove convergence on the (half circle) contour defined by $-\pi/2 \le t \le \pi/2$.
 
-Далее, заменим переменную интегрирования:
+Next, we do a variable change:
 \begin{equation*}
@@
 \end{equation*}
-, что после подстановки дает:
+, and after substitution:
 \begin{equation}\label{eq:int_f}
@@
 
-На пути интегрирования присутствуют особенности при $y = C - R$, $y = Z$, $y = C + R$, и подынтегральное выражение все еще достаточно сложно для непосредственной оценки.
-Разделим интеграл на несколько сегментов и оценим каждый.
+On the integration path we cross singularities at $y = C - R$, $y = Z$, $y = C + R$, and the integrand is still too complex for direct estimation.
+Let's split the integration path in multiple segments and estimate them independently.
 

### 2016-12-19 bundle.tex
More

@@
 
-\subsubsection{Случай 1: $C - R \le y \le Z$}
-Очень важным свойством $s(k)$ является ее стремление к 1 при $\Im k$ стремящемся к нулю.
-Благодаря этому $\ln s(k)$ стремится к нулю, что в свою очередь необходимо чтобы компенсировать сингулярность функции $\frac{1}{R - C + y}$ при $y = C - R$.
-Интуитивно, контур интегрирования становится все ближе и ближе к $\bbR$ при увеличении радиуса и если бы $\ln s(k)$ не занулялась, сходимость бы пропала.
-Таким образом, разумная нижняя оценка на $s(k)$ также должна удовлетворять свойству сходимости к $1$ при $\Im k$ стремящемся к $0$.
+\subsubsection{Case 1: $C - R \le y \le Z$}
+A crucial property of $s(k)$ is its convergence to 1 as $\Im k$ converges to TODO ZERO??, since then $\ln s(k)$ goes to zero, which is necessary to compensate the singularity of $\frac{1}{R - C + y}$ at $y = C - R$.
+% TODO: Интуитивно, контур интегрирования становится все ближе и ближе к $\bbR$ при увеличении радиуса и если бы $\ln s(k)$ не занулялась, сходимость бы пропала.
+This implies that lower bound for $s(k)$ should also converge to $1$ as $\Im k$ goes to $0$.
 
-Так как $l$ выпукла при $0 \le y \le Z$, она может быть оценена снизу с помощью первой производной в $0$.
-Однако, этого недостаточно, так как это нарушит неотрицательность выражения под знаком логарифма, следовательно, надо быть аккуратнее и оценить снизу функцию в точке $Z$ в том числа, после чего склеить эти две оценки в некой точке $Z_0$:
+Since $l$ is convex when $0 \le y \le Z$, we can estimate it from below using its first derivative at $0$.
+However, this is not enough, since it will this will violate the property of the estimate being positive (it is under the logarithm sign) TODO PLOT IT, so we have to be more careful and approximate the function at $Z$ with its first derivative as well, and then glue them together at some point $Z_0$:
 \begin{align*}
@@
 
-Заметим, что в качестве $Z_0$ можно взять любое число в полуинтервале $[C-R, Z)$ (оценка снизу не обязана быть непрерывной функцией), главное чтобы $f(y)$ была неотрицательно определенной.
-Для простоты вычислений нам подойдет $Z_0 = \frac{V}{4}$.
-\mtodo{plot?}
+Note that lower bound does not have to be a continuous function, so we can pick any number in $[C - R, Z)$ as $Z_0$. For the ease of calculations, let's take $Z_0 = \frac{V}{4}$. \mtodo{plot?}
 
-Далее, отдельно рассматриваем интегралы на участках $[C - R, \frac{V}{4})$ и $[\frac{V}{4}, Z)$.
+Next we investigate integrals on $[C - R, \frac{V}{4})$ and $[\frac{V}{4}, Z)$ separately.
 

### 2016-12-19 bundle.tex
more

@@
 
-Посчитаем верхнюю оценку на подынтегральное выражение (\ref{eq:int_f}). Заметим, что при $C - R \le y \le \frac{V}{4}$:
+Let's compute an upper bound for the integrand (\ref{eq:int_f}). Note that for $C - R \le y \le \frac{V}{4}$:
 \begin{align*}
@@
 \end{align*}
-,воспользуемся неравенством $\frac{x}{1 + x} \le \ln (1 + x)$ для $x > -1$, где $x = -\frac{2}{V} y$.
-Так как выражение под логарифмом меньше единицы, получим что $\ln^2 (1 + x) \le \frac{x^2}{(1 + x)^2}$:
+
+Now, we use a well known inequality which holds for $x > -1$: TODO REFERENCE
+\[
+\frac{x}{1 + x} \le \ln (1 + x)
+\]
+, where in our case $x = -\frac{2}{V} y$. Since the expression under logarithm is less than 1, we get $\ln^2 (1 + x) \le \frac{x^2}{(1 + x)^2}$:
 \begin{align*}
@@
 \\ \le & \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V} \frac{V}{4})^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
+\\ = & \frac{\frac{4}{V^2}}{(1 - \frac{2}{V} \frac{V}{4})^2} \frac{R}{\sqrt{R + C - Z}} \frac{y^2}{R^2 - C^2 + 2 (C + 1) y + 1}  \frac{1}{\sqrt{R - C + y}}
 \end{align*}
 
-Заметим, что подынтегральное выражение теперь имеет вид $\frac{y^2}{a + b y}$, где $a = R^2 - C^2 + 1, b = 2 (C + 1)$, и при достаточно больших $R$ и $C$, $a > 0$ и $b > 0$.
-Заметим, что при этом $\frac{y^2}{a + b y}$ неотрицательно при $y > 0$, и строго возрастает:
+Note that we can ignore the terms dependent on $V$ only since $V$ is a constant independent of $r$.
+Now the integrand (TODO ACTUALLY ONLY ONE PART OF IT) has the form $\frac{y^2}{a + b y}$, where $a = R^2 - C^2 + 1, b = 2 (C + 1)$; when $R$ and $C$ are big enough, $a > 0$ (TODO WHY) и $b > 0$.
+That means $\frac{y^2}{a + b y}$ will be nonnegative when $y > 0$, and strictly increasing, since:
 \[
@@
 
-Следовательно, функцию можно оценить сверху ее значением на правом конце интервала в точке $\frac{V}{4}$, и легко видеть, что:
+This implies that we can estimate the function from above by using its value on the rightmost point of the interval at $\frac{V}{4}$.
 \[
@@
 \]
+TODO ELABORATE ON THAT!
 
-Оставшаяся часть интеграла имеет вид:
+The remaning part of integral is:
 \[
@@
 \]
-, и в итоге весь интеграл на участке $[C - R, \frac{V}{4})$ имеет порядок $\mcO\left(\frac{1}{R}\right)$.
+
+And finally, after combining all these estimages, we get $\mcO(1) \mcO(\sqrt{R}) \mcO\left(\frac{1}{R}\right) \mcO(1)  = \mcO\left(\frac{1}{\sqrt{R}}\right)$ TODO EXPAND IN TERMS OF small r!
 

### 2016-12-19 bundle.tex
more

@@
 
-Оценим сверху подынтегральное выражение (\ref{eq:int_f}). Заметим, что для $\frac{V}{4} \le y < Z$:
+Let's estimate the integral (\ref{eq:int_f}) from above. Note that for $\frac{V}{4} \le y < Z$:
 \begin{align*}
-    & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}} 
-\\ \le & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}}
-\\ \le & \ln^2 \left( \frac{1}{2 V}(V^2 - 1) (y - Z) \right) \frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}}
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}} 
+\\ \le & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}}
+\\ \le &  \frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}} \int \ln^2 \left( \frac{1}{2 V}(V^2 - 1) (y - Z) \right)
 \end{align*}
 
-Функция $\ln^2(x)$ интегрируема в окрестности $x = 0$, и известно что: %  REFTODO
+$\ln^2(x)$ is integrable in the neighborhood of $x = 0$, and it is known that: %  REFTODO
 
@@
 
-В нашем случае: $x_0 = \frac{V}{4}$, $b = Z$, следовательно, $x_0 - b \ne 0$ и определенный интеграл ограничен постоянной, не зависящей от $R$ и $C$.
+In our case $x_0 = \frac{V}{4}$, $a = \frac{1}{2 V}(V^2 - 1)$, $b = Z$, and we can see that the integral is bounded by a constant independent of $R$ and $C$.
 Таким образом, поведение интеграла зависит только от поведения множителя:
@@
 \[
-\frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R - C + \frac{V}{4}}} \frac{1}{\sqrt{R + C - Z}}
+\frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}} 
 \]
 
-Очевидно, что при $r \to \infty$, $R \to \infty$, $C \to \infty$, $R - C \to 0$, и можно легко видеть, что выражение выше принадлежит классу $\mcO(\frac{1}{\sqrt{R}})$, и, следовательно, в пределе будет зануляться.
+Clearly, as $r \to \infty$, we get $R \to \infty$, $C \to \infty$, $R - C \to 0$, and we can see that the expression grows as $\mcO(\frac{1}{\sqrt{R}})$ TODO ELABORATE
 
-\subsubsection{Случай 2: $y > Z$}
+\subsubsection{Case 2: $y > Z$}
 При $y > Z$, 

### 2016-12-19 bundle.tex
more

@@
 \subsubsection{Case 2: $y > Z$}
-При $y > Z$, 
+When $y > Z$, 
 \[
@@
 \mtodo{proof? just take a look at second derivative?}
-Так как $l$ вогнута, строго возрастает, и для фиксированного $r$, нас интересуют только $y \le C + R$, мы можем оценить функцию линейной: \mtodo{plot?}
+Since $l$ is concave, strictly increasing and for a fixed $r$, we are only interested at $y \le C + R$, we can estimate the function by a linear one: \mtodo{plot?}
 \[
@@
 \mtodo{actually, even C + R is okay but whatever}
-Заметим, что в точке $C + R$, для начиная с достаточно большого $r$, функция $l(y)$ с зажата константами, не зависящими от $C$ и $R$.
-Это легко понять так как $\tanh y$ на бесконечности уходит к $1$, соответственно, $l(y)$ в пределе будет равно $1 - \frac{2 V}{V + 1}$.
-Это является довольно важным свойством данного квантового графа, если бы $l$ на бесконечности устремлялась к нулю, эта часть доказательства не могла бы быть проведена (см.
-\autoref{sec:ring}).
 
-В начале заметим, что на всем участке $Z \le y \le R + C$ у функции $\frac{1}{\sqrt{R - C + y}}$ нет сингулярности, и подынтегральное выражение (\ref{eq:int_f}) можно оценить как:
+Notice that when $y = C + R$, for a sufficiently big $r$, $l(y)$ is bounded from both sides by constants, independent from $C$ and $R$.
+This is because $\tanh y$ goes to $1$ as $y$ goes to infinity, therefore, $l(y)$ in the limit will be equal to $1 - \frac{2 V}{V + 1}$.
+This is an important property of this specific model, since if $l$ went to zero on infinity, this part of proof couldn't have been done (see \autoref{sec:ring}).
+
+First, not that on $Z \le y \le R + C$ the function $\frac{1}{\sqrt{R - C + y}}$ has no singularities and we can estimate integral (\ref{eq:int_f}) as:
 \begin{equation}\label{eq:int_f_up}
 \begin{aligned}
-       & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
-\\ \le & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
+\\ \le & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}} 
 \end{aligned}
@@
 
-Чтобы оценить это выражение, разделим интеграл на интервалы $[Z, Z + \frac{1}{R})$, $[Z + \frac{1}{R}, C)$, $[C, C + R]$.
+To estimate this expression, let's split the integration interval in two: $[Z, Z + \frac{1}{R})$, $[Z + \frac{1}{R}, C)$, $[C, C + R]$.
 
@@
 
-Оценим сверху выражение (\ref{eq:int_f_up}):
+Let's estimate (\ref{eq:int_f_up}), replacing functions in integrands by their extreme value at interval's ends:
 \begin{align*}
-       & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
-\\ \le & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}}
-% \\  = & \ln^2 f(y) \mcO()
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+\\ \le & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}}
+\\ =   & \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}} \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \int \ln^2 f(y) 
 \end{align*}
@@
 \mtodo{reference?}
-$\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy$ легко вычислить явно, используя:
+$\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy$ can be computed explicitly, using:
 \[
@@
 
-Таким образом, $\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy = \frac{1}{R} ( \ln^2 (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) - 2 \ln (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) + 2)$.
-Так как $l(C + R)$ ограничена константами, не зависящими от $r$, раскрывая логарифмы, легко можно понять что выражение принадлежит классу $\mcO(\frac{\ln^2 R}{R})$.
-Учитывая что коэффициент перед интегралом:
+Hence, $\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy = \frac{1}{R} ( \ln^2 (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) - 2 \ln (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) + 2)$.
+As we noted above, $l(C + R)$ is bounded by constants independent on $r$, and we can clearly see that the expression grows as $\mcO(\frac{\ln^2 R}{R})$.
+Since the coefficient before the integral:
 \[
@@
 \]
-, очевидно, имеет порядок $\mcO\left(\frac{1}{\sqrt{R}}\right)$, очевидно что интеграл на данном интервале стремится к нулю при $R, C \to \infty$.
+, has order of growth $\mcO\left(\frac{1}{\sqrt{R}}\right)$, it is clear that the integral on this interval goes to zero as $R, C \to \infty$.
 

### 2016-12-19 bundle.tex
one more section

@@
 
-To estimate this expression, let's split the integration interval in two: $[Z, Z + \frac{1}{R})$, $[Z + \frac{1}{R}, C)$, $[C, C + R]$.
+To estimate this expression, let's split the integration interval in three: $[Z, Z + \frac{1}{R})$, $[Z + \frac{1}{R}, C)$, $[C, C + R]$.
 
@@
 \subsubsection{$Z + \frac{1}{R} \le y < C$}
-Оценим сверху выражение (\ref{eq:int_f_up}):
+Let's estimate (\ref{eq:int_f_up}) from above TODO again by picking extreme values blah blah:
 \begin{align*}
-       & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
-\\ \le & \ln^2 f(Z + \frac{1}{R}) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - C}} \frac{1}{\sqrt{R - C + Z}}
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+\\ \le & \int \ln^2 f(Z + \frac{1}{R}) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - C}} \frac{1}{\sqrt{R - C + Z}}
+\\  =  & \ln^2 f(Z + \frac{1}{R})  \frac{R}{\sqrt{R + C - C}} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{R^2 - C^2 + 2 (C + 1) y + 1}
 \end{align*}
 
-Первообразная для функции подобного вида широко известна:
+TODO REPLACE R BY C(R) EVERYWHERE?
+
+Antiderivative for such a function is well known:
 \[
@@
 \]
-, где в нашем случае $a = 2 (C + 1)$, $b = R^2 - C^2 + 1$. Применяя формулу Ньютона-Лейбница для интервала $(Z + \frac{1}{R}, C)$, получим:
+, in our case $a = 2 (C + 1)$, $b = R^2 - C^2 + 1$. Substituting the ends of the interval $(Z + \frac{1}{R}, C)$, we get the definite integral:
 \[
@@
 
-При стремлении $R$ к бесконечности, $\ln^2 f(Z + \frac{1}{R})$ будет также стремиться к бесконечности, поэтому необходимо оценить порядок особенности.
-Так как $\ln f(Z + \frac{1}{R}) = \ln \left( \frac{l(C + R)}{C + R - Z} \frac{1}{R} \right) = \ln l(C + R) - \ln (C + R - Z) - \ln R$, легко видеть что $\ln^2 f(Z + \frac{1}{R}) = \mcO (\ln^2 R)$.
+As $R$ goes to infinity, $\ln^2 f(Z + \frac{1}{R})$ goes to infinity as well, so we have to compute the order of singularity.
+Since $\ln f(Z + \frac{1}{R}) = \ln \left( \frac{l(C + R)}{C + R - Z} \frac{1}{R} \right) = \ln l(C + R) - \ln (C + R - Z) - \ln R$, we can see that $\ln^2 f(Z + \frac{1}{R}) = \mcO (\ln^2 R)$.
 
-В результате, комбинируя все оценки, получаем: $\mcO (\ln^2 R) \mcO\left( \frac{\ln R}{R} \right) \frac{R}{\sqrt{R}} \frac{1}{\sqrt{R - C + Z}} = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)$, что означает что интеграл на этом участке стремится к $0$ с увеличением $r$.
+Finally, after combining all estimates, we get: $\mcO (\ln^2 R) \mcO\left( \frac{\ln R}{R} \right) \frac{R}{\sqrt{R}} \frac{1}{\sqrt{R - C + Z}} = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)$, which means that integral goes to $0$ on this interval as $r$ goes to $1$.
 

### 2016-12-20 bundle.tex
Final!

@@
 
-Оценим сверху выражение (\ref{eq:int_f_up}):
+Let's estimate (\ref{eq:int_f_up}) from above:
 \begin{align*}
-       & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
-\\ \le & \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+\\ \le & \int \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+\\ =   & \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{\sqrt{R + C - y}}
 % \\  = & \ln^2 f(y) \mcO()
@@
 
-Интеграл $\frac{1}{\sqrt{R + C - y}}$ от $C$ до $C + R$ тривиален и равен $2 \sqrt{R}$.
-Функция $f$ в точке $C$ ограничена константами не зависящими от $R$ и $C$, следовательно, и квадрат ее логарифма.
-Очевидно, что в результате получим выражение $\mcO \left( \frac{1}{R} \right) \sqrt R = \mcO \left( \frac{1}{\sqrt{R}} \right)$.
+Integral $\frac{1}{\sqrt{R + C - y}}$ from $C$ to $C + R$ is elementary and equals $2 \sqrt{R}$.
+Function $f$ at $C$ is bounded by constants not dependent on $r$, therefore, the square of its logarithm as well.
+Finally, we get an expression of order $\mcO \left( \frac{1}{R} \right) \mcO( \sqrt R ) = \mcO \left( \frac{1}{\sqrt{R}} \right)$.
 
-\subsubsection{Оценка $\int \abs{f(t)}^2$: итог}
-Итого, мы разбили интегрирование на пять различных участков, и в итоге имеем порядок интеграла:
+\subsubsection{Final estimate of $\int \abs{f(t)}^2$}
+We split our integration path in five intervals, and the integral has order:
 \[
-\mcO \left( \frac{1}{R} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)
+\mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)
 \]
-, что означает, что весь интеграл уходит в 0 при стремлении $r$ к 1 (соответственно, $R$ к бесконечности), что и требовалось доказать.
+, which means that integral converges to $0$ as $r$ goes to $1$.

### 2016-12-20 bundle.tex
Moved preamble

@@
 \end{tikzpicture}
-\caption{Квантовый граф $\Gamma$, состоящий из полубесконечных ребер $\Omega_L, \Omega_R$ и рассеивателя $\Omega$, представляющего из себя $W$ идентичных ребер длины 1.
-В вершинах $V_a$, $V_b$ находятся $\delta$-образные потенциальные ямы глубины $a$ и $b$ соответственно.}\label{fig:res_bundle}
+\caption{Quantum graph $\Gamma$, consisting of semi infinite edges  $\Omega_L, \Omega_R$ and a resonator $\Omega$, consisting of $W$ identical edges of length 1.}
+\label{fig:res_bundle}
 \end{figure}
@@
 In our case $x_0 = \frac{V}{4}$, $a = \frac{1}{2 V}(V^2 - 1)$, $b = Z$, and we can see that the integral is bounded by a constant independent of $R$ and $C$.
-Таким образом, поведение интеграла зависит только от поведения множителя:
+Hence, the behaviour of the integral only dependends on the behaviour of the multiplier:
 

### 2016-12-20 paper.tex
Translated and simplified parts of paper
Moved preamble
Inlined macros, less packages

@@
-\input{preamble.tex}
-\input{macros/macros.tex}
+\documentclass[12pt, a4paper]{article}
+
+\usepackage[utf8]{inputenc}
+\usepackage[T2A]{fontenc}
+\usepackage[russian, english]{babel}
+
+% \usepackage{fullpage}
+\usepackage{cite}
+\usepackage{hyperref} % \url{url} \href{url}{displayed text}
+
+\usepackage[pdftex]{graphicx}
+\graphicspath{{pic/}}
+\usepackage{tikz}
+\usepackage{xcolor} % \textcolor
+\usepackage{mathtools} % xmapsto, \Vector
+\usepackage{amsmath,amsfonts,amssymb,amsthm,amscd,amsxtra}
+\usepackage{physics}
+\usepackage[colorinlistoftodos,prependcaption,disable]{todonotes} % TODO: move to preamble!!
+\presetkeys%
+    {todonotes}%
+    {inline,backgroundcolor=red}{}
+\newcommand{\mtodo}[1]{\todo[linecolor=green!70!white, backgroundcolor=blue!20!white, bordercolor=red]{#1}}
+
+\newcommand{\hilb}[1]{\mathcal{H}_{#1}}
+\newcommand{\cconj}[1]{\overline{#1}}
+\newcommand{\hank}[1]{H_{#1}^{(1)}}
+
+\newcommand{\mcF}{\mathcal{F}}
+\newcommand{\mcH}{\mathcal{H}} % ???
+\newcommand{\mcI}{\mathcal{I}}
+\newcommand{\mcL}{\mathcal{L}} % L2 space
+\newcommand{\mcO}{\mathcal{O}} % Big O
+\newcommand{\mcP}{\mathcal{P}}
+
+\newcommand{\bbC}{\mathbb{C}} % complex plane
+\newcommand{\bbD}{\mathbb{D}} % complex unit disk
+\newcommand{\bbN}{\mathbb{N}}
+\newcommand{\bbK}{\mathbb{K}}
+\newcommand{\bbR}{\mathbb{R}}
+\newcommand{\bbT}{\mathbb{T}} % complex unit circle
+\newcommand{\bbZ}{\mathbb{Z}}
+
+% imaginary unit
+\newcommand{\iu}{{i\mkern1mu}}
+
+\newcommand{\eps}{\varepsilon}
+
+\renewcommand{\Re}{\operatorname{Re}}
+\renewcommand{\Im}{\operatorname{Im}}
+\renewcommand{\phi}{\varphi} % TODO is there a prettier way to do that
+
+\newcommand{\eexp}[1]{e^{#1}}
+
+\DeclareMathOperator\atanh{atanh}
 
@@
 
-Latex math notes demo.
-
-ITMO University.
-
-\[
-\bra{\vb{\psi}} \ket{\eps}
-\]
-
 \input{bundle.tex}

### 2016-12-20 chapter_1_background.tex
More

\section{Различные обозначения}
\begin{itemize}
\item $\bbC$ — комплексная плоскость, $\bbC = \{ x + \iu y \mid x, y \in \bbR \}$ 
\item $\bbH$ — верхняя комплексная полуплоскость (англ. upper half-plane), $\bbH = \{ x + \iu y \mid y > 0, x, y \in \bbR \}$
\item $\bbD$ — комплексный единичный круг (англ. unit disk), $\bbD = \{ z \mid \abs{z} < 1 \}$
\item $\bbT$ — комплексная единичная окружность (англ. unit circle), $\bbT = \partial \bbD =  \{z \mid \abs{z} = 1 \}$
\item $z$ используется в качестве переменной, обозначающей точку в верхней комплексной полуплоскости $\bbH$
\item $\zeta$ используется в качестве переменной, обозначающей точку на комплексном единичном диске $\bbD$
\end{itemize}

\section{Уравнение Шредингера}

Уравнение Шредингера описывает временную эволюцию чистых состояний квантовых систем во времени, и выглядит как:
\[
\iu \hbar \pdv{t} \Psi(t) = H \Psi(t)
\]
, $\hbar$ — приведенная постоянная Планка, $H$ — гамильтониан, оператор полной энергии системы. Спектром гамильтониана является множество возможных значений энергии квантовой системы, которые можно получить при ее измерении.

Так как в этой работе нам интересна математическая задача рассеяния, и качественное поведение системы, а не конкретные значения энергий, далее мы будем игнорировать постоянную Планка и примем ее равной $1$; а так система статична, и гамильтониан не зависит от времени, можно перейти к стационарному уравнению Шредингера:
\[
H \Psi = E \Psi
\]
При этом решения уравнения разделяются на два класса: связанные состояния (англ. bound states) — те, которые соответствуют дискретной части спектра и чью собственные функции являются квадратично интегрируемыми, и состояния рассеяния (англ. scattering states), которые являются лишь формальными решениями, и соответствуют непрерывной части спектра. Такие решения не лежат не являются квадратично интегрируемыми, и в них мы будем заинтересованы в данной работе.

\section{S-матрица}\label{sec:smatrix}
% \mtodo{картиночку с полюсами и нулями??}
Рассмотрим локализованный одномерный потенциальный барьер или резонатор. Пусть на барьер слева и справа направлены частицы с волновым вектором $k$ (который будет скаляром в одномерном случае). Слева и справа от резонатора частицы ведут себя как свободные, соответственно, в общем виде их волновые функции имеют следующий вид:

\begin{equation}\label{eq:wlwl}
\begin{aligned}
   \psi_L(x) &= A \eexp{\iu k x} + B \eexp{-\iu k x}
\\ \psi_R(x) &= C \eexp{\iu k x} + D \eexp{-\iu k x}
\end{aligned}
\end{equation}

S-матрица, или  матрица рассеяния (англ. scattering matrix) выражает зависимость исходящего состояния от входящего:
\begin{equation}\label{eq:smatrix}
\begin{pmatrix} B \\ C \end{pmatrix} = S \begin{pmatrix} A \\ D \end{pmatrix}
\end{equation}
, и полностью характеризует рассеивающие свойства потенциального барьера.

$S$-матрица обладает рядом интересных свойств \cite[стр. 75]{perelomov1998quantum}, позволяющих анализировать рассеяние в квантовой системе: к примеру, $S$-матрица как функция комплексного аргумента, аналитична в верхней комплексной полуплоскости, а ее полюса соответствуют связным состояниям или резонансам.

\section{Квантовые графы}
Квантовый граф (англ. quantum graph) — широко используемая модель наносистемы \cite{kuchment2002graph, lobanov2013genetic, brown2010analysis}. Квантовый граф представляет из себя набор вершин и линейных, одномерных ребер, их соединяющих, или уходящих на бесконечность (можно обратиться к \autoref{fig:res_segment} в качестве простейшего примера). При этом на ребрах графа действует дифференциальный оператор, к примеру, оператор Шредингера свободной частицы: $-\dv[2]{\psi}{x}$, а в вершинах графа установлено граничное условие, связывающее волновые функции на смежных ребрах.

% Заметим, что если граф $\Gamma$ состоит только из конечного числа ребер конечной длины, его гамильтониан имеет чисто дискретный спектр, и его собственные функции образуют полную систему в $\mcL_2(\Gamma)$. Если же граф $\Gamma$ представляет из себя резонатор $\Omega$ с полубесконечными ребрами, в спектре будет присутствовать непрерывная часть и резонансы, индуцированные собственными числами гамильтониана резонатора $\mcH_\Omega$. Резонансные состояния оператора Шредингера не принадлежат пространству $\mcL_2(\Gamma)$, однако, при сужении их на конечный домен $\Omega$, становятся квадратично интегрируемыми и лежат в пространстве $\mcL_2(\Omega)$. Для многих приложений интересно знать, формируют ли полную систему резонансные состояния графа $\Gamma$ в пространстве $\mcL_2(\Omega)$ резонатора.

\section{Преобразование Кэли}

Прямое преобразование Кэли (англ. Cayley transform) конформно отображает $\bbH$ в $\bbD$:
\begin{equation}\label{eq:cayley}
W(z) = \frac{z - \iu}{z + \iu}
\end{equation}
, обратное преобразование Кэли аналогично отображает $\bbD$ в $\bbH$:
\begin{equation}\label{eq:cayley_inverse}
w(\zeta) = \iu \frac{1 + \zeta}{1 - \zeta}
\end{equation}

Важным свойством преобразование Кэли является инъективное отображение $\bbR$ в единичную окружность $\bbT$.

Так как преобразование Кэли является трансформацией Мебиуса, оно сохраняет окружности. В частности, окружность с радиусом $r$ в нуле, под действием обратного преобразование Кэли перейдет в окружность с центром в $C(r)$ и радиусом $R(r)$, где:

\begin{equation}\label{eq:c_and_r}
\begin{aligned}
   C(r) &= \Im \frac{w(r) + w(-r)}{2}
\\ R(r) &= \Im \frac{w(r) - w(-r)}{2}
\end{aligned}
\end{equation}

Легко заметить, что при стремлении $r$ к $1$, $R(r)$ стремится к бесконечности, а $C(r)$ стремится к $R(r)$, что естественно так как в пределе комплексная единичная окружность отображается в вещественную ось.

\section{Теория Лакса-Филипса}
Мы рассматриваем рассеяние в подходе Лакса-Филипса, кратко опишем его (подробно с ним можно ознакомиться в работах \cite{lax1990scattering,lax1976scattering}).

Рассмотрим задачу Коши для волнового уравнения в области $\Gamma$:
\begin{equation}
\begin{aligned}
   u''_{tt}   &= H u
\\ u(x, 0)    &= u_0(x)
\\ u'_t(x, 0) &= u_1(x).
\end{aligned}
\end{equation}

Пусть $\mathcal{E}$ — гильбертово пространство двухкомпонентных функций с конечной энергией $(u_0, u_1)$ на графе $\Gamma$:
\[
\norm{(u_0, u_1)}^2_{\mathcal{E}} = \frac{1}{2} \int\limits_\Gamma (\abs{u'_0}^2 + \abs{u_1}^2) dx
\]
, где пара $(u_0, u_1)$ называется данными Коши (англ. Cauchy data), а оператор $U(t)$, дающий решение этой задаче: $U(t)(u_0, u_1) = (u(x, t), u'_t(x, t))$, порождает унитарную группу $\{ U(t) \mid t \in \bbR \}$. Данная группа содержит два ортогональных подпространства: $D_-$ — входящее подпространство, и $D_+$ — исходящее.

В теории рассеяния установлено, что существуют отображения $T_\pm: \mathcal{R} \to \mcL^2(\bbR, \bbC^2)$, такие что $T_\pm U(t) = \eexp{\iu k t T_\pm}$, которые называются исходящим (соответственно, входящим) спектральным представлением унитарной группы $U(t)$. Обозначим $K = \mathcal{E} \ominus (D_+ \oplus D_-)$, и рассмотрим полугруппу $Z(t) = \mcP_K U(t)|_K, t > 0$, где $\mcP_K$ — оператор проецирования на $K$. Пусть $B$ — генератор $Z(t)$, то есть $Z(t) = \eexp{\iu B t}$, тогда собственные вектора этого оператора и будут резонансными состояниями, а $T_- T_+^{-1}$ называется оператором рассеяния. Оператор рассеяния действует как умножения на матрично-значную функцию $S(k)$, и являющейся матрицей рассеяния (см. \autoref{sec:smatrix}).

\begin{theorem}[{\cite[стр. 95]{nikol2012treatise}}]
Пусть $S$ — внутренняя функция, тогда следущие утверждения эквивалентны:
\begin{itemize}
\item Оператор $Z$ полный.
\item $S$ — произведение Бляшке-Потапова.
\end{itemize}
\end{theorem}

\begin{theorem}[{\cite[стр. 99]{nikol2012treatise}}]
Пусть вспомогательное пространство конечномерно. Тогда, следующие утверждения эквивалентны:
\begin{itemize}
\item $S$ — произведение Бляшке-Потапова.
\item
\begin{equation}\label{eq:blaschke}
\lim\limits_{r = 1} \int\limits_{\bbT} \log \abs{\det S(r \zeta)} d m(\zeta) = 0
\end{equation}
\end{itemize}
\end{theorem}
Непосредственно применяя эти теоремы, и пользуясь тем, что нашим вспомогательным пространством является $\bbC^2$, получаем, что мы можем воспользоваться данным упрощенным критерием для доказательства полноты резонансных состояний в квантовом графе.

\section{Критерий сходимости}

Так как $\det S$ является скалярной внутренней функцией \cite{nikol2012treatise}, мы можем воспользоваться критерием \ref{eq:blaschke} для исследования полноты системы резонансных состояний. В пространстве единичного диска он будем выглядеть как:
\begin{equation}\label{eq:crit_cayley}
\lim\limits_{r = 1} \int\limits_{\abs{\zeta} = r} \log \abs{\det S(\zeta)} d \zeta = 0
\end{equation}

Так как $S$-матрица естественным образом определена на комплексной плоскости, иногда бывает удобнее работать с этим признаком в верхней полуплоскости $\bbH$, а не на единичном диске. Заменим в (\ref{eq:crit_cayley}) переменную, применив к интегралу преобразование Кэли (\ref{eq:cayley}) к дифференциалу и области интегрирования, получив:

\begin{equation}\label{eq:crit}
\lim\limits_{r \to 1} \int\limits_{C_r} \ln \abs{\det S(k)} \frac{2 \iu}{(k + i)^2} dk = 0
\end{equation}
, где $C_r$ — образ $\abs{\zeta} = r$ относительно обратного преобразования Кэли. Для удобства вычислений параметризуем $C_r$ как $C_r = \{R(r) \eexp{\iu t} + \iu C(r) \mid t \in [0, 2 \pi)\}$ (см. \ref{eq:c_and_r}). Для краткости, обозначим:

\[
s(k) = \abs{\det S(k)}
\]
, и, откинув константы, не влияющие на сходимость/расходимость интеграла, получаем финальную форму критерия, которой и будем пользоваться в дальнейшем:

\begin{equation}\label{eq:critp}
\lim\limits_{r \to 1} \int\limits_{0}^{2 \pi} \ln s(R(r) \eexp{\iu t} + \iu C(r)) \frac{R}{(R(r) \eexp{\iu t} + \iu C(r) + i)^2} dt = 0
\end{equation}
\mtodo{$C + R = \Im w(r) = \frac{1 + r}{1 - r}$, $C - R = \Im w(-r) = \frac{1 - r}{1 + r}$}

### 2016-12-20 chapter_1_background.tex
more

@@
-\section{Различные обозначения}
+\section{Definitions}
 \begin{itemize}
-\item $\bbC$ — комплексная плоскость, $\bbC = \{ x + \iu y \mid x, y \in \bbR \}$ 
-\item $\bbH$ — верхняя комплексная полуплоскость (англ. upper half-plane), $\bbH = \{ x + \iu y \mid y > 0, x, y \in \bbR \}$
-\item $\bbD$ — комплексный единичный круг (англ. unit disk), $\bbD = \{ z \mid \abs{z} < 1 \}$
-\item $\bbT$ — комплексная единичная окружность (англ. unit circle), $\bbT = \partial \bbD =  \{z \mid \abs{z} = 1 \}$
-\item $z$ используется в качестве переменной, обозначающей точку в верхней комплексной полуплоскости $\bbH$
-\item $\zeta$ используется в качестве переменной, обозначающей точку на комплексном единичном диске $\bbD$
+\item $\bbC$ — complex plane, $\bbC = \{ x + \iu y \mid x, y \in \bbR \}$ 
+\item $\bbH$ — upper complex half-plane, $\bbH = \{ x + \iu y \mid y > 0, x, y \in \bbR \}$
+\item $\bbD$ — unit disk, $\bbD = \{ z \mid \abs{z} < 1 \}$
+\item $\bbT$ — unit circle, $\bbT = \partial \bbD =  \{z \mid \abs{z} = 1 \}$
+\item $z$ denotes a complex argument on upper complex half-plane $\bbH$
+\item $\zeta$ denotes a complex argument on unit disk $\bbD$
 \end{itemize}
 
-\section{Уравнение Шредингера}
+\section{Schrodinger's equation}
+In this paper we are only interested in the mathematical scattering problem and not actual energies, so we define Plank's constant as $1$ and use stationary Schrodinger's equation: $H \Psi = E \Psi$.
+We are going to be interested in scattering state solutions for this equation.
 
-Уравнение Шредингера описывает временную эволюцию чистых состояний квантовых систем во времени, и выглядит как:
-\[
-\iu \hbar \pdv{t} \Psi(t) = H \Psi(t)
-\]
-, $\hbar$ — приведенная постоянная Планка, $H$ — гамильтониан, оператор полной энергии системы.
-Спектром гамильтониана является множество возможных значений энергии квантовой системы, которые можно получить при ее измерении.
-
-Так как в этой работе нам интересна математическая задача рассеяния, и качественное поведение системы, а не конкретные значения энергий, далее мы будем игнорировать постоянную Планка и примем ее равной $1$; а так система статична, и гамильтониан не зависит от времени, можно перейти к стационарному уравнению Шредингера:
-\[
-H \Psi = E \Psi
-\]
-При этом решения уравнения разделяются на два класса: связанные состояния (англ.
-bound states) — те, которые соответствуют дискретной части спектра и чью собственные функции являются квадратично интегрируемыми, и состояния рассеяния (англ.
-scattering states), которые являются лишь формальными решениями, и соответствуют непрерывной части спектра.
-Такие решения не лежат не являются квадратично интегрируемыми, и в них мы будем заинтересованы в данной работе.
-
-\section{S-матрица}\label{sec:smatrix}
+\section{S-matrix}\label{sec:smatrix}
 % \mtodo{картиночку с полюсами и нулями??}
+Consider a localized one dimensional potential barrier or resonator. From the left and right we TODO BLAH BLAH
 Рассмотрим локализованный одномерный потенциальный барьер или резонатор.
@@
 
-S-матрица, или  матрица рассеяния (англ. scattering matrix) выражает зависимость исходящего состояния от входящего:
+S-matrix, or scattering matrix relates the final and initial states of the system:
 \begin{equation}\label{eq:smatrix}
@@
 \end{equation}
-, и полностью характеризует рассеивающие свойства потенциального барьера.
+, and defines scattering properties of a potential barriers.
 
-$S$-матрица обладает рядом интересных свойств \cite[стр.
+% $S$-матрица обладает рядом интересных свойств \cite[стр.
 75]{perelomov1998quantum}, позволяющих анализировать рассеяние в квантовой системе: к примеру, $S$-матрица как функция комплексного аргумента, аналитична в верхней комплексной полуплоскости, а ее полюса соответствуют связным состояниям или резонансам.
 
-\section{Квантовые графы}
-Квантовый граф (англ.
+% \section{Квантовые графы}
+% Квантовый граф (англ.
 quantum graph) — широко используемая модель наносистемы \cite{kuchment2002graph, lobanov2013genetic, brown2010analysis}.
@@
 
-\section{Преобразование Кэли}
+\section{Cayley transform}
 
-Прямое преобразование Кэли (англ. Cayley transform) конформно отображает $\bbH$ в $\bbD$:
+Cayley transform maps $\bbH$ to $\bbD$:
 \begin{equation}\label{eq:cayley}
@@
 \end{equation}
-, обратное преобразование Кэли аналогично отображает $\bbD$ в $\bbH$:
+, inverse Cayley transform maps $\bbD$ to $\bbH$:
 \begin{equation}\label{eq:cayley_inverse}
@@
 
-Важным свойством преобразование Кэли является инъективное отображение $\bbR$ в единичную окружность $\bbT$.
+One notable property of the Cayley transform is that it injectively maps $\bbR$ into unit circle $\bbT$.
 
-Так как преобразование Кэли является трансформацией Мебиуса, оно сохраняет окружности.
-В частности, окружность с радиусом $r$ в нуле, под действием обратного преобразование Кэли перейдет в окружность с центром в $C(r)$ и радиусом $R(r)$, где:
+Another important property we are going to use is that Cayley transform preserves circles.
+In particular, a circle with radius $r < 1$ centered in zero, under inverse Cayley transform maps into a circle with center $C(r)$ and radius $R(r)$, where:
 
@@
 
-Легко заметить, что при стремлении $r$ к $1$, $R(r)$ стремится к бесконечности, а $C(r)$ стремится к $R(r)$, что естественно так как в пределе комплексная единичная окружность отображается в вещественную ось.
+From these formulas it's easy to see that if we limit $r$ to $1$, $R(r)$ goes to infinity and $C(r)$ converges to $R(r)$, which intuinively makes sense since a complex unit circle maps to a real axis.
+TODO ???
 

### 2016-12-20 chapter_1_background.tex
more background

@@
 \begin{itemize}
-\item $\bbC$ — complex plane, $\bbC = \{ x + \iu y \mid x, y \in \bbR \}$ 
-\item $\bbH$ — upper complex half-plane, $\bbH = \{ x + \iu y \mid y > 0, x, y \in \bbR \}$
-\item $\bbD$ — unit disk, $\bbD = \{ z \mid \abs{z} < 1 \}$
-\item $\bbT$ — unit circle, $\bbT = \partial \bbD =  \{z \mid \abs{z} = 1 \}$
+\item $\bbC$: complex plane, $\bbC = \{ x + \iu y \mid x, y \in \bbR \}$ 
+\item $\bbH$: upper complex half-plane, $\bbH = \{ x + \iu y \mid y > 0, x, y \in \bbR \}$
+\item $\bbD$: unit disk, $\bbD = \{ z \mid \abs{z} < 1 \}$
+\item $\bbT$: unit circle, $\bbT = \partial \bbD =  \{z \mid \abs{z} = 1 \}$
 \item $z$ denotes a complex argument on upper complex half-plane $\bbH$
@@
 \section{S-matrix}\label{sec:smatrix}
-% \mtodo{картиночку с полюсами и нулями??}
 Consider a localized one dimensional potential barrier or resonator. From the left and right we TODO BLAH BLAH
@@
 , and defines scattering properties of a potential barriers.
-
-% $S$-матрица обладает рядом интересных свойств \cite[стр.
-75]{perelomov1998quantum}, позволяющих анализировать рассеяние в квантовой системе: к примеру, $S$-матрица как функция комплексного аргумента, аналитична в верхней комплексной полуплоскости, а ее полюса соответствуют связным состояниям или резонансам.
-
-% \section{Квантовые графы}
-% Квантовый граф (англ.
-quantum graph) — широко используемая модель наносистемы \cite{kuchment2002graph, lobanov2013genetic, brown2010analysis}.
-Квантовый граф представляет из себя набор вершин и линейных, одномерных ребер, их соединяющих, или уходящих на бесконечность (можно обратиться к \autoref{fig:res_segment} в качестве простейшего примера).
-При этом на ребрах графа действует дифференциальный оператор, к примеру, оператор Шредингера свободной частицы: $-\dv[2]{\psi}{x}$, а в вершинах графа установлено граничное условие, связывающее волновые функции на смежных ребрах.
-
-% Заметим, что если граф $\Gamma$ состоит только из конечного числа ребер конечной длины, его гамильтониан имеет чисто дискретный спектр, и его собственные функции образуют полную систему в $\mcL_2(\Gamma)$.
-Если же граф $\Gamma$ представляет из себя резонатор $\Omega$ с полубесконечными ребрами, в спектре будет присутствовать непрерывная часть и резонансы, индуцированные собственными числами гамильтониана резонатора $\mcH_\Omega$.
-Резонансные состояния оператора Шредингера не принадлежат пространству $\mcL_2(\Gamma)$, однако, при сужении их на конечный домен $\Omega$, становятся квадратично интегрируемыми и лежат в пространстве $\mcL_2(\Omega)$.
-Для многих приложений интересно знать, формируют ли полную систему резонансные состояния графа $\Gamma$ в пространстве $\mcL_2(\Omega)$ резонатора.
 
@@
 
-\section{Теория Лакса-Филипса}
-Мы рассматриваем рассеяние в подходе Лакса-Филипса, кратко опишем его (подробно с ним можно ознакомиться в работах \cite{lax1990scattering,lax1976scattering}).
+\section{???}
+There is a connection between the S-matrix and the completeness of the resonant states for a scattering problem:
 
-Рассмотрим задачу Коши для волнового уравнения в области $\Gamma$:
-\begin{equation}
-\begin{aligned}
-   u''_{tt}   &= H u
-\\ u(x, 0)    &= u_0(x)
-\\ u'_t(x, 0) &= u_1(x).
-\end{aligned}
-\end{equation}
+TODO something about dissipating operator
 
-Пусть $\mathcal{E}$ — гильбертово пространство двухкомпонентных функций с конечной энергией $(u_0, u_1)$ на графе $\Gamma$:
-\[
-\norm{(u_0, u_1)}^2_{\mathcal{E}} = \frac{1}{2} \int\limits_\Gamma (\abs{u'_0}^2 + \abs{u_1}^2) dx
-\]
-, где пара $(u_0, u_1)$ называется данными Коши (англ.
-Cauchy data), а оператор $U(t)$, дающий решение этой задаче: $U(t)(u_0, u_1) = (u(x, t), u'_t(x, t))$, порождает унитарную группу $\{ U(t) \mid t \in \bbR \}$.
-Данная группа содержит два ортогональных подпространства: $D_-$ — входящее подпространство, и $D_+$ — исходящее.
-
-В теории рассеяния установлено, что существуют отображения $T_\pm: \mathcal{R} \to \mcL^2(\bbR, \bbC^2)$, такие что $T_\pm U(t) = \eexp{\iu k t T_\pm}$, которые называются исходящим (соответственно, входящим) спектральным представлением унитарной группы $U(t)$.
-Обозначим $K = \mathcal{E} \ominus (D_+ \oplus D_-)$, и рассмотрим полугруппу $Z(t) = \mcP_K U(t)|_K, t > 0$, где $\mcP_K$ — оператор проецирования на $K$.
-Пусть $B$ — генератор $Z(t)$, то есть $Z(t) = \eexp{\iu B t}$, тогда собственные вектора этого оператора и будут резонансными состояниями, а $T_- T_+^{-1}$ называется оператором рассеяния.
-Оператор рассеяния действует как умножения на матрично-значную функцию $S(k)$, и являющейся матрицей рассеяния (см.
-\autoref{sec:smatrix}).
-
-\begin{theorem}[{\cite[стр. 95]{nikol2012treatise}}]
-Пусть $S$ — внутренняя функция, тогда следущие утверждения эквивалентны:
+\begin{theorem}[{\cite[p. 95]{nikol2012treatise}}, {\cite[p. 99]{nikol2012treatise}}]
+The following statements are equivalent:
 \begin{itemize}
-\item Оператор $Z$ полный.
-\item $S$ — произведение Бляшке-Потапова.
-\end{itemize}
-\end{theorem}
-
-\begin{theorem}[{\cite[стр. 99]{nikol2012treatise}}]
-Пусть вспомогательное пространство конечномерно. Тогда, следующие утверждения эквивалентны:
-\begin{itemize}
-\item $S$ — произведение Бляшке-Потапова.
+\item the dissipating operator $Z$ is complete
 \item
@@
 \end{theorem}
-Непосредственно применяя эти теоремы, и пользуясь тем, что нашим вспомогательным пространством является $\bbC^2$, получаем, что мы можем воспользоваться данным упрощенным критерием для доказательства полноты резонансных состояний в квантовом графе.
 
-\section{Критерий сходимости}
+\section{Convergence criterion}
 
-Так как $\det S$ является скалярной внутренней функцией \cite{nikol2012treatise}, мы можем воспользоваться критерием \ref{eq:blaschke} для исследования полноты системы резонансных состояний.
-В пространстве единичного диска он будем выглядеть как:
+Next, we will use the criterion \ref{eq:blaschke} to analyse the completeness of the system of resonant states. In the space of the unit disk it looks like:
 \begin{equation}\label{eq:crit_cayley}
@@
 
-Так как $S$-матрица естественным образом определена на комплексной плоскости, иногда бывает удобнее работать с этим признаком в верхней полуплоскости $\bbH$, а не на единичном диске.
-Заменим в (\ref{eq:crit_cayley}) переменную, применив к интегралу преобразование Кэли (\ref{eq:cayley}) к дифференциалу и области интегрирования, получив:
+Since S-matrix is naturally defined on the complex plance, it makes sense to use the upper complex plane for the analysis of completeness.
+We change the variable in (\ref{eq:crit_cayley}), applying Cayley transform to the integral, which results in:
 
@@
 \end{equation}
-, где $C_r$ — образ $\abs{\zeta} = r$ относительно обратного преобразования Кэли.
-Для удобства вычислений параметризуем $C_r$ как $C_r = \{R(r) \eexp{\iu t} + \iu C(r) \mid t \in [0, 2 \pi)\}$ (см.
-\ref{eq:c_and_r}).
-Для краткости, обозначим:
+, where $C_r$ is an image of $\abs{\zeta} = r$ under the inverse Cayley transform.
+It can be parameterised as $C_r = \{R(r) \eexp{\iu t} + \iu C(r) \mid t \in [0, 2 \pi)\}$ (see \ref{eq:c_and_r}).
+For brewity, define:
 
@@
 \]
-, и, откинув константы, не влияющие на сходимость/расходимость интеграла, получаем финальную форму критерия, которой и будем пользоваться в дальнейшем:
+, and after throwing away constants which are irrelevant for convergence, we get the final form of the criterion, which we are going to use afterwards:
 

### 2016-12-20 paper.tex
More
Inline parts

@@
 
+\theoremstyle{plain}
+\newtheorem{theorem}{Теорема}
+
 \newcommand{\hilb}[1]{\mathcal{H}_{#1}}
@@
 \newcommand{\bbZ}{\mathbb{Z}}
+\newcommand{\bbH}{\mathbb{H}}
 
@@
 
-\input{bundle.tex}
+\section{Introduction}
+TODO ?????
+
+\section{Definitions}
+\begin{itemize}
+\item $\bbC$: complex plane, $\bbC = \{ x + \iu y \mid x, y \in \bbR \}$ 
+\item $\bbH$: upper complex half-plane, $\bbH = \{ x + \iu y \mid y > 0, x, y \in \bbR \}$
+\item $\bbD$: unit disk, $\bbD = \{ z \mid \abs{z} < 1 \}$
+\item $\bbT$: unit circle, $\bbT = \partial \bbD =  \{z \mid \abs{z} = 1 \}$
+\item $z$ denotes a complex argument on upper complex half-plane $\bbH$
+\item $\zeta$ denotes a complex argument on unit disk $\bbD$
+\end{itemize}
+
+\section{Schrodinger's equation}
+In this paper we are only interested in the mathematical scattering problem and not actual energies, so we define Plank's constant as $1$ and use stationary Schrodinger's equation: $H \Psi = E \Psi$.
+We are going to be interested in scattering state solutions for this equation.
+
+\section{S-matrix}\label{sec:smatrix}
+Consider a localized one dimensional potential barrier or resonator.
+From the left and right we subject in to beams of quantum particles with the wavevector $k$ (which will be a scalar in 1D case).
+Outside the potential barrier the particles behave as plane waves:
+
+\begin{equation}\label{eq:wlwl}
+\begin{aligned}
+   \psi_L(x) &= A \eexp{\iu k x} + B \eexp{-\iu k x}
+\\ \psi_R(x) &= C \eexp{\iu k x} + D \eexp{-\iu k x}
+\end{aligned}
+\end{equation}
+
+S-matrix, or scattering matrix relates the final and initial states of the system:
+\begin{equation}\label{eq:smatrix}
+\begin{pmatrix} B \\ C \end{pmatrix} = S \begin{pmatrix} A \\ D \end{pmatrix}
+\end{equation}
+, and defines scattering properties of a potential barriers.
+
+\section{Cayley transform}
+
+Cayley transform maps $\bbH$ to $\bbD$:
+\begin{equation}\label{eq:cayley}
+W(z) = \frac{z - \iu}{z + \iu}
+\end{equation}
+, inverse Cayley transform maps $\bbD$ to $\bbH$:
+\begin{equation}\label{eq:cayley_inverse}
+w(\zeta) = \iu \frac{1 + \zeta}{1 - \zeta}
+\end{equation}
+
+One notable property of the Cayley transform is that it injectively maps $\bbR$ into unit circle $\bbT$.
+
+Another important property we are going to use is that Cayley transform preserves circles.
+In particular, a circle with radius $r < 1$ centered in zero, under inverse Cayley transform maps into a circle with center $C(r)$ and radius $R(r)$, where:
+
+\begin{equation}\label{eq:c_and_r}
+\begin{aligned}
+   C(r) &= \Im \frac{w(r) + w(-r)}{2}
+\\ R(r) &= \Im \frac{w(r) - w(-r)}{2}
+\end{aligned}
+\end{equation}
+
+From these formulas it's easy to see that if we limit $r$ to $1$, $R(r)$ goes to infinity and $C(r)$ converges to $R(r)$, which intuinively makes sense since a complex unit circle maps to a real axis.
+TODO ???
+
+\section{Convergence criterion}
+There is a connection between the S-matrix and the completeness of the resonant states for a scattering problem:
+
+TODO something about dissipating operator
+
+\begin{theorem}[{\cite[p. 95]{nikol2012treatise}}, {\cite[p. 99]{nikol2012treatise}}]
+The following statements are equivalent:
+\begin{itemize}
+\item the dissipating operator $Z$ is complete
+\item
+\begin{equation}\label{eq:blaschke}
+\lim\limits_{r = 1} \int\limits_{\bbT} \log \abs{\det S(r \zeta)} d m(\zeta) = 0
+\end{equation}
+\end{itemize}
+\end{theorem}
+
+Next, we will use the criterion \ref{eq:blaschke} to analyse the completeness of the system of resonant states. In the space of the unit disk it looks like:
+\begin{equation}\label{eq:crit_cayley}
+\lim\limits_{r = 1} \int\limits_{\abs{\zeta} = r} \log \abs{\det S(\zeta)} d \zeta = 0
+\end{equation}
+
+Since S-matrix is naturally defined on the complex plance, it makes sense to use the upper complex plane for the analysis of completeness.
+We change the variable in (\ref{eq:crit_cayley}), applying Cayley transform to the integral, which results in:
+
+\begin{equation}\label{eq:crit}
+\lim\limits_{r \to 1} \int\limits_{C_r} \ln \abs{\det S(k)} \frac{2 \iu}{(k + i)^2} dk = 0
+\end{equation}
+, where $C_r$ is an image of $\abs{\zeta} = r$ under the inverse Cayley transform.
+It can be parameterised as $C_r = \{R(r) \eexp{\iu t} + \iu C(r) \mid t \in [0, 2 \pi)\}$ (see \ref{eq:c_and_r}).
+For brewity, define:
+
+\[
+s(k) = \abs{\det S(k)}
+\]
+, and after throwing away constants which are irrelevant for convergence, we get the final form of the criterion, which we are going to use afterwards:
+
+\begin{equation}\label{eq:critp}
+\lim\limits_{r \to 1} \int\limits_{0}^{2 \pi} \ln s(R(r) \eexp{\iu t} + \iu C(r)) \frac{R}{(R(r) \eexp{\iu t} + \iu C(r) + i)^2} dt = 0
+\end{equation}
+\mtodo{$C + R = \Im w(r) = \frac{1 + r}{1 - r}$, $C - R = \Im w(-r) = \frac{1 - r}{1 + r}$}
+
+\section{The model}
+% TODO http://tex.stackexchange.com/a/155317/5966 ?
+\begin{figure}
+\centering
+\begin{tikzpicture}[scale=1.1] % TODO SCALE!!!
+\input{pic/resonator_bundle.tex}
+\end{tikzpicture}
+\caption{Quantum graph $\Gamma$, consisting of semi infinite edges  $\Omega_L, \Omega_R$ and a resonator $\Omega$, consisting of $W$ identical edges of length 1.}
+\label{fig:res_bundle}
+\end{figure}
+
+Let's investigate the model on \autoref{fig:res_bundle}.
+Schrodinger's operator is defined on edges of the graph as  $-\dv[2]{\psi}{x}$.
+At the vertices $V_a$ and $V_b$ we require the wavefunction and its derivatives to be continuous:
+
+\begin{equation}\label{eq:bundle_system}
+\begin{aligned}
+   \forall i: \psi_i(0) &= \psi_L(0)
+\\ \forall i: \psi_i(1) &= \psi_R(0)
+\\ \psi'_L(0) - \sum\limits_{i = 1}^W \psi'_i(0) &= 0
+\\ -\psi'_R(0) + \sum\limits_{i = 1}^W \psi'_i(1) &= 0
+\end{aligned}
+\end{equation}
+
+\subsection{Calculation of $S$ matrix}
+After solving \ref{eq:bundle_system} в сочетании с \ref{eq:wlwl}, we get:
+\begin{equation*}
+\det S(k) = \frac{2 i \, W \cos\left(k\right) - {\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}
+\end{equation*}
+
+\begin{equation}\label{eq:bundle_s}
+s(k) = \abs{\det S(k)} = \abs{\frac{2 i \, W \cos\left(k\right) - {\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}}
+\end{equation}
+
+\mtodo{график S-матрицы?}
+
+TODO: define contour
+
+Let's fix $r$, and further, for the sake of readability, let's define $C = C(r)$ and $R = R(r)$. For each $r$, we estimate the integral and show that the sequence of estimates converges to zero.
+
+Let's use Cauchy–Schwarz's inequality:
+\[
+\big| \langle u,v \rangle \big| \leq \left\|u\right\| \left\|v\right\|
+\]
+, to be precise, it's $\mcL^2[a, b]$ version:
+\[
+\abs{
+\int\limits_{t=a}^{b} f(t) g^*(t) dt
+}
+\le
+\sqrt{\int\limits_{t=a}^b \abs{f(t)}^2 dt }
+\sqrt{\int\limits_{t=a}^b \abs{g(t)}^2 dt }
+\]
+% 
+To use inequality, we are going to represent the integrand in (\ref{eq:critp}) as $f(t) g^*(t)$ as follows:
+\begin{equation}\label{eq:split}
+\begin{aligned}
+a      &= 0 \\
+b      &= 2 \pi \\
+f(t)   &= \ln s(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
+g^*(t) &= \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
+\end{aligned}
+\end{equation}
+Next, we will show that $\norm{g}$ (that is, $\sqrt{\int \abs{g(t)}^2}$) is bounded by a constant which does not depend on $r$, and $\norm{f}$ goes to $0$ as $r$ goes to $1$, hence (\ref{eq:critp}) converges.
+
+\subsubsection{Estimate of $\norm{g}$}
+
+First, we evaluate the integrand:
+\begin{align*}
+\abs{g(t)}^2 = \abs{g^*(t)}^2
+&=   \frac{\sqrt{R}^2}{\abs{R \cos t + \iu R \sin t + \iu C + i}^2} \\
+&=   \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} \\
+&= \frac{R}{R^2 \cos^2 t + R^2 \sin^2 t + (C + 1)^2  + 2 R (C + 1) \sin t} \\
+&=   \frac{1}{R + \frac{(C + 1)^2}{R} + 2 (C + 1) \sin t} \\ 
+\end{align*}
+
+We have to integrate this function on interval $[0, 2 \pi]$. Integral of such type is well-known: (TODO REFERENCE)
+\[
+\int\limits_{0}^{2 \pi} \frac{dx}{a + b \sin x} = \frac{2 \pi}{\sqrt{a^2 - b^2}}
+\]
+, when $a > b$. In our case, $a = R + \frac{(C + 1)^2}{R}$, $b = 2 (C + 1)$).
+
+First, we check that $a > b$:
+\begin{align*}
+   R + \frac{(C + 1)^2}{R} - 2 (C + 1)
+   &= \frac{R^2 + C^2 + 2C + 1 - 2 RC - 2 R}{R}
+\\ &= \frac{(C - R)^2 + 2(C - R) + 1}{R}
+\\ &= \frac{(C - R + 1)^2 }{R}
+\\ &> 0 && \text{,strictly greater since $C > R$} 
+\end{align*}
+
+Next, we compute en estimate for $\sqrt{a^2 - b^2}$:
+\begin{align*}
+a^2 - b^2
+& =  (R + \frac{(C + 1)^2}{R})^2 - (2 (C + 1))^2\\
+& =  R^2 + \frac{(C+1)^4}{R^2} + 2 (C+1)^2 - 4 (C + 1)^2 \\
+& =  \left( \frac{(C + 1)^2}{R} - R \right)^2 \\
+& =  \left( \frac{(C + 1)^2 - R^2}{R}\right)^2 \\
+& =  \left( \frac{(C + 1 - R) (C + 1 + R)}{R}\right)^2 && \text{,since $C > R > 0$} \\
+&\ge \left( \frac{(1) (R + R)}{R}\right)^2  \\
+&\ge 4
+\end{align*}
+
+Finally, since $\frac{2 \pi}{\sqrt{a^2 - b^2}} \le \frac{2 \pi}{2} = \pi$, and we just proved that $\norm{g}$ is bounded by a constant.
+
+\subsubsection{Estimating $\int \abs{f(t)}^2$}
+Function $s(k)$ (\ref{eq:bundle_s}) is too complex for direct proof of the convergence.
+
+We proceed as follows:
+
+\begin{itemize}
+\item Since $s(k)$ is an absolute value of the determinant of the $S$ matrix, in the upper complex plane $0 \le s(k) \le 1$ holds.
+From here, we immediately know that the integral is bounded from above since TODO blah blah
+\item We replace $s(k)$ with a lower bound $l(k)$ such that: $0 \le l(k) \le s(k) \le 1$.
+\item By appling logarithm to the expression above, we get $\ln l(k) \le \ln s(k) \le 0$, and therefore, $\ln^2 s(k) \le \ln^2 l(k)$.
+\item Now, if we prove convergence for $l(k)$, this immediately proves the convergence of the original integral.
+\end{itemize}
+
+We are going to use this fact in our proof and do such function changes under the integral sign, replacing complicated function with simpler (in particular, piecewise linear) lower bounds, and then using well known facts to estimate the integral.
+
+\subsubsection{Simplifying $s(k)$}
+We build a simple estimate for $s(k)$ over the upper complex plane. This function will be independent of the complex part of its argument which will make the analysis way easier.
+
+\begin{enumerate}
+\item
+  It is easy to spot that if we fix the complex part of the argument, $s(k)$ is periodic with respect to the real part of its argument.
+% Since $\sin k$ and $\cos k$ are periodic w.r.t the real axis, with the period of $2 \pi$, 
+\mtodo{is this step really necessary?}
+\item 
+  Function $s(k)$ has countably infinite set of zeros, and each of them has $\Im k = \atanh \frac{2 W}{W^2 + 1}$. For brewity, we define:
+
+  \begin{equation*}
+  \begin{aligned}
+     V &= \frac{2 W}{W^2 + 1}
+  \\ Z &= \atanh V
+  \end{aligned}
+  \end{equation*}
+\item
+  Notice that for each $x$, $s(x + \iu y) \le s(\iu y)$. \mtodo{How to prove? We could probably take a look at numerator and denominator in separate?} 
+\end{enumerate}
+
+Given these fact, we can build a simple lower bound for $s(x + \iu y)$:
+\begin{align*}
+l(x + \iu y)
+   &= \abs{\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}}
+\\ &= \abs{\frac{\tanh y - V}{\tanh y + V}} && \text{(since $\cosh y > 0$)}
+\end{align*}
+
+It's pretty clear that $l(k)$ has a continuum of zeros over the line $\Im k = Z$, which implies that $\ln l(k)$ has continuum number of singularities over this line.
+Intuitively, it shouldn't spoil the convergence of integral since the contour of integration cound intersect the singularities of the original function anyway.
+And indeed, we will give a rigorous argument that we still can prove convergence in this case.
+Since the function is independent from the real part of the argument now, for brewity, we will omit it and defince $l(y) = l(\iu y)$.
+\mtodo{Plot?}
+
+% Так как $\tanh y$ неотрицательна и растет при $y \ge 0$, мы можем избавиться от знака модуля:
+
+% \todo{make the formula bigger}
+% \todo{get rid of it??}
+% \[
+% l(x + \iu y)
+%  = \begin{cases}
+%  \frac{V - \tanh y}{\tanh y + V}, & 0 \le y \le Z \\
+%  \frac{\tanh y - V}{\tanh y + V}, & y > Z 
+%  \end{cases}
+% \]
+
+Now, we will simplify the integral (TODO REF) using the bound we just built:
+\begin{align*}
+       \int\limits_{t=0}^{2 \pi} \abs{f(t)}^2 dt
+   = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R \eexp{\iu t} + \iu C) \frac{R}{\norm{R \eexp{\iu t} + \iu C + i}^2} dt
+\\ = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R \sin t + C) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dt
+\end{align*}
+% TODO f зависит только от Im k
+
+First, notice that:
+
+\begin{equation*}
+\begin{aligned}
+   \sin(-\pi/2 + t)   &= \sin(-\pi/2 - t) = - \cos t
+\\ \cos^2(-\pi/2 + t) &= \cos^2(-\pi/2 = t) = \sin^2 t
+\end{aligned}
+\end{equation*}
+, that is, the integrand is symmetric with respect to $y$ and for proving convergence it is enough to prove convergence on the (half circle) contour defined by $-\pi/2 \le t \le \pi/2$.
+
+Next, we do a variable change:
+\begin{equation*}
+\begin{aligned}
+   y         &= R \sin t + C
+\\ t         &= \asin \frac{y - C}{R}
+\\ dt        &= \frac{1}{\sqrt{R^2 - (C - y)^2}} dy
+\\ \cos t    &= \frac{\sqrt{R^2 - (C - y)^2}}{R}
+\\ y(-\pi/2) &= C - R 
+\\ y(\pi/2)  &= C + R 
+\end{aligned}
+\end{equation*}
+, and after substitution:
+\begin{equation}\label{eq:int_f}
+\resizebox{0.9\hsize}{!}{$
+\begin{aligned}
+    & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dy \\
+=   & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 - (C - y)^2 + (y + 1)^2} \frac{1}{\sqrt{R^2 - (C - y)^2}} dy\\
+=   & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}  dy\\
+\end{aligned}
+$}
+\end{equation}
+
+On the integration path we cross singularities at $y = C - R$, $y = Z$, $y = C + R$, and the integrand is still too complex for direct estimation.
+Let's split the integration path in multiple segments and estimate them independently.
+
+\subsubsection{Case 1: $C - R \le y \le Z$}
+A crucial property of $s(k)$ is its convergence to 1 as $\Im k$ converges to TODO ZERO??, since then $\ln s(k)$ goes to zero, which is necessary to compensate the singularity of $\frac{1}{R - C + y}$ at $y = C - R$.
+% TODO: Интуитивно, контур интегрирования становится все ближе и ближе к $\bbR$ при увеличении радиуса и если бы $\ln s(k)$ не занулялась, сходимость бы пропала.
+This implies that lower bound for $s(k)$ should also converge to $1$ as $\Im k$ goes to $0$.
+
+Since $l$ is convex when $0 \le y \le Z$, we can estimate it from below using its first derivative at $0$.
+However, this is not enough, since it will this will violate the property of the estimate being positive (it is under the logarithm sign) TODO PLOT IT, so we have to be more careful and approximate the function at $Z$ with its first derivative as well, and then glue them together at some point $Z_0$:
+\begin{align*}
+f(y)
+& = 
+\begin{cases}
+l'(0) y + 1   &, 0 \le y < Z_0  \\
+l'(Z) (y - Z) &, Z_0 \le y < Z \\
+\end{cases}
+\\
+& =
+\begin{cases}
+\frac{-2}{V} y + 1   &, 0 \le y < Z_0  \\
+\frac{1}{2 V}(V^2 - 1) (y - Z) &, Z_0 \le y < Z \\
+\end{cases}
+\end{align*}
+
+Note that lower bound does not have to be a continuous function, so we can pick any number in $[C - R, Z)$ as $Z_0$. For the ease of calculations, let's take $Z_0 = \frac{V}{4}$. \mtodo{plot?}
+
+Next we investigate integrals on $[C - R, \frac{V}{4})$ and $[\frac{V}{4}, Z)$ separately.
+
+\subsubsection{$C - R \le y < \frac{V}{4}$}
+
+Let's compute an upper bound for the integrand (\ref{eq:int_f}). Note that for $C - R \le y \le \frac{V}{4}$:
+\begin{align*}
+       & \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
+\\ \le & \ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
+% \\ \le & \ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+\end{align*}
+
+Now, we use a well known inequality which holds for $x > -1$: TODO REFERENCE
+\[
+\frac{x}{1 + x} \le \ln (1 + x)
+\]
+, where in our case $x = -\frac{2}{V} y$. Since the expression under logarithm is less than 1, we get $\ln^2 (1 + x) \le \frac{x^2}{(1 + x)^2}$:
+\begin{align*}
+       & \dots 
+\\ \le & \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V}y)^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
+\\ \le & \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V} \frac{V}{4})^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
+\\ = & \frac{\frac{4}{V^2}}{(1 - \frac{2}{V} \frac{V}{4})^2} \frac{R}{\sqrt{R + C - Z}} \frac{y^2}{R^2 - C^2 + 2 (C + 1) y + 1}  \frac{1}{\sqrt{R - C + y}}
+\end{align*}
+
+Note that we can ignore the terms dependent on $V$ only since $V$ is a constant independent of $r$.
+Now the integrand (TODO ACTUALLY ONLY ONE PART OF IT) has the form $\frac{y^2}{a + b y}$, where $a = R^2 - C^2 + 1, b = 2 (C + 1)$; when $R$ and $C$ are big enough, $a > 0$ (TODO WHY) и $b > 0$.
+That means $\frac{y^2}{a + b y}$ will be nonnegative when $y > 0$, and strictly increasing, since:
+\[
+  \left(\frac{y^2}{a + b y}\right)'
+= \frac{2y}{a + by} + y^2 \frac{-b}{(a + by)^2}
+= \frac{2y (a + by) - b y^2}{(a + by)^2}
+= \frac{y (2a + by)}{(a + by)^2}
+\ge 0
+\]
+
+This implies that we can estimate the function from above by using its value on the rightmost point of the interval at $\frac{V}{4}$.
+\[
+\frac{y^2}{a + b y} = \mcO\left(\frac{1}{R}\right)
+\]
+TODO ELABORATE ON THAT!
+
+The remaning part of integral is:
+\[
+\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} = 2 \sqrt{\frac{V}{4} - C + R} = \mcO(1)
+\]
+
+And finally, after combining all these estimages, we get $\mcO(1) \mcO(\sqrt{R}) \mcO\left(\frac{1}{R}\right) \mcO(1)  = \mcO\left(\frac{1}{\sqrt{R}}\right)$ TODO EXPAND IN TERMS OF small r!
+
+\subsubsection{$\frac{V}{4} \le y < Z$}
+
+Let's estimate the integral (\ref{eq:int_f}) from above. Note that for $\frac{V}{4} \le y < Z$:
+\begin{align*}
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}} 
+\\ \le & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}}
+\\ \le &  \frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}} \int \ln^2 \left( \frac{1}{2 V}(V^2 - 1) (y - Z) \right)
+\end{align*}
+
+$\ln^2(x)$ is integrable in the neighborhood of $x = 0$, and it is known that: %  REFTODO
+
+\[
+\int\limits_{x=x_0}^b \ln^2(a (x - b)) dx = (b - x_0) (\ln^2(a (x_0 - b)) - 2 \ln(a (x_0 - b)) + 2)
+\]
+
+In our case $x_0 = \frac{V}{4}$, $a = \frac{1}{2 V}(V^2 - 1)$, $b = Z$, and we can see that the integral is bounded by a constant independent of $R$ and $C$.
+Hence, the behaviour of the integral only dependends on the behaviour of the multiplier:
+
+\[
+\frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}} 
+\]
+
+Clearly, as $r \to \infty$, we get $R \to \infty$, $C \to \infty$, $R - C \to 0$, and we can see that the expression grows as $\mcO(\frac{1}{\sqrt{R}})$ TODO ELABORATE
+
+\subsubsection{Case 2: $y > Z$}
+When $y > Z$, 
+\[
+l(x + \iu y) 
+ = \frac{\tanh y - V}{\tanh y + V}
+ = 1 - 2 \frac{V}{\tanh y + V}
+\]
+
+% https://proofwiki.org/wiki/Inverse_of_Strictly_Increasing_Strictly_Concave_Real_Function_is_Strictly_Convex
+\mtodo{proof? just take a look at second derivative?}
+Since $l$ is concave, strictly increasing and for a fixed $r$, we are only interested at $y \le C + R$, we can estimate the function by a linear one: \mtodo{plot?}
+\[
+f(y) = \frac{l(C + R)}{C + R - Z} (y - Z)
+\]
+\mtodo{actually, even C + R is okay but whatever}
+
+Notice that when $y = C + R$, for a sufficiently big $r$, $l(y)$ is bounded from both sides by constants, independent from $C$ and $R$.
+This is because $\tanh y$ goes to $1$ as $y$ goes to infinity, therefore, $l(y)$ in the limit will be equal to $1 - \frac{2 V}{V + 1}$.
+This is an important property of this specific model, since if $l$ went to zero on infinity, this part of proof couldn't have been done (see \autoref{sec:ring}).
+
+First, not that on $Z \le y \le R + C$ the function $\frac{1}{\sqrt{R - C + y}}$ has no singularities and we can estimate integral (\ref{eq:int_f}) as:
+\begin{equation}\label{eq:int_f_up}
+\begin{aligned}
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
+\\ \le & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}} 
+\end{aligned}
+\end{equation}
+
+To estimate this expression, let's split the integration interval in three: $[Z, Z + \frac{1}{R})$, $[Z + \frac{1}{R}, C)$, $[C, C + R]$.
+
+\subsubsection{$Z \le y < Z + \frac{1}{R}$}
+
+Let's estimate (\ref{eq:int_f_up}), replacing functions in integrands by their extreme value at interval's ends:
+\begin{align*}
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+\\ \le & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}}
+\\ =   & \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}} \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \int \ln^2 f(y) 
+\end{align*}
+
+\mtodo{reference?}
+$\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy$ can be computed explicitly, using:
+\[
+    \int\limits_b^{b + c} \ln^2 (a (x - b)) dx = c (\ln^2(a c) - 2 \ln (a c) + 2)
+\]
+
+Hence, $\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy = \frac{1}{R} ( \ln^2 (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) - 2 \ln (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) + 2)$.
+As we noted above, $l(C + R)$ is bounded by constants independent on $r$, and we can clearly see that the expression grows as $\mcO(\frac{\ln^2 R}{R})$.
+Since the coefficient before the integral:
+\[
+\frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}}
+\]
+, has order of growth $\mcO\left(\frac{1}{\sqrt{R}}\right)$, it is clear that the integral on this interval goes to zero as $R, C \to \infty$.
+
+\subsubsection{$Z + \frac{1}{R} \le y < C$}
+Let's estimate (\ref{eq:int_f_up}) from above TODO again by picking extreme values blah blah:
+\begin{align*}
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+\\ \le & \int \ln^2 f(Z + \frac{1}{R}) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - C}} \frac{1}{\sqrt{R - C + Z}}
+\\  =  & \ln^2 f(Z + \frac{1}{R})  \frac{R}{\sqrt{R + C - C}} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{R^2 - C^2 + 2 (C + 1) y + 1}
+\end{align*}
+
+TODO REPLACE R BY C(R) EVERYWHERE?
+
+Antiderivative for such a function is well known:
+\[
+\int \frac{1}{a x + b} = \frac{\ln (a x + b)}{a}
+\]
+, in our case $a = 2 (C + 1)$, $b = R^2 - C^2 + 1$. Substituting the ends of the interval $(Z + \frac{1}{R}, C)$, we get the definite integral:
+\[
+\frac{\ln \frac{2 (C + 1) C + R^2 - C^2 + 1}{2 (C + 1) (Z + \frac{1}{R}) + R^2 - C^2 + 1}}{2 (C + 1)} = \mcO\left( \frac{\ln R}{R} \right)
+\]
+
+As $R$ goes to infinity, $\ln^2 f(Z + \frac{1}{R})$ goes to infinity as well, so we have to compute the order of singularity.
+Since $\ln f(Z + \frac{1}{R}) = \ln \left( \frac{l(C + R)}{C + R - Z} \frac{1}{R} \right) = \ln l(C + R) - \ln (C + R - Z) - \ln R$, we can see that $\ln^2 f(Z + \frac{1}{R}) = \mcO (\ln^2 R)$.
+
+Finally, after combining all estimates, we get: $\mcO (\ln^2 R) \mcO\left( \frac{\ln R}{R} \right) \frac{R}{\sqrt{R}} \frac{1}{\sqrt{R - C + Z}} = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)$, which means that integral goes to $0$ on this interval as $r$ goes to $1$.
+
+\subsubsection{$C \le y \le C + R$}
+
+Let's estimate (\ref{eq:int_f_up}) from above:
+\begin{align*}
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+\\ \le & \int \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+\\ =   & \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{\sqrt{R + C - y}}
+% \\  = & \ln^2 f(y) \mcO()
+\end{align*}
+
+Integral $\frac{1}{\sqrt{R + C - y}}$ from $C$ to $C + R$ is elementary and equals $2 \sqrt{R}$.
+Function $f$ at $C$ is bounded by constants not dependent on $r$, therefore, the square of its logarithm as well.
+Finally, we get an expression of order $\mcO \left( \frac{1}{R} \right) \mcO( \sqrt R ) = \mcO \left( \frac{1}{\sqrt{R}} \right)$.
+
+\subsubsection{Final estimate of $\int \abs{f(t)}^2$}
+We split our integration path in five intervals, and the integral has order:
+\[
+\mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)
+\]
+, which means that integral converges to $0$ as $r$ goes to $1$.
+
 \end{document}

### 2016-12-20 paper.tex
Less packages and macros

@@
 
-\usepackage[utf8]{inputenc}
-\usepackage[T2A]{fontenc}
-\usepackage[russian, english]{babel}
+\usepackage[english]{babel}
 
-% \usepackage{fullpage}
 \usepackage{cite}
@@
 \usepackage{tikz}
-\usepackage{xcolor} % \textcolor
-\usepackage{mathtools} % xmapsto, \Vector
 \usepackage{amsmath,amsfonts,amssymb,amsthm,amscd,amsxtra}
 \usepackage{physics}
-\usepackage[colorinlistoftodos,prependcaption,disable]{todonotes} % TODO: move to preamble!!
-\presetkeys%
-    {todonotes}%
-    {inline,backgroundcolor=red}{}
-\newcommand{\mtodo}[1]{\todo[linecolor=green!70!white, backgroundcolor=blue!20!white, bordercolor=red]{#1}}
 
 \theoremstyle{plain}
-\newtheorem{theorem}{Теорема}
-
-\newcommand{\hilb}[1]{\mathcal{H}_{#1}}
-\newcommand{\cconj}[1]{\overline{#1}}
-\newcommand{\hank}[1]{H_{#1}^{(1)}}
+\newtheorem{theorem}{Theorem}
 
@@
 \end{equation}
-\mtodo{$C + R = \Im w(r) = \frac{1 + r}{1 - r}$, $C - R = \Im w(-r) = \frac{1 - r}{1 + r}$}
+TODO: $C + R = \Im w(r) = \frac{1 + r}{1 - r}$, $C - R = \Im w(-r) = \frac{1 - r}{1 + r}$
 
@@
 \subsection{Calculation of $S$ matrix}
-After solving \ref{eq:bundle_system} в сочетании с \ref{eq:wlwl}, we get:
+After solving \ref{eq:bundle_system} in conjunction with \ref{eq:wlwl}, we get:
 \begin{equation*}
@@
 \end{equation}
-
-\mtodo{график S-матрицы?}
 
@@
 
-\subsubsection{Estimate of $\norm{g}$}
+\subsection{Estimating $\norm{g}$}
 
@@
 
-\subsubsection{Estimating $\int \abs{f(t)}^2$}
+\subsection{Estimating $\norm{f}$}
 Function $s(k)$ (\ref{eq:bundle_s}) is too complex for direct proof of the convergence.
@@
   It is easy to spot that if we fix the complex part of the argument, $s(k)$ is periodic with respect to the real part of its argument.
-% Since $\sin k$ and $\cos k$ are periodic w.r.t the real axis, with the period of $2 \pi$, 
-\mtodo{is this step really necessary?}
 \item 
@@
 \item
-  Notice that for each $x$, $s(x + \iu y) \le s(\iu y)$. \mtodo{How to prove? We could probably take a look at numerator and denominator in separate?} 
+  Notice that for each $x$, $s(x + \iu y) \le s(\iu y)$.
+  % \mtodo{How to prove? We could probably take a look at numerator and denominator in separate?} 
 \end{enumerate}
@@
 Since the function is independent from the real part of the argument now, for brewity, we will omit it and defince $l(y) = l(\iu y)$.
-\mtodo{Plot?}
-
-% Так как $\tanh y$ неотрицательна и растет при $y \ge 0$, мы можем избавиться от знака модуля:
-
-% \todo{make the formula bigger}
-% \todo{get rid of it??}
-% \[
-% l(x + \iu y)
-%  = \begin{cases}
-%  \frac{V - \tanh y}{\tanh y + V}, & 0 \le y \le Z \\
-%  \frac{\tanh y - V}{\tanh y + V}, & y > Z 
-%  \end{cases}
-% \]
+% \mtodo{Plot?}
 
@@
 \end{align*}
-% TODO f зависит только от Im k
 
@@
 A crucial property of $s(k)$ is its convergence to 1 as $\Im k$ converges to TODO ZERO??, since then $\ln s(k)$ goes to zero, which is necessary to compensate the singularity of $\frac{1}{R - C + y}$ at $y = C - R$.
-% TODO: Интуитивно, контур интегрирования становится все ближе и ближе к $\bbR$ при увеличении радиуса и если бы $\ln s(k)$ не занулялась, сходимость бы пропала.
 This implies that lower bound for $s(k)$ should also converge to $1$ as $\Im k$ goes to $0$.
@@
 
-Note that lower bound does not have to be a continuous function, so we can pick any number in $[C - R, Z)$ as $Z_0$. For the ease of calculations, let's take $Z_0 = \frac{V}{4}$. \mtodo{plot?}
+Note that lower bound does not have to be a continuous function, so we can pick any number in $[C - R, Z)$ as $Z_0$. For the ease of calculations, let's take $Z_0 = \frac{V}{4}$.  % \mtodo{plot?}
 
@@
 \\ \le & \ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
-% \\ \le & \ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
 \end{align*}
@@
 
-% https://proofwiki.org/wiki/Inverse_of_Strictly_Increasing_Strictly_Concave_Real_Function_is_Strictly_Convex
-\mtodo{proof? just take a look at second derivative?}
-Since $l$ is concave, strictly increasing and for a fixed $r$, we are only interested at $y \le C + R$, we can estimate the function by a linear one: \mtodo{plot?}
+Since $l$ is concave, strictly increasing and for a fixed $r$, we are only interested at $y \le C + R$, we can estimate the function by a linear one: % \mtodo{plot?}
 \[
@@
 \]
-\mtodo{actually, even C + R is okay but whatever}
 
@@
 
-\mtodo{reference?}
+% \mtodo{reference?}
 $\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy$ can be computed explicitly, using:

### 2016-12-20 paper.tex
Even less macros
Clean up of interval 1

@@
 \usepackage{cite}
-\usepackage{hyperref} % \url{url} \href{url}{displayed text}
+\usepackage{hyperref} % \autoref
 
@@
 \usepackage{tikz}
+
 \usepackage{amsmath,amsfonts,amssymb,amsthm,amscd,amsxtra}
-\usepackage{physics}
+\usepackage{mathtools}
 
@@
 
-\newcommand{\mcF}{\mathcal{F}}
-\newcommand{\mcH}{\mathcal{H}} % ???
-\newcommand{\mcI}{\mathcal{I}}
 \newcommand{\mcL}{\mathcal{L}} % L2 space
 \newcommand{\mcO}{\mathcal{O}} % Big O
-\newcommand{\mcP}{\mathcal{P}}
-
 \newcommand{\bbC}{\mathbb{C}} % complex plane
 \newcommand{\bbD}{\mathbb{D}} % complex unit disk
-\newcommand{\bbN}{\mathbb{N}}
-\newcommand{\bbK}{\mathbb{K}}
 \newcommand{\bbR}{\mathbb{R}}
 \newcommand{\bbT}{\mathbb{T}} % complex unit circle
-\newcommand{\bbZ}{\mathbb{Z}}
-\newcommand{\bbH}{\mathbb{H}}
+\newcommand{\bbH}{\mathbb{H}} % complex upper half plane
 
@@
 
-\newcommand{\eps}{\varepsilon}
+% \renewcommand{\Re}{\operatorname{Re}}
+% \renewcommand{\Im}{\operatorname{Im}}
+
+\newcommand{\eexp}[1]{e^{#1}}
 
@@
 \renewcommand{\Im}{\operatorname{Im}}
-\renewcommand{\phi}{\varphi} % TODO is there a prettier way to do that
-
-\newcommand{\eexp}[1]{e^{#1}}
-
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
+\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
+\DeclareMathOperator\asin{asin}
 \DeclareMathOperator\atanh{atanh}
@@
 Another important property we are going to use is that Cayley transform preserves circles.
-In particular, a circle with radius $r < 1$ centered in zero, under inverse Cayley transform maps into a circle with center $C(r)$ and radius $R(r)$, where:
+In particular, a circle with radius $r < 1$ centered in zero, under inverse Cayley transform maps into a circle with center $\iu C(r)$ and radius $R(r)$, where:
 
@@
 \begin{aligned}
-   C(r) &= \Im \frac{w(r) + w(-r)}{2}
-\\ R(r) &= \Im \frac{w(r) - w(-r)}{2}
+   C(r) &= \Im \frac{w(r) + w(-r)}{2} = \frac{1 + r^2}{1 - r^2}
+\\ R(r) &= \Im \frac{w(r) - w(-r)}{2} = \frac{2 r}{1 - r^2}
 \end{aligned}
@@
 From these formulas it's easy to see that if we limit $r$ to $1$, $R(r)$ goes to infinity and $C(r)$ converges to $R(r)$, which intuinively makes sense since a complex unit circle maps to a real axis.
-TODO ???
+
+Also, we'll note two useful facts:
+\begin{itemize}
+\item $C(r) - R(r) > 0$
+\item $C(r) - R(r) = \frac{1 - r}{1 + r} < \frac{1}{R(r)} = \frac{1 - r^2}{2 r}$, which means that $C - R$ is $\mcO(\frac{1}{R})$
+\end{itemize}
+
+% TODO: $C(r) + R(r) = \Im w(r) = \frac{1 + r}{1 - r}$, $C(r) - R(r) = \Im w(-r) = \frac{1 - r}{1 + r}$
 
@@
 \end{equation}
-TODO: $C + R = \Im w(r) = \frac{1 + r}{1 - r}$, $C - R = \Im w(-r) = \frac{1 - r}{1 + r}$
 
@@
 Let's investigate the model on \autoref{fig:res_bundle}.
-Schrodinger's operator is defined on edges of the graph as  $-\dv[2]{\psi}{x}$.
+Schrodinger's operator is defined on edges of the graph as  $-\frac{d^2 \psi}{dx^2}$.
 At the vertices $V_a$ and $V_b$ we require the wavefunction and its derivatives to be continuous:
@@
 
-Let's use Cauchy–Schwarz's inequality:
+Let's use Cauchy-Schwarz's inequality:
 \[
@@
 \begin{align*}
-       & \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
-\\ \le & \ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
+       & \int \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
+\\ \le & \int \ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
 \end{align*}
@@
        & \dots 
-\\ \le & \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V}y)^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
-\\ \le & \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V} \frac{V}{4})^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
-\\ = & \frac{\frac{4}{V^2}}{(1 - \frac{2}{V} \frac{V}{4})^2} \frac{R}{\sqrt{R + C - Z}} \frac{y^2}{R^2 - C^2 + 2 (C + 1) y + 1}  \frac{1}{\sqrt{R - C + y}}
+\\ \le & \int \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V}y)^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
+\\ \le & \int \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V} \frac{V}{4})^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
+\\ =   & \frac{\frac{4}{V^2}}{(1 - \frac{2}{V} \frac{V}{4})^2} \frac{R}{\sqrt{R + C - Z}}  \int \frac{y^2}{R^2 - C^2 + 2 (C + 1) y + 1}  \frac{1}{\sqrt{R - C + y}}
 \end{align*}
 
-Note that we can ignore the terms dependent on $V$ only since $V$ is a constant independent of $r$.
-Now the integrand (TODO ACTUALLY ONLY ONE PART OF IT) has the form $\frac{y^2}{a + b y}$, where $a = R^2 - C^2 + 1, b = 2 (C + 1)$; when $R$ and $C$ are big enough, $a > 0$ (TODO WHY) и $b > 0$.
-That means $\frac{y^2}{a + b y}$ will be nonnegative when $y > 0$, and strictly increasing, since:
+It's clear that the multiplier before the integral has order $\mcO(\sqrt{R})$ (we can ignore the terms dependent on $V$ only since $V$ is a constant independent of $r$).
+
+The first part of the integrand has the form $\frac{y^2}{a + b y}$, where $a = R^2 - C^2 + 1, b = 2 (C + 1)$; when $R$ and $C$ are big enough, $a > 0$ and $b > 0$.
+That means $\frac{y^2}{a + b y}$ will be nonnegative when $y > 0$, and non decreasing, since:
 \[
@@
 \[
-\frac{y^2}{a + b y} = \mcO\left(\frac{1}{R}\right)
-\]
-TODO ELABORATE ON THAT!
-
-The remaning part of integral is:
-\[
-\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} = 2 \sqrt{\frac{V}{4} - C + R} = \mcO(1)
+\frac{y^2}{a + b y} \le \frac{\frac{V^2}{16}}{R^2 - C^2 + 1 + 2 (C + 1) \frac{V}{4}} = \mcO\left(\frac{1}{R}\right)
 \]
 
-And finally, after combining all these estimages, we get $\mcO(1) \mcO(\sqrt{R}) \mcO\left(\frac{1}{R}\right) \mcO(1)  = \mcO\left(\frac{1}{\sqrt{R}}\right)$ TODO EXPAND IN TERMS OF small r!
+Interal of the second part of the integrand is:
+\[
+\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} = 2 \sqrt{\frac{V}{4} - (C - R)} < 2 \sqrt{\frac{V}{4}} = \mcO(1)
+\]
+
+And finally, after combining we get $\mcO(\sqrt{R}) \mcO\left(\frac{1}{R}\right) \mcO(1)  = \mcO\left(\frac{1}{\sqrt{R}}\right)$.
 

### 2016-12-20 paper.tex
Final prettification

@@
 \DeclarePairedDelimiter\norm{\lVert}{\rVert}%
+
 \DeclareMathOperator\asin{asin}
@@
 
-We have to integrate this function on interval $[0, 2 \pi]$. Integral of such type is well-known: (TODO REFERENCE)
+We have to integrate this function on interval $[0, 2 \pi]$. Integral of such type is well-known: % REFTODO
 \[
@@
 \item Since $s(k)$ is an absolute value of the determinant of the $S$ matrix, in the upper complex plane $0 \le s(k) \le 1$ holds.
-From here, we immediately know that the integral is bounded from above since TODO blah blah
+From here, we immediately know that the integral is bounded from above since $ln^2 1 = 0$.
 \item We replace $s(k)$ with a lower bound $l(k)$ such that: $0 \le l(k) \le s(k) \le 1$.
@@
 
-Given these fact, we can build a simple lower bound for $s(x + \iu y)$:
+Given these facts, we can build a simple lower bound for $s(x + \iu y)$:
 \begin{align*}
@@
 
-Now, we will simplify the integral (TODO REF) using the bound we just built:
+Now, we will simplify the integral using the bound we just constructed:
 \begin{align*}
@@
 \subsubsection{Case 1: $C - R \le y \le Z$}
-A crucial property of $s(k)$ is its convergence to 1 as $\Im k$ converges to TODO ZERO??, since then $\ln s(k)$ goes to zero, which is necessary to compensate the singularity of $\frac{1}{R - C + y}$ at $y = C - R$.
-This implies that lower bound for $s(k)$ should also converge to $1$ as $\Im k$ goes to $0$.
+A crucial property of $s(k)$ is its convergence to 1 as $\Im k$ goes to 0 (which is because $s$ is the determinant of S-matrix), since then $\ln s(k)$ goes to zero, which is necessary to compensate the singularity of $\frac{1}{R - C + y}$ at $y = C - R$.
+This means that to prove convergence using lower bound for $s(k)$, we have to require that $s(k)$ also converges to $1$ as $\Im k$ goes to $0$.
 
+% TODO plot?
 Since $l$ is convex when $0 \le y \le Z$, we can estimate it from below using its first derivative at $0$.
-However, this is not enough, since it will this will violate the property of the estimate being positive (it is under the logarithm sign) TODO PLOT IT, so we have to be more careful and approximate the function at $Z$ with its first derivative as well, and then glue them together at some point $Z_0$:
+However, this is not enough, since it will this will violate the property of the estimate being positive (it is under the logarithm sign), so we have to be more careful and approximate the function at $Z$ with its first derivative as well, and then glue them together at some point $Z_0$:
 \begin{align*}
@@
 
-Next we investigate integrals on $[C - R, \frac{V}{4})$ and $[\frac{V}{4}, Z)$ separately.
+Next we compute upper bounds for the integral \ref{eq:int_f} on $[C - R, \frac{V}{4})$ and $[\frac{V}{4}, Z)$ separately.
 
@@
 
-Let's compute an upper bound for the integrand (\ref{eq:int_f}). Note that for $C - R \le y \le \frac{V}{4}$:
+Note that for $C - R \le y \le \frac{V}{4}$:
 \begin{align*}
@@
 
-Now, we use a well known inequality which holds for $x > -1$: TODO REFERENCE
+Now, we use a well known inequality which holds for $x > -1$: % REFTODO
 \[
@@
 
-Let's estimate the integral (\ref{eq:int_f}) from above. Note that for $\frac{V}{4} \le y < Z$:
+Note that for $\frac{V}{4} \le y < Z$:
 \begin{align*}
@@
 
-$\ln^2(x)$ is integrable in the neighborhood of $x = 0$, and it is known that: %  REFTODO
+First, take a look at the multiplier before the integral, it's pretty clear it has order of growth $\mcO(\frac{1}{\sqrt{R}})$.
+
+As for the integral, $\ln^2(x)$ is integrable in the neighborhood of $x = 0$, and it is known that: %  REFTODO
 
@@
 
-In our case $x_0 = \frac{V}{4}$, $a = \frac{1}{2 V}(V^2 - 1)$, $b = Z$, and we can see that the integral is bounded by a constant independent of $R$ and $C$.
-Hence, the behaviour of the integral only dependends on the behaviour of the multiplier:
-
-\[
-\frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}} 
-\]
-
-Clearly, as $r \to \infty$, we get $R \to \infty$, $C \to \infty$, $R - C \to 0$, and we can see that the expression grows as $\mcO(\frac{1}{\sqrt{R}})$ TODO ELABORATE
+In our case $x_0 = \frac{V}{4}$, $a = \frac{1}{2 V}(V^2 - 1)$, $b = Z$, and we can see that the integral is bounded by a constant independent of $R$ and $C$, hence the integral on this interval grows as $\mcO(\frac{1}{\sqrt{R}})$.
 
@@
 
-First, not that on $Z \le y \le R + C$ the function $\frac{1}{\sqrt{R - C + y}}$ has no singularities and we can estimate integral (\ref{eq:int_f}) as:
+First, note that on $Z \le y \le R + C$ the function $\frac{1}{\sqrt{R - C + y}}$ has no singularities and we can estimate integral \ref{eq:int_f} as:
 \begin{equation}\label{eq:int_f_up}
@@
 
-To estimate this expression, let's split the integration interval in three: $[Z, Z + \frac{1}{R})$, $[Z + \frac{1}{R}, C)$, $[C, C + R]$.
+To estimate this expression, let's split the integration path in three intervals: $[Z, Z + \frac{1}{R})$, $[Z + \frac{1}{R}, C)$, $[C, C + R]$.
 
@@
 
-Let's estimate (\ref{eq:int_f_up}), replacing functions in integrands by their extreme value at interval's ends:
+Let's estimate \ref{eq:int_f_up}, replacing functions under the integral sign by their extreme value at interval's ends:
 \begin{align*}
@@
 
+It's easy to see that the coefficient before the integral has order of growth $\mcO\left(\frac{1}{\sqrt{R}}\right)$.
+
 % \mtodo{reference?}
-$\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy$ can be computed explicitly, using:
+As for the integral $\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy$, it can be computed explicitly, using:
 \[
@@
 Hence, $\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy = \frac{1}{R} ( \ln^2 (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) - 2 \ln (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) + 2)$.
-As we noted above, $l(C + R)$ is bounded by constants independent on $r$, and we can clearly see that the expression grows as $\mcO(\frac{\ln^2 R}{R})$.
-Since the coefficient before the integral:
-\[
-\frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}}
-\]
-, has order of growth $\mcO\left(\frac{1}{\sqrt{R}}\right)$, it is clear that the integral on this interval goes to zero as $R, C \to \infty$.
+As we noted above, $l(C + R)$ is bounded by positive constants less than $1$ and independent of $r$, and we can see that the expression grows as $\mcO(\frac{\ln^2 R}{R})$.
+
+By combining the estimates for the coefficient and the integral, we get $\mcO(\frac{\ln^2 R}{R \sqrt{R}})$.
 
 \subsubsection{$Z + \frac{1}{R} \le y < C$}
-Let's estimate (\ref{eq:int_f_up}) from above TODO again by picking extreme values blah blah:
+Again, by picking extreme values for the parts of integrands, we can estimate \ref{eq:int_f_up} as:
 \begin{align*}
@@
 
-TODO REPLACE R BY C(R) EVERYWHERE?
+As $R$ goes to infinity, $\ln^2 f(Z + \frac{1}{R})$ goes to infinity as well, so we have to compute the order of singularity.
+Since $\ln f(Z + \frac{1}{R}) = \ln \left( \frac{l(C + R)}{C + R - Z} \frac{1}{R} \right) = \ln l(C + R) - \ln (C + R - Z) - \ln R$, we can see that $\ln^2 f(Z + \frac{1}{R}) = \mcO (\ln^2 R)$.
 
-Antiderivative for such a function is well known:
+As for the integral, antiderivative for such a function is well known:
 \[
@@
 
-As $R$ goes to infinity, $\ln^2 f(Z + \frac{1}{R})$ goes to infinity as well, so we have to compute the order of singularity.
-Since $\ln f(Z + \frac{1}{R}) = \ln \left( \frac{l(C + R)}{C + R - Z} \frac{1}{R} \right) = \ln l(C + R) - \ln (C + R - Z) - \ln R$, we can see that $\ln^2 f(Z + \frac{1}{R}) = \mcO (\ln^2 R)$.
-
-Finally, after combining all estimates, we get: $\mcO (\ln^2 R) \mcO\left( \frac{\ln R}{R} \right) \frac{R}{\sqrt{R}} \frac{1}{\sqrt{R - C + Z}} = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)$, which means that integral goes to $0$ on this interval as $r$ goes to $1$.
+Finally, after combining, we get: $\mcO (\ln^2 R) \frac{R}{\sqrt{R}} \frac{1}{\sqrt{R - C + Z}} \mcO\left( \frac{\ln R}{R} \right)  = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)$.
 
@@
 
-Let's estimate (\ref{eq:int_f_up}) from above:
+Again, estimating \ref{eq:int_f_up} from above:
 \begin{align*}
@@
 \[
-\mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)
+\mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) +\mcO\left(\frac{\ln^2 R}{R \sqrt{R}}\right) + \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)
 \]
-, which means that integral converges to $0$ as $r$ goes to $1$.
+, which means that integral converges to $0$ as $r$ goes to $1$ and $R$ goes to $\infty$.
 

### 2016-12-20 paper_gerasimovd.tex
Less macros

--- 2016-12-20 paper.tex
@@
 \usepackage{hyperref} % \autoref
-
-\usepackage[pdftex]{graphicx}
-\graphicspath{{pic/}}
 \usepackage{tikz}
-
 \usepackage{amsmath,amsfonts,amssymb,amsthm,amscd,amsxtra}
@@
 
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}
+\newcommand{\mcO}{\mathcal{O}} % Big O
+\newcommand{\iu}{{i\mkern1mu}} % imaginary unit
+\newcommand{\eexp}[1]{e^{#1}}  % convenient exponent
 
-\newcommand{\mcL}{\mathcal{L}} % L2 space
-\newcommand{\mcO}{\mathcal{O}} % Big O
-\newcommand{\bbC}{\mathbb{C}} % complex plane
-\newcommand{\bbD}{\mathbb{D}} % complex unit disk
-\newcommand{\bbR}{\mathbb{R}}
-\newcommand{\bbT}{\mathbb{T}} % complex unit circle
-\newcommand{\bbH}{\mathbb{H}} % complex upper half plane
+\renewcommand{\Re}{\operatorname{Re}} % default Re/Im is weird
+\renewcommand{\Im}{\operatorname{Im}}
 
-% imaginary unit
-\newcommand{\iu}{{i\mkern1mu}}
-
-% \renewcommand{\Re}{\operatorname{Re}}
-% \renewcommand{\Im}{\operatorname{Im}}
-
-\newcommand{\eexp}[1]{e^{#1}}
-
-\renewcommand{\Re}{\operatorname{Re}}
-\renewcommand{\Im}{\operatorname{Im}}
 \DeclarePairedDelimiter\abs{\lvert}{\rvert}%
@@
 \begin{itemize}
-\item $\bbC$: complex plane, $\bbC = \{ x + \iu y \mid x, y \in \bbR \}$ 
-\item $\bbH$: upper complex half-plane, $\bbH = \{ x + \iu y \mid y > 0, x, y \in \bbR \}$
-\item $\bbD$: unit disk, $\bbD = \{ z \mid \abs{z} < 1 \}$
-\item $\bbT$: unit circle, $\bbT = \partial \bbD =  \{z \mid \abs{z} = 1 \}$
-\item $z$ denotes a complex argument on upper complex half-plane $\bbH$
-\item $\zeta$ denotes a complex argument on unit disk $\bbD$
+\item $\mathbb{C}$: complex plane, $\mathbb{C} = \{ x + \iu y \mid x, y \in \mathbb{R} \}$ 
+\item $\mathbb{H}$: upper complex half-plane, $\mathbb{H} = \{ x + \iu y \mid y > 0, x, y \in \mathbb{R} \}$
+\item $\mathbb{D}$: unit disk, $\mathbb{D} = \{ z \mid \abs{z} < 1 \}$
+\item $\mathbb{T}$: unit circle, $\mathbb{T} = \partial \mathbb{D} =  \{z \mid \abs{z} = 1 \}$
+\item $z$ denotes a complex argument on upper complex half-plane $\mathbb{H}$
+\item $\zeta$ denotes a complex argument on unit disk $\mathbb{D}$
 \end{itemize}
@@
 
-Cayley transform maps $\bbH$ to $\bbD$:
+Cayley transform maps $\mathbb{H}$ to $\mathbb{D}$:
 \begin{equation}\label{eq:cayley}
@@
 \end{equation}
-, inverse Cayley transform maps $\bbD$ to $\bbH$:
+, inverse Cayley transform maps $\mathbb{D}$ to $\mathbb{H}$:
 \begin{equation}\label{eq:cayley_inverse}
@@
 
-One notable property of the Cayley transform is that it injectively maps $\bbR$ into unit circle $\bbT$.
+One notable property of the Cayley transform is that it injectively maps $\mathbb{R}$ into unit circle $\mathbb{T}$.
 
@@
 
-\begin{theorem}[{\cite[p. 95]{nikol2012treatise}}, {\cite[p. 99]{nikol2012treatise}}]
+Theorem ({\cite[p. 95]{nikol2012treatise}}, {\cite[p. 99]{nikol2012treatise}}):
+
 The following statements are equivalent:
@@
 \begin{equation}\label{eq:blaschke}
-\lim\limits_{r = 1} \int\limits_{\bbT} \log \abs{\det S(r \zeta)} d m(\zeta) = 0
+\lim\limits_{r = 1} \int\limits_{\mathbb{T}} \log \abs{\det S(r \zeta)} d m(\zeta) = 0
 \end{equation}
 \end{itemize}
-\end{theorem}
 
@@
 \begin{tikzpicture}[scale=1.1] % TODO SCALE!!!
-\input{pic/resonator_bundle.tex}
+\input{resonator_bundle.tex}
 \end{tikzpicture}
@@
 \]
-, to be precise, it's $\mcL^2[a, b]$ version:
+, to be precise, it's $\mathcal{L}^2[a, b]$ version:
 \[

### 2016-12-21 cvee_paper_gerasimovd.tex
New template files

% gCOVguide.tex
% v4.0 released February 2015

\documentclass{gCOV2e}

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables

\theoremstyle{plain}% Theorem-like structures
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\begin{document}

%\jvol{00} \jnum{00} \jyear{2015} \jmonth{February}

\articletype{GUIDE}

\title{\textit{Complex Variables and Elliptic Equations} \LaTeX\ guide for authors (Style 2 + NLM reference style)}

\author{
\name{A.N. Author\textsuperscript{a}$^{\ast}$\thanks{$^\ast$Corresponding author. Email: latex.helpdesk@tandf.co.uk}
and I.T. Consultant\textsuperscript{b}}
\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton Park, Abingdon, UK;
\textsuperscript{b}Institut f\"{u}r Informatik, Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany}
\received{v4.0 released February 2015}
}

\maketitle

\begin{abstract}
This guide is for authors who are preparing papers for \textit{Complex Variables and Elliptic Equations} (\textit{gCOV})
using the \LaTeX\ document preparation system and the class file \texttt{gCOV2e.cls},
which is available via the journal's home page on the Taylor \& Francis website.
\end{abstract}

\begin{keywords}
submission instructions; source file coding; environments; references citation; fonts; numbering
\textbf{(Please provide three to six keywords taken from terms used in your manuscript)}
\end{keywords}

\begin{classcode}F1.1; F4.3 \textbf{(... for example; authors are encouraged to provide two to six 2010 Mathematics Subject Classification codes)}\end{classcode}

{\abstractfont\centerline{\bfseries Index to information contained in this guide}\vspace{12pt}
\hbox to \textwidth{\hsize\textwidth\vbox{\hsize17pc
\hspace*{-12pt} {1.}    Introduction\\
\hspace*{7pt} {1.1.}  The \textit{gCOV} document class\\
\hspace*{7pt} {1.2.}  Submission of \LaTeX\ articles\\
\hspace*{24pt}        to the journal\\
{2.}    Using the \textit{gCOV} class file\\
{3.}    Additional features\\
\hspace*{10pt}{3.1.}  Title, authors' names, abstract\\
\hspace*{24pt}        and keywords\\
\hspace*{10pt}{3.2.}  Additional footnotes to the\\
\hspace*{24pt}        title or authors' names\\
\hspace*{10pt}{3.3.}  Lists\\
{4.}    Some guidelines for using\\
\hspace*{6pt}        standard features\\
\hspace*{10pt}{4.1.}  Sections\\
\hspace*{10pt}{4.2.}  Illustrations (figures)\\
\hspace*{10pt}{4.3.}  Tables\\
\hspace*{10pt}{4.4.}  Landscape pages\\
\hspace*{10pt}{4.5.}   Theorem-like environments\\
\noindent \hspace*{7pt} {4.6.}   Typesetting mathematics\\
\hspace*{24pt} {4.6.1.}  Displayed mathematics\\
\hspace*{24pt} {4.6.2.}  Bold math italic symbols\\
\hspace*{24pt} {4.6.3.}  Bold Greek\\
\hspace*{24pt} {4.6.4.}  Upright Greek characters \\
\hspace*{47pt}            and the upright partial \\
\hspace*{47pt}            derivative sign }
\hspace{-24pt}\vbox{\noindent\hsize17pc
\hspace*{7pt} {4.7.}   Acknowledgements \\
\hspace*{7pt} {4.8.}   Disclosure \\
\hspace*{7pt} {4.9.}   Funding \\
\hspace*{7pt} {4.10.}   Notes \\
\hspace*{7pt} {4.11.}   Supplemental material \\
\hspace*{7pt} {4.12.}   References \\
\hspace*{24pt} {4.12.1.}  References cited in the \\
\hspace*{52pt}            text\\
\hspace*{24pt} {4.12.2.}  The list of references\\
\hspace*{7pt} {4.13.}   Appendices \\
{5.}    Example of a section heading \\*
\hspace*{6pt}   including {\fontencoding{T1}\scshape{small caps}}, \textit{italic}, \\
\hspace*{6pt}   and bold Greek such as ${\bm\kappa}$ \\
{6.}    \textit{gCOV} journal style \\
\hspace*{10pt}{6.1.}   Hyphens, en rules, em rules \\ \hspace*{27pt}and minus signs\\
\hspace*{10pt}{6.2.}   References \\
\hspace*{10pt}{6.3.}   Maths fonts\\
{7.}    Troubleshooting\\
{8.}    Fixes for coding problems\\
{9.}    Obtaining the \texttt{gCOV2e} class file\\
\hspace*{10pt}{9.1}  Via the Taylor \& Francis \\
\hspace*{24pt}       website\\
\hspace*{10pt}{9.2}  Via e-mail\\}}}

\section{Introduction}

In order to assist authors in the process of preparing a manuscript for \textit{Complex Variables and Elliptic Equations} (\textit{gCOV}), the journal's layout style has been implemented as a \LaTeXe\ class file based on the \texttt{article} document class. A \textsc{Bib}\TeX\ style file is also provided to assist with the formatting of your references in a style appropriate to that of the journal.

Commands that differ from or are provided in addition to the standard \LaTeXe\ interface are explained in this guide. The guide alone is not intended as a substitute for an appropriate \LaTeXe\ manual.

The \texttt{gCOVguide.tex} file can also be used as a template for composing an article for submission by cutting, pasting, inserting and
deleting text as appropriate, using the \LaTeX\ environments provided (e.g. \verb"\begin{equation}", \verb"\begin{enumerate}").

\textbf{Please note that the index following the abstract in this guide is provided for information only. An index is not required in submitted papers.}

\subsection{The \textit{gCOV} document class}\label{class}

The \textit{gCOV} class file preserves the standard \LaTeXe\ interface such that any document that can
be produced using \texttt{article.cls} can also be produced with minimal alteration using the \textit{gCOV} document class.
However, the measure (the width of the text on a page) differs from the default for \texttt{article.cls}, therefore line breaks
will change and some long equations may need to be reformatted accordingly.

If your article is accepted for publication in the journal, it will be typeset in Monotype Times. As most authors do not own this font, it is possible that the page make-up may alter slightly with the change of font. Please therefore ignore details such as slightly long lines of text, or figures and tables not appearing in exact synchronization with their citations in the text: these details will be dealt with by the typesetter during preparation of the proofs. Similarly, it is unnecessary to spend time addressing warnings in the log file -- if your .tex file compiles to produce a PDF document that correctly reflects how you wish your paper to appear, such warnings will not prevent your source files being imported into the typesetter's program.

\subsection{Submission of \LaTeX\ articles to the journal}\label{submission}

Manuscripts for possible publication in the journal should be submitted to the Editors for review as directed in the journal's Instructions for Authors, which may be found at \texttt{http://www.tandf.co.uk/journals/authors/gcovauth.asp}.

Manuscripts created using \LaTeX\ should be converted to PDF format prior to submission. The \LaTeX\ source files and any graphics files will be required in addition to the final PDF version when final, revised versions of accepted manuscripts are submitted.

`Open-source' \LaTeXe\ should be used in preference to proprietary systems such as TCILaTeX or Scientific WorkPlace; similarly, class files such as REVTeX that produce a document in the style of a different publisher or journal should not be used for preference.

Please ensure that any author-defined macros are gathered together in the preamble of your .tex file, before the
\verb"\begin{document}" command. Note that if serious problems are encountered with the coding of a paper (missing author-defined macros,
for example), it may prove necessary to divert it to conventional typesetting, i.e. it will be re-keyed.

\section{Using the \textit{gCOV} class file}

If the file \texttt{gCOV2e.cls} is not already in the appropriate system directory for \LaTeXe\ files, either
arrange for it to be put there, or simply copy it to your working folder. In order to use the \textit{gCOV} document class, replace the command
\verb"\documentclass{article}" at the beginning of your document with the command \verb"\documentclass{gCOV2e}".

The following document-class options should \emph{not} be used with the \textit{gCOV} class file:
\begin{itemize}
  \item \texttt{10pt}, \texttt{11pt}, \texttt{12pt} -- unavailable;
  \item \texttt{oneside}, \texttt{twoside} -- not necessary, oneside is the default;
  \item \texttt{leqno}, \texttt{titlepage} -- should not be used;
  \item \texttt{onecolumn} -- not necessary as it is the default style.
\end{itemize}
The \texttt{geometry} package and commands associated with it should also not be used to adjust the page dimensions.

\section{Additional features}

\subsection{Title, authors' names, abstract and keywords}

The title should be generated at the beginning of your article using the \verb"\maketitle" command.
In the final version, the author name(s) and affiliation(s) must be followed immediately by \verb"\maketitle" as shown below in order for them to be displayed in your PDF document.
To prepare an anonymous version for peer review, you can put the \verb"\maketitle" between the \verb"\title" and the \verb"\author" in order to conceal the authors' identities from the reviewers.
Next you should include an abstract, which should be enclosed within an \texttt{abstract} environment.
For example, the titles for this guide begin as follows:
\begin{verbatim}
\title{\textit{Complex Variables and Elliptic Equations} \LaTeX\
guide for authors (Style 2 + NLM reference style)}

\author{
\name{A.N. Author\textsuperscript{a}$^{\ast}$\thanks{$^\ast$Corresponding
author. Email: latex.helpdesk@tandf.co.uk}
and I.T. Consultant\textsuperscript{b}}
\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton
Park, Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik,
Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany}
\received{v4.0 released February 2015} }

\maketitle

\begin{abstract}
This guide is for authors who are preparing papers for \textit{Complex
Variables and Elliptic Equations} (\textit{gCOV}) using the \LaTeX\
document preparation system and the class file \texttt{gCOV2e.cls},
which is available via the journal's home page on the Taylor \&
Francis website.
\end{abstract}
\end{verbatim}
A list of keywords should follow the abstract, enclosed within a \texttt{keywords} environment, followed by subject classification codes enclosed within a \texttt{classcode} environment.

\subsection{Additional footnotes to the title or authors' names}

The \verb"\thanks" command may be used to produce additional footnotes to the title or authors' names if required.
Footnote symbols for this purpose should be used in the order:
$\dagger$ (coded as \verb"\dagger"), $\ddagger$ (\verb"\ddagger"), $\S$ (\verb"\S"), $\P$ (\verb"\P"), $\|$ (\verb"\|"),\break
$\dagger\dagger$ (\verb"\dagger\dagger"), $\ddagger\ddagger$ (\verb"\ddagger\ddagger"), $\S\S$ (\verb"\S\S"),
$\P\P$ (\verb"\P\P"), $\|\|$ (\verb"\|\|").

Note that any \verb"footnote"s to the main text will automatically be assigned the superscript
 symbols 1, 2, 3, etc. by the class file.\footnote{If preferred, the \texttt{endnotes} package
 may be used to set the notes at the end of your text, before the bibliography.
 The symbols will be changed to match the style of the journal if necessary by the typesetter.}

\subsection{Lists}

The \textit{gCOV} class file provides numbered and unnumbered lists using the \texttt{enumerate} environment and bulleted
lists using the \texttt{itemize} environment.

The enumerated list will number each list item with arabic numerals by default. For example,
\begin{enumerate}
  \item first item
  \item second item
  \item third item
\end{enumerate}
was produced by
\begin{verbatim}
\begin{enumerate}
  \item first item
  \item second item
  \item third item
\end{enumerate}
\end{verbatim}
Alternative numbering styles can be achieved by inserting an optional argument in square brackets to each \verb"item", e.g. \verb"\item[(i)] first item"\, to create a list numbered with roman numerals.

Unnumbered lists can also be produced using the \texttt{enumerate} environment, e.g.
\begin{enumerate}
  \item[] First unnumbered item
  \item[] Second unnumbered item
  \item[] Third unnumbered item
\end{enumerate}
was produced by
\begin{verbatim}
\begin{enumerate}
  \item[] First unnumbered item
  \item[] Second unnumbered item
  \item[] Third unnumbered item
\end{enumerate}
\end{verbatim}

Bulleted lists are provided using the \texttt{itemize} environment. For example,
\begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
\end{itemize}
was produced by
\begin{verbatim}
\begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
\end{itemize}
\end{verbatim}

\section{Some guidelines for using standard features}

The following notes are intended to help you achieve the best effects with the \texttt{gCOV2e} class file.

\subsection{Sections}

\LaTeXe\ provides five levels of section heading, all of which are defined in the \texttt{gCOV2e} class file:
\begin{enumerate}
  \item[(A)] \verb"\section"
  \item[(B)] \verb"\subsection"
  \item[(C)] \verb"\subsubsection"
  \item[(D)] \verb"\paragraph"
  \item[(E)] \verb"\subparagraph"
\end{enumerate}
Section, subsection, subsubsection and paragraph headings are numbered automatically.
If you need additional text styles in the headings, see the examples given in Section~\ref{headings}.

\subsection{Illustrations (figures)}

See `Instructions for Authors' in the journal's home page on the Taylor \& Francis website for how to submit artwork (note that requests to supply figures and tables separately from text are for the benefit of authors using Microsoft Word; authors using \LaTeX\ may incorporate these at the appropriate locations). The source files of any illustrations will be required when the final, revised version is submitted. Authors should ensure that their figures are suitable (in terms of lettering size, etc.) for the reductions they intend.

The \textit{gCOV} class file will cope with most positioning of your illustrations and you should not normally need to use the optional placement specifiers of the \texttt{figure} environment.
Figure captions should appear below the figure itself, therefore the \verb"\caption" command should appear after the figure.
For example, Figure~\ref{sample-figure} with caption and sub-captions is produced using the following commands:
\begin{verbatim}
\begin{figure}
\begin{center}
\subfigure[An example of an individual figure sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr1.eps}}}\hspace{5pt}
\subfigure[A slightly shorter sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr2.eps}}}
\caption{Example of a two-part figure with individual sub-captions
 showing that captions are flush left and justified if greater
 than one line of text, otherwise centred below the figure.}
\label{sample-figure}
\end{center}
\end{figure}
\end{verbatim}

\begin{figure}
\begin{center}
\subfigure[An example of an individual figure sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr1.eps}}}\hspace{5pt}
\subfigure[A slightly shorter sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr2.eps}}}
\caption{Example of a two-part figure with individual sub-captions
 showing that captions are flush left and justified if greater
 than one line of text, otherwise centred below the figure.}
\label{sample-figure}
\end{center}
\end{figure}

The \verb"\subfigure{}" and \verb"\includegraphics{}" commands require subfigure.sty and graphicx.sty.
The former is called in the preamble of the \texttt{gCOVguide.tex} file (in order to allow your choice of an alternative package if preferred)
and the latter by the \texttt{gCOV2e} class file; both are included with the \LaTeX\ style guide package for this journal for convenience.
Please supply any additional figure macros you use with your article in the preamble of your .tex file before \verb"\begin{document}".

To ensure that figures are correctly numbered automatically, the \verb"\label{}" command should be inserted just
after the \verb"\caption{}" command, or in its argument.

The \texttt{epstopdf} package can be used to incorporate Encapsulated PostScript (.eps) illustrations when using PDF\LaTeX, etc.
Please provide the original .eps source files rather than the generated PDF images of those illustrations for production purposes.

\subsection{Tables}

The \textit{gCOV} class file will cope with most positioning of your tables and you should not normally need to use the optional
placement specifiers of the \texttt{table} environment.

The \texttt{tabular} environment can be used as illustrated here to produce tables with appropriately spaced single thick and thin
horizontal rules, which are allowed, if desired. Thick rules should be used at the head and foot only, and thin rules elsewhere as appropriate.
Commands to redefine quantities such as \verb"\arraystretch" should be omitted.

The table caption appears above the body of the table in \textit{gCOV} style, therefore the \verb"\tbl" command should be used before the body of the table.
For example, Table~\ref{sample-table} is produced using the following commands. Note that \verb"\rm" will produce a roman character in math mode.
There are also \verb"\bf" and \verb"\it", which produce bold face and text italic in math mode.

\begin{table}
\tbl{Example of a table showing that its caption is as wide as the
 table itself and justified.}
{\begin{tabular}[l]{@{}lcccccc}\toprule
  Class$^{\rm a}$ & $\gamma _1$ & $\gamma _2$$^{\rm b}$
         & $\langle \gamma \rangle$
         & $G$ & $|{\bm f}|$ & $\theta _{c}$ \\
\colrule
  BL Lacs & 5 & 36 & 7 & $-4.0$ & $1.0\times 10^{-2}$ & 10$^\circ$ \\
  FSRQs & 5 & 40 & 11 & $-2.3$ & $0.5\times 10^{-2}$ & 14$^\circ$ \\
\botrule
\end{tabular}}
\tabnote{$^{\rm a}$This footnote shows what footnote symbols to use.}
\tabnote{$^{\rm b}$This footnote shows the text turning over when a long footnote is added.}
\label{sample-table}
\end{table}

\begin{verbatim}
\begin{table}
\tbl{Example of a table showing that its caption is as wide as the
 table itself and justified.}
{\begin{tabular}[l]{@{}lcccccc}\toprule
  Class$^{\rm a}$ & $\gamma _1$ & $\gamma _2$$^{\rm b}$
         & $\langle \gamma \rangle$
         & $G$ & $|{\bm f}|$ & $\theta _{c}$ \\
\colrule
  BL Lacs & 5 & 36 & 7 & $-4.0$ & $1.0\times 10^{-2}$ & 10$^\circ$ \\
  FSRQs & 5 & 40 & 11 & $-2.3$ & $0.5\times 10^{-2}$ & 14$^\circ$ \\
\botrule
\end{tabular}}
\tabnote{$^{\rm a}$This footnote shows what footnote symbols to use.}
\tabnote{$^{\rm b}$This footnote shows the text turning over when a
 long footnote is added.}
\label{sample-table}
\end{table}
\end{verbatim}

To ensure that tables are correctly numbered automatically, the \verb"\label{}" command should be inserted just before \verb"\end{table}".

Tables produced using the \texttt{booktabs} package of macros for typesetting tables are also compatible with the \textit{gCOV} class file.

\subsection{Landscape pages}\label{landscape}

If a table or illustration is too wide to fit the measure it will need to be turned, along with its caption, through 90$^{\circ}$ anticlockwise.
Landscape illustrations and/or tables can be produced using the \verb"rotating" package, which is called by the \textit{gCOV} class file.
The following commands (for example) can be used to produce such pages.
\begin{verbatim}
\setcounter{figure}{0}
\begin{sidewaysfigure}
\centerline{\epsfbox{figname.eps}}
\caption{Example landscape figure caption.}
\label{landfig}
\end{sidewaysfigure}
\end{verbatim}

\begin{verbatim}
\setcounter{table}{0}
\begin{sidewaystable}
 \tbl{Example landscape table caption.}
  {\begin{tabular}{@{}llllcll}
    .
    .
    .
  \end{tabular}}\label{landtab}
\end{sidewaystable}
\end{verbatim}
Before any such float environment, use the \verb"\setcounter" command as above to fix the numbering of the caption.
Subsequent captions will then be automatically renumbered accordingly.
The \verb"\epsfbox{}" command requires epsfig.sty, which is called by the \texttt{gCOV2e} class file and included with the \LaTeX\ style guide package for this journal for convenience.

\subsection{Theorem-like environments}

A predefined \verb"proof" environment is provided by the \texttt{amsthm} package (which is called by the \textit{gCOV} class file), as follows:

\begin{proof}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proof}
\noindent This was produced by simply typing:
\begin{verbatim}
\begin{proof}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proof}
\end{verbatim}
Other theorem-like environments (theorem, lemma, corollary, etc.) need to be defined as required, e.g. using \verb"\newtheorem{theorem}{Theorem}[section]"
in the preamble of your .tex file before \verb"\begin{document}". Theorem-like structures in \textit{gCOV} are generally numbered as per the following examples:

\begin{theorem}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{theorem}
\begin{lemma}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{lemma}
\begin{corollary}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{corollary}
\begin{proposition}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proposition}
\begin{definition}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{definition}
\begin{remark}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{remark}

\noindent These were defined as shown in detail in the preamble of the \texttt{gCOVguide.tex} file, and produced by typing, for example:
\begin{verbatim}
\begin{theorem}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{theorem}
\end{verbatim}
The format of the text in these environments may be changed if necessary to match the style of the journal by the typesetter during preparation of your proofs.

\subsection{Typesetting mathematics}\label{maths}

\subsubsection{Displayed mathematics}

The \textit{gCOV} class file will set displayed mathematics centred on the measure without equation numbers if the \LaTeX\ standard commands open (\verb"\[") and close (\verb"\]") square brackets are used as
delimiters. The equation
\[
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\]
\normalfont was typeset using the commands
\begin{verbatim}
\[
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\]
\end{verbatim}

For those of your equations that you wish to be automatically numbered sequentially throughout the text,
use the \texttt{equation} environment, e.g.
\begin{equation}
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\end{equation}
was typeset using the commands
\begin{verbatim}
\begin{equation}
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})quad
  i\in {\mathbb R}
\end{equation}
\end{verbatim}

Part numbers for sets of equations may be generated using the \texttt{subequations} environment, e.g.
\begin{subequations} \label{subeqnexample}
\begin{equation}
        \varepsilon \rho w_{tt}(s,t)
        =
        N[w_{s}(s,t),w_{st}(s,t)]_{s},
        \label{subeqnpart}
\end{equation}
\begin{equation}
        w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
\end{equation}
\end{subequations}
which was generated using the commands
\begin{verbatim}
\begin{subequations} \label{subeqnexample}
\begin{equation}
        \varepsilon \rho w_{tt}(s,t)
        =
        N[w_{s}(s,t),w_{st}(s,t)]_{s},
        \label{subeqnpart}
\end{equation}
\begin{equation}
        w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
\end{equation}
\end{subequations}
\end{verbatim}
This is made possible by the \texttt{subeqn} package, which is called
by the class file. If you put the \verb"\label{}" just after the
\verb"\begin{subequations}" line, references will be to the
collection of equations, `(\ref{subeqnexample})' in the example
above. Or, like the example code above, you can reference each
equation individually -- e.g. `(\ref{subeqnpart})'.

Displayed mathematics should be given end-of-line punctuation appropriate to the running text sentence of which it forms a part, if required.

\subsubsection{Bold math italic symbols}

To get bold math italic you can use \verb"\bm", which works for all sizes, e.g.
\begin{verbatim}
\sffamily
\begin{equation}
  {\rm d}({\bm s_{t_{\bm u}}) = \langle{\bm\alpha({\sf{\textbf L}})}
  [RM({\bm X}_y + {\bm s}_t) - RM({\bm x}_y)]^2 \rangle
\end{equation}
\normalfont
\end{verbatim}
produces\sffamily
\begin{equation}
  {\rm d}({\bm s_{t_{\bm u}}}) = \langle {\bm\alpha({\sf{\textbf L}})}[RM({\bm X}_y
  + {\bm s}_t) - RM({\bm x}_y)]^2 \rangle
\end{equation}\normalfont
Note that subscript, superscript, subscript to subscript, etc.
sizes will take care of themselves and are italic, not bold,
unless coded individually. \verb"\bm" produces the same effect as
\verb"\boldmath". \verb"\sffamily"...\verb"\normalfont" allows
upright sans serif fonts to be created in math mode by using the
control sequence `\verb"\sf"'.

\subsubsection{Bold Greek}\label{boldgreek}

Bold lowercase as well as uppercase Greek characters can be
obtained by \verb"{\bm \gamma}", which gives ${\bm \gamma}$, and
\verb"{\bm \Gamma}", which gives ${\bm \Gamma}$.

\subsubsection{Upright lowercase Greek characters and the upright partial derivative sign}\label{upgreek}

Upright lowercase Greek characters can be obtained with the \textit{gCOV} class file by inserting the letter `u' in the control
code for the character, e.g. \verb"\umu" and \verb"\upi" produce $\umu$ (used, for example, in the symbol for the
unit microns -- $\umu{\rm m}$) and $\upi$ (the ratio of the circumference to the diameter of a circle). Similarly,
the control code for the upright partial derivative $\upartial$ is \verb"\upartial".

\subsection{Acknowledgements}

An unnumbered section, e.g.\ \verb"\section*{Acknowledgement(s)}", should be used for thanks, etc.
and included \emph{in the non-anonymous version} before any Notes or References section.

\subsection{Disclosure}

An unnumbered section, e.g.\ \verb"\section*{Disclosure}", should be used to state any potential conflict of interest
and included \emph{in the non-anonymous version} before the References section, after any Acknowledgements and before any Funding statement.

\subsection{Funding}

An unnumbered section, e.g.\ \verb"\section*{Funding}", should be used for grant details, etc.
and included \emph{in the non-anonymous version} before any Notes or References section.

\subsection{Notes}

An unnumbered `Notes' section may be placed before the References section (if using the \verb"endnotes" package, use the command \verb"\theendnotes" where the notes are to appear instead of creating a \verb"\section").

\subsection{Supplemental material}

Supplemental material should be referenced within your article where appropriate. An unnumbered section, e.g. \verb"\section*{Supplemental material}", detailing the supplemental material available should be placed immediately before the list of references, and should include a brief description of each supplemental file.

\subsection{References}\label{refs}

\subsubsection{References cited in the text}

References should be cited in accordance with US National Library of Medicine (NLM) style (please refer to the style guide in the journal's Instructions for Authors for details). References are cited in the text by a number in square brackets (e.g. [1], [2,4,10], [11--15], not [11]--[15]), in the order in which they first appear.

Each bibliographical entry has a key, which is assigned by the author and used to refer to that entry in the text. In this document, the key \verb"neu83" in the citation form
\verb"\cite{neu83}" produces `\cite{neu83}', and the keys \verb"ed84" and \verb"aiex00" in the citation form
\verb"\cite{ed84,aiex00}" produce `\cite{ed84,aiex00}'. The citation for a range of bibliographic entries (e.g.
`\cite{Eri1984,glov00,hk97,glov86,Agu95,Holl04,Shak78,Mil93}') will automatically be produced by
\verb"\cite{Eri1984,glov00,hk97,glov86,Agu95,Holl04,Shak78,Mil93}". Optional notes may be included at the end of a citation by the use of square brackets, e.g. \verb"\cite[see][p.73-–77]{cwm73}" produces `\cite[see][p.73--77]{cwm73}'.

\subsubsection{The list of references}

References should be listed at the end of the main text in the order in which they are first cited in the text. The following list shows some references prepared in the style of the journal.

\begin{thebibliography}{99}

\bibitem{neu83}%1
Neumann M. Parallel GRASP with path-relinking for job shop scheduling. Mol
  Phys. 1983;50:841--843.

\bibitem{ed84}%2
Edwards DMF, McDonald IR. Positive bases in numerical optimization. Comput
  Optim Appl. 1984;21:169--175.

\bibitem{aiex00}%3
Aiex RM, Pierce IF, Donizetti G, von~Weber CM, Bizet G, Bach CPE, Strauss
  R, van~Beethoven L, Mozart WA, Dukas P. Computing tools for modelling
  orchestral performance. Cambridge (UK): University of Cambridge; 2000.
  Report No.: DAMTP 2000/NA10.

\bibitem{Eri1984}%4
Ericsson KA, Simon HA. Protocol analysis: verbal reports as data. Cambridge
  (MA): MIT Press; 1984.

\bibitem{glov00}%5
Glover F. Multi-start and strategic oscillation methods -- principles to exploit
  adaptive memory. In: Laguna M, Gonz\'{a}les-Velarde JL, editors. Computing
  tools for modeling, optimization and simulation: interfaces in computer
  science and operations research. 2nd ed. Vol.~2. Boston (MA): Kluwer Academic;
  2000. p. 1--24.

\bibitem{hk97}%6
Kern H. The resurgent Japanese economy and a Japan--United States free
  trade agreement. In: Lambert C, Holst G, editors. 4th International
  Conference on the Restructuring of the Economic and Political System in Japan
  and Europe; 1996 May 21--25; Milan, Italy. Singapore: World Scientific;
  1997. p. 147--156.

\bibitem{glov86}%7
Glover F. Hilbert modular forms and the Galois representations associated to
  Hilbert--Blumenthal abelian varieties [dissertation]. Cambridge (MA): Harvard
  University; 1986.

\bibitem{Agu95}%8
Agutter AJ. The linguistic significance of current British slang [unpublished
  doctoral dissertation]. Edinburgh (UK): Edinburgh University; 1995.

\bibitem{Holl04}%9
Holland M. Guide to citing internet sources. 2004~[cited~2012 Nov 4].
  Available from: http://www.bournemouth.ac.uk/library/using/guide\_to\_citing\_internet\_sourc.html.

\bibitem{Shak78}%10
Shakelford RT. Surgery of the alimentary tract. Philadelphia (PA): W.B.
Saunders; 1978. Chapter 2, Esophagoscopy; p. 29--40.

\bibitem{Mil93}%11
Miller ME. The interactive tester (version 4.0) [computer software].
  Westminster (CA): Psytek Services; 1993.

\bibitem{cwm73}%12
Misner CW. Efficient algorithms for layer assignment problems. In: Gottlob I,
  editor. Gravitation in a collapsing Universe. 2nd ed. San Francisco (CA):
  Freeman; 1973. p. 63--83. (Einstein's legacy; vol.~5).

\end{thebibliography}
\bigskip
\noindent This was produced by typing:
\begin{verbatim}
\begin{thebibliography}{99}

\bibitem{neu83}%1
Neumann M. Parallel GRASP with path-relinking for job shop
 scheduling. Mol Phys. 1983;50:841--843.

\bibitem{ed84}%2
Edwards DMF, McDonald IR. Positive bases in numerical optimization.
 Comput Optim Appl. 1984;21:169--175.

\bibitem{aiex00}%3
Aiex RM, Pierce IF, Donizetti G, von~Weber CM, Bizet G, Bach CPE,
 Strauss R, van~Beethoven L, Mozart WA, Dukas P. Computing tools
 for modelling orchestral performance. Cambridge (UK): University
 of Cambridge; 2000. Report No.: DAMTP 2000/NA10.

\bibitem{Eri1984}%4
Ericsson KA, Simon HA. Protocol analysis: verbal reports as data.
 Cambridge (MA): MIT Press; 1984.

\bibitem{glov00}%5
Glover F. Multi-start and strategic oscillation methods -- principles
 to exploit adaptive memory. In: Laguna M, Gonz\'{a}les-Velarde JL,
 editors. Computing tools for modeling, optimization and simulation:
 interfaces in computer science and operations research. 2nd ed.
 Vol.~2. Boston (MA): Kluwer Academic; 2000. p. 1--24.

\bibitem{hk97}%6
Kern H. The resurgent Japanese economy and a Japan--United States
 free trade agreement. In: Lambert C, Holst G, editors. 4th
 International Conference on the Restructuring of the Economic
 and Political System in Japan and Europe; 1996 May 21--25;
 Milan, Italy. Singapore: World Scientific; 1997. p. 147--156.

\bibitem{glov86}%7
Glover F. Hilbert modular forms and the Galois representations
 associated to Hilbert--Blumenthal abelian varieties [dissertation].
 Cambridge (MA): Harvard University; 1986.

\bibitem{Agu95}%8
Agutter AJ. The linguistic significance of current British slang
 [unpublished doctoral dissertation]. Edinburgh (UK): Edinburgh
 University; 1995.

\bibitem{Holl04}%9
Holland M. Guide to citing internet sources. 2004 [cited~2012 Nov 4].
 Available from:
 http://www.bournemouth.ac.uk/library/using/guide\_to\_citing\_internet\_sourc.html.

\bibitem{Shak78}%10
Shakelford RT. Surgery of the alimentary tract. Philadelphia (PA):
 W.B. Saunders; 1978. Chapter 2, Esophagoscopy; p. 29--40.

\bibitem{Mil93}%11
Miller ME. The interactive tester (version 4.0) [computer software].
 Westminster (CA): Psytek Services; 1993.

\bibitem{cwm73}%12
Misner CW. Efficient algorithms for layer assignment problems. In:
 Gottlob I, editor. Gravitation in a collapsing Universe. 2nd ed.
 San Francisco (CA): Freeman; 1973. p. 63--83. (Einstein's legacy;
 vol.~5).

\end{thebibliography}
\end{verbatim}
\bigskip
\noindent Each entry takes the form:
\begin{verbatim}
\bibitem{key} Bibliography entry
\end{verbatim}
where `\texttt{key}' is the tag that is to be used as an argument for the \verb"\cite{}" commands in the text of the article and \texttt{Bibliography entry} is the material that is to appear in the list of references, suitably formatted.

Instead of typing the bibliography by hand, you may prefer to create the list of references using a \textsc{Bib}\TeX\ database. Include the lines
\begin{verbatim}
\bibliographystyle{gCOV}
\bibliography{gCOVguide}
\end{verbatim}
where the list of references should appear, where \texttt{gCOV.bst} is the name of the \textsc{Bib}\TeX\ style file for this journal and \texttt{gCOVguide.bib} is the database of bibliographic details for the references section included with the \textit{gCOV} \LaTeX\ style guide package (to be replaced with the name of your own \textsc{Bib}\TeX\ database). The \LaTeX\ source file of your paper will extract from your .bib file only those references that are cited in that paper and list them in the References section of it.

Please include a copy of your .bib file and/or the final generated .bbl file among your source files if your .tex file does not contain a reference list in a \texttt{thebibliography} environment.

\subsection{Appendices}\label{appendices}

Any appendices should be placed after the list of references, beginning with the
command \verb"\appendices" followed by the command \verb"\section"
for each appendix title, e.g.
\begin{verbatim}
\appendices
\section{This is the title of the first appendix}
\section{This is the title of the second appendix}
\end{verbatim}

\noindent produces:\medskip

\noindent\textbf{Appendix A. This is the title of the first appendix}\medskip

\noindent\textbf{Appendix B. This is the title of the second appendix}\medskip

\noindent Subsections, equations, figures, tables, etc. within
appendices will then be automatically numbered as appropriate.

\section{Example of a section heading including {\fontencoding{T1}\scshape{small caps}},
   \textit{italic}, and bold Greek such as ${\bm\kappa}$}\label{headings}

The following code shows how to achieve this section heading:
\begin{verbatim}
\section{Example of a section heading including
 {\fontencoding{T1}\scshape{small caps}}, \textit{italic},
 and bold Greek such as ${\bm\kappa}$}\label{headings}
\end{verbatim}

\section{\textit{gCOV} journal style}

The notes given here relate to common style errors found in manuscripts, but are \emph{not}
intended to be exhaustive.

\subsection{Hyphens, en rules, em rules and minus signs}\label{dashes}

\begin{enumerate}
\item[(i)] Hyphens (one dash in \TeX/\LaTeX). \textit{gCOV} uses hyphens for compound adjectives (e.g.\ low-density gas, least-squares fit,
two-component model) but not for complex units or ranges, which could become cumbersome (e.g.\ 15~km~s$^{-1}$
feature, 100--200~$\umu$m observations).

\item[(ii)] en rules (two dashes in \TeX/\LaTeX). These are used (a) to denote a range (e.g.\ 1.6--2.2~$\umu$m);
(b) to denote the joining of two words of equal standing (e.g.\ Kolmogorov--Smirnov test, Herbig--Haro object);
(c) with spaces, as an alternative to parentheses (e.g.\ `the results -- assuming no temperature gradient -- are indicative of \ldots').

\item[(iii)] The em rule (three dashes in \TeX/\LaTeX) has no specified use in \textit{gCOV}.

\item[(iv)] The minus sign is produced automatically in math mode by the use of a single dash, e.g.
\begin{equation}
y_{i} \in \{-1, 1 \} \quad \forall i \in V,
\end{equation}
\noindent where $|-V|=A^2+B^2.$\medskip

\noindent is produced by
\begin{verbatim}
\begin{equation}
y_{i} \in \{-1, 1 \} \quad \forall i \in V,
\end{equation}
\noindent where $|-V|=A^2+B^2.$
\end{verbatim}

\end{enumerate}

\subsection{References}

It is important to use the correct reference style, details of which can be found in Section~\ref{refs}.

\subsection{Maths fonts}

Scalar variables should be mediumface italic (e.g.\ $s$ for speed);
vectors should be bold italic (e.g.\ $\bm v$ for velocity);
matrices should be bold roman (upright) (e.g.\ $\bf A$), and
tensors should be bold upright sans serif (e.g.\ {\sffamily{\textbf L}}).
Differential d, partial differential $\upartial$, complex i,
exponential e, superscript T for `transpose', sin, cos, tan, log, etc.,
should all be roman. Openface, or `blackboard', fonts can be used,
for example, for the integers $\mathbb Z$ and the reals $\mathbb R$.
Sub/superscripts that are physical variables should be italic,
while those that are labels should be roman (e.g.\ $C_p$, $T_{\rm eff}$).

\section{Troubleshooting}

Authors may from time to time encounter problems with the preparation
of a paper using \LaTeX\/. The appropriate action to take will depend
on the nature of the problem -- the following is intended as a guide.

\begin{enumerate}
\item[(i)] If the problem is with \LaTeX\ itself, rather than with the
actual macros, please refer to an appropriate handbook for
initial advice. If the solution cannot be found, or if you
suspect that the problem lies with the macros, then please contact
Taylor \& Francis for assistance (\texttt{latex.helpdesk@tandf.co.uk}).

\item[(ii)] Problems with page make-up (e.g.\ large spaces between paragraphs,
above headings, or below figures; figures/tables appearing out of order):
please do not attempt to remedy these using `hard' page make-up
commands -- the typesetter will deal with such problems. (You may, if you
wish, draw attention to particular problems when submitting the final version
of your paper.)

\item[(iii)] If a required font is not available at your site, allow \TeX\
to substitute the font and specify which font you require in a covering letter
accompanying your file(s).
\end{enumerate}

\section{Fixes for coding problems}

This guide has been designed to minimize the need for user-defined macros to create special symbols. Authors
are urged, wherever possible, to use the following coding rather than to create their own. This will minimize
the danger of author-defined macros being accidentally `overridden' when the paper is typeset (see
Section~\ref{maths}, `Typesetting mathematics'). In cases where it is essential to create your own macros,
these should be displayed in the preamble of your \texttt{.tex} file before \verb"\begin{document}".

\begin{enumerate}
\item[(i)] Fonts in section headings and paper titles. The following are examples
of styles that sometimes prove difficult to code.

\subsection*{Paper titles:}

\hsize380pt\bf{\noindent Generalized Flory theory at ${\bm\delta >
{\bf 50}^\circ}$}\\

    \noindent\normalfont is produced by
\begin{verbatim}
\title{Generalized Flory theory at
        ${\bm\delta > {\bfseries 50}^\circ}$}
\end{verbatim}
\bigskip

{\bf{\noindent Ion--ion correlations in H\,{\sc ii} regions}}\\

\noindent\normalfont is produced by
\begin{verbatim}
\title{Ion--ion correlations in H\,{\sc ii} regions}
\end{verbatim}

\stepcounter{enumi}

\item[(ii)] en rules, em rules, hyphens and minus signs (see Section~\ref{dashes} for
correct usage). To create the correct symbols in the sentence
\begin{quote}
The high-resolution observations were made along a line at an
angle of $-15^\circ$ (East from North) from the axis of the
jet -- which runs North--South
\end{quote}
you would use the following code:
\begin{verbatim}
The high-resolution observations were made along a line at an
angle of $-15^\circ$ (East from North) from the axis of the
jet -- which runs North--South
\end{verbatim}

\item[(iii)] Fonts in superscripts and subscripts. Subscripts and superscripts will automatically come out in the correct font
and size in a math environment (e.g. enclosed by `\verb"$"'
delimiters in running text or within \verb"\[...\]" or the
`\texttt{equation}' environment for displayed equations). You can create
the output ${\bm k_x}$ by typing \verb"${\bm k_x}$". If the
subscripts or superscripts need to be other than italic, they
should be coded individually -- see (vi) below.

\item[(iv)] Calligraphic letters ($\mathcal{UPPER\ CASE\ ONLY}$).
Normal calligraphic can be produced with \verb"\mathcal" as usual (in math mode).

\item[(v)] Automatic scaling of brackets. The codes \verb"\left" and
\verb"\right" should  be used to scale brackets automatically to
fit the equation being set. For example, to get
\[
   v = x \left( \frac{N+2}{N} \right)
\]
use the code
\begin{verbatim}
\[
   v = x \left( \frac{N+2}{N} \right)
\]
\end{verbatim}

\item[(vi)] Roman font in equations. It is often necessary to make some
symbols roman in an equation (e.g.\ units, non-variable subscripts).
For example, to get
\[
   \sigma \simeq (r/13~h^{-1}~{\rm Mpc})^{-0.9},
   \qquad \omega = \frac{N-N_{\rm s}}{N_{\rm R}}
\]
\noindent use the code
\begin{verbatim}
\[
   \sigma \simeq (r/13~h^{-1}
   ~{\rm Mpc})^{-0.9}, \qquad \omega
   =\frac{N-N_{{\rm s}}}{N_{{\rm R}}}
\]
\end{verbatim}
The \texttt{SIunits} package of macros for typesetting units is also compatible with the \texttt{gCOV2e} class file.
\end{enumerate}

\section{Obtaining the gCOV2e class file}\label{FTP}

\subsection{Via the Taylor \& Francis website}

This Guide for Authors and the \texttt{gCOV2e} class file may be obtained via the Instructions for Authors
on the Taylor \& Francis homepage for the journal.

Please note that the class file calls up the following open-source \LaTeX\ packages, which will, for convenience,
unpack with the downloaded Guide for Authors and class file: amsbsy.sty; amsfonts.sty; amsmath.sty; amssymb.sty; epsfig.sty; graphicx.sty; natbib.sty; rotating.sty.
The Guide for Authors calls for subfigure.sty, which is also supplied for convenience.

\subsection{Via e-mail}

This Guide for Authors, the class file and the associated open-source \LaTeX\ packages are also available by e-mail.
Requests should be addressed to \texttt{latex.helpdesk@tandf.co.uk} clearly stating for which journal you require the Guide for Authors and/or class file.

\end{document}

### 2016-12-21 cvee_paper_gerasimovd.tex
More stuff

@@
 
+\newcommand{\mcO}{\mathcal{O}} % Big O
+\newcommand{\iu}{{i\mkern1mu}} % imaginary unit
+\newcommand{\eexp}[1]{e^{#1}}  % convenient exponent
+
+\renewcommand{\Re}{\operatorname{Re}} % default Re/Im is weird
+\renewcommand{\Im}{\operatorname{Im}}
+
+% \DeclarePairedDelimiter\abs{\lvert}{\rvert}%
+% \DeclarePairedDelimiter\norm{\lVert}{\rVert}%
+
+\newcommand\abs[1]{\left|#1\right|}
+\DeclareMathOperator\asin{asin}
+\DeclareMathOperator\atanh{atanh}
 \begin{document}
@@
 
-In order to assist authors in the process of preparing a manuscript for \textit{Complex Variables and Elliptic Equations} (\textit{gCOV}), the journal's layout style has been implemented as a \LaTeXe\ class file based on the \texttt{article} document class.
+?????
+
+% In order to assist authors in the process of preparing a manuscript for \textit{Complex Variables and Elliptic Equations} (\textit{gCOV}), the journal's layout style has been implemented as a \LaTeXe\ class file based on the \texttt{article} document class.
 A \textsc{Bib}\TeX\ style file is also provided to assist with the formatting of your references in a style appropriate to that of the journal.
 
-Commands that differ from or are provided in addition to the standard \LaTeXe\ interface are explained in this guide.
+% Commands that differ from or are provided in addition to the standard \LaTeXe\ interface are explained in this guide.
 The guide alone is not intended as a substitute for an appropriate \LaTeXe\ manual.
 
-The \texttt{gCOVguide.tex} file can also be used as a template for composing an article for submission by cutting, pasting, inserting and
-deleting text as appropriate, using the \LaTeX\ environments provided (e.g. \verb"\begin{equation}", \verb"\begin{enumerate}").
-
-\textbf{Please note that the index following the abstract in this guide is provided for information only. An index is not required in submitted papers.}
-
-\subsection{The \textit{gCOV} document class}\label{class}
-
-The \textit{gCOV} class file preserves the standard \LaTeXe\ interface such that any document that can
-be produced using \texttt{article.cls} can also be produced with minimal alteration using the \textit{gCOV} document class.
-However, the measure (the width of the text on a page) differs from the default for \texttt{article.cls}, therefore line breaks
-will change and some long equations may need to be reformatted accordingly.
-
-If your article is accepted for publication in the journal, it will be typeset in Monotype Times.
-As most authors do not own this font, it is possible that the page make-up may alter slightly with the change of font.
-Please therefore ignore details such as slightly long lines of text, or figures and tables not appearing in exact synchronization with their citations in the text: these details will be dealt with by the typesetter during preparation of the proofs.
-Similarly, it is unnecessary to spend time addressing warnings in the log file -- if your .tex file compiles to produce a PDF document that correctly reflects how you wish your paper to appear, such warnings will not prevent your source files being imported into the typesetter's program.
-
-\subsection{Submission of \LaTeX\ articles to the journal}\label{submission}
-
-Manuscripts for possible publication in the journal should be submitted to the Editors for review as directed in the journal's Instructions for Authors, which may be found at \texttt{http://www.tandf.co.uk/journals/authors/gcovauth.asp}.
-
-Manuscripts created using \LaTeX\ should be converted to PDF format prior to submission.
-The \LaTeX\ source files and any graphics files will be required in addition to the final PDF version when final, revised versions of accepted manuscripts are submitted.
-
-`Open-source' \LaTeXe\ should be used in preference to proprietary systems such as TCILaTeX or Scientific WorkPlace; similarly, class files such as REVTeX that produce a document in the style of a different publisher or journal should not be used for preference.
-
-Please ensure that any author-defined macros are gathered together in the preamble of your .tex file, before the
-\verb"\begin{document}" command. Note that if serious problems are encountered with the coding of a paper (missing author-defined macros,
-for example), it may prove necessary to divert it to conventional typesetting, i.e. it will be re-keyed.
+% The \texttt{gCOVguide.tex} file can also be used as a template for composing an article for submission by cutting, pasting, inserting and
+% deleting text as appropriate, using the \LaTeX\ environments provided (e.g. \verb"\begin{equation}", \verb"\begin{enumerate}").
+
+% \textbf{Please note that the index following the abstract in this guide is provided for information only. An index is not required in submitted papers.}
+
+\section{Definitions and notation}
+
+\subsection{Notation}
+
+\begin{itemize}
+\item $\mathbb{C}$: complex plane, $\mathbb{C} = \{ x + \iu y \mid x, y \in \mathbb{R} \}$ 
+\item $\mathbb{H}$: upper complex half-plane, $\mathbb{H} = \{ x + \iu y \mid y > 0, x, y \in \mathbb{R} \}$
+\item $\mathbb{D}$: unit disk, $\mathbb{D} = \{ z \mid \abs{z} < 1 \}$
+\item $\mathbb{T}$: unit circle, $\mathbb{T} = \partial \mathbb{D} =  \{z \mid \abs{z} = 1 \}$
+\item $z$ denotes a complex argument on complex plane $\mathbb{C}$
+\item $\zeta$ denotes a complex argument on unit disk $\mathbb{D}$
+\end{itemize}
+
+\subsection{Cayley transform}
+
+Cayley transform maps $\mathbb{H}$ to $\mathbb{D}$:
+\begin{equation}\label{eq:cayley}
+W(z) = \frac{z - \iu}{z + \iu}
+\end{equation}
+, whereas inverse Cayley transform maps $\mathbb{D}$ to $\mathbb{H}$:
+\begin{equation}\label{eq:cayley_inverse}
+w(\zeta) = \iu \frac{1 + \zeta}{1 - \zeta}
+\end{equation}
+
+One notable property of the Cayley transform is that it injectively maps $\mathbb{R}$ into unit circle $\mathbb{T}$.
+
+Another important property we are going to use is that Cayley transform preserves circles.
+In particular, a circle with radius $r < 1$ centered in zero, under inverse Cayley transform maps into a circle with center $\iu C(r)$ and radius $R(r)$, where:
+
+\begin{equation}\label{eq:c_and_r}
+\begin{aligned}
+   C(r) &= \Im \frac{w(r) + w(-r)}{2} = \frac{1 + r^2}{1 - r^2}
+\\ R(r) &= \Im \frac{w(r) - w(-r)}{2} = \frac{2 r}{1 - r^2}
+\end{aligned}
+\end{equation}
+
+From these formulas it's easy to see that if we limit $r$ to $1$, $R(r)$ goes to infinity and $C(r)$ converges to $R(r)$.
+
+Also, we'll note two useful facts:
+\begin{itemize}
+\item $C(r) - R(r) > 0$
+\item $C(r) - R(r) = \frac{1 - r}{1 + r} < \frac{1}{R(r)} = \frac{1 - r^2}{2 r}$, which means that $C - R$ is $\mcO(\frac{1}{R})$
+\end{itemize}
+
+\subsection{S-matrix}\label{sec:smatrix}
+Consider a localized one dimensional potential barrier or resonator.
+We assume that the system evolves under the stationary Schrodinger's equation.
+Since we are only interested in the mathematical scattering problem and scattering state solutions, we set Plank's constant to $1$.
+
+From the left and right we subject in to beams of quantum particles with the wavevector $k$, which will be a scalar in 1D case. Outside the potential barrier the particles behave as plane waves:
+
+\begin{equation}\label{eq:wlwl}
+\begin{aligned}
+   \psi_L(x) &= A \eexp{\iu k x} + B \eexp{-\iu k x}
+\\ \psi_R(x) &= C \eexp{\iu k x} + D \eexp{-\iu k x}
+\end{aligned}
+\end{equation}
+
+S-matrix, or scattering matrix relates the final and initial states of the system:
+\begin{equation}\label{eq:smatrix}
+\begin{pmatrix} B \\ C \end{pmatrix} = S \begin{pmatrix} A \\ D \end{pmatrix}
+\end{equation}
+, and defines scattering properties of a potential barrier.
+
+\section{Convergence criterion}
+There is a connection between the S-matrix and the completeness of the resonant states for a scattering problem:
+
+TODO something about dissipating operator
+
+\begin{theorem}[{\cite[p. 95]{nikol2012treatise}}, {\cite[p. 99]{nikol2012treatise}}]
+The following statements are equivalent:
+\begin{itemize}
+\item the dissipating operator $Z$ is complete
+\item
+\begin{equation}\label{eq:blaschke}
+\lim\limits_{r = 1} \int\limits_{\mathbb{T}} \log \abs{\det S(r \zeta)} d m(\zeta) = 0
+\end{equation}
+\end{itemize}
+\end{theorem}
+
+We will use the criterion (\ref{eq:blaschke}) to analyse the completeness of the system of resonant states. In the space of the unit disk it looks like:
+\begin{equation}\label{eq:crit_cayley}
+\lim\limits_{r = 1} \int\limits_{\abs{\zeta} = r} \log \abs{\det S(\zeta)} d \zeta = 0
+\end{equation}
+
+Since S-matrix is naturally defined on the complex plance, it makes sense to use the upper complex plane for the analysis of completeness.
+We change the variable in (\ref{eq:crit_cayley}), applying Cayley transform to the integral, which results in:
+
+\begin{equation}\label{eq:crit}
+\lim\limits_{r \to 1} \int\limits_{C_r} \ln \abs{\det S(k)} \frac{2 \iu}{(k + i)^2} dk = 0
+\end{equation}
+, where $C_r$ is an image of $\abs{\zeta} = r$ under the inverse Cayley transform.
+It can be parameterised as $C_r = \{R(r) \eexp{\iu t} + \iu C(r) \mid t \in [0, 2 \pi)\}$ (see \ref{eq:c_and_r}).
+For brevity, define:
+
+\[
+s(k) = \abs{\det S(k)}
+\]
+, and after throwing away constants which are irrelevant for convergence, we get the final form of the criterion, which is convenient for us and will be used afterwards:
+
+\begin{equation}\label{eq:critp}
+\lim\limits_{r \to 1} \int\limits_{0}^{2 \pi} \ln s(R(r) \eexp{\iu t} + \iu C(r)) \frac{R}{(R(r) \eexp{\iu t} + \iu C(r) + i)^2} dt = 0
+\end{equation}
+
+\section{Description of model}
+
+\section{Proof of completeness of resonant states}
 

### 2016-12-21 cvee_paper_gerasimovd.tex
CVEE template

@@
 \newcommand{\eexp}[1]{e^{#1}}  % convenient exponent
-
 \renewcommand{\Re}{\operatorname{Re}} % default Re/Im is weird
 \renewcommand{\Im}{\operatorname{Im}}
-
-% \DeclarePairedDelimiter\abs{\lvert}{\rvert}%
-% \DeclarePairedDelimiter\norm{\lVert}{\rVert}%
-
 \newcommand\abs[1]{\left|#1\right|}
+\newcommand\norm[1]{\left\|#1\right\|}
 \DeclareMathOperator\asin{asin}
@@
 
-% In order to assist authors in the process of preparing a manuscript for \textit{Complex Variables and Elliptic Equations} (\textit{gCOV}), the journal's layout style has been implemented as a \LaTeXe\ class file based on the \texttt{article} document class.
-A \textsc{Bib}\TeX\ style file is also provided to assist with the formatting of your references in a style appropriate to that of the journal.
-
-% Commands that differ from or are provided in addition to the standard \LaTeXe\ interface are explained in this guide.
-The guide alone is not intended as a substitute for an appropriate \LaTeXe\ manual.
-
-% The \texttt{gCOVguide.tex} file can also be used as a template for composing an article for submission by cutting, pasting, inserting and
-% deleting text as appropriate, using the \LaTeX\ environments provided (e.g. \verb"\begin{equation}", \verb"\begin{enumerate}").
-
-% \textbf{Please note that the index following the abstract in this guide is provided for information only. An index is not required in submitted papers.}
-
 \section{Definitions and notation}
@@
 
-\begin{theorem}[{\cite[p. 95]{nikol2012treatise}}, {\cite[p. 99]{nikol2012treatise}}]
+\begin{theorem}[{\cite[p. 95, 99]{nikol2012treatise}}]
 The following statements are equivalent:
@@
 
-\section{Proof of completeness of resonant states}
-
-\section{Using the \textit{gCOV} class file}
-
-If the file \texttt{gCOV2e.cls} is not already in the appropriate system directory for \LaTeXe\ files, either
-arrange for it to be put there, or simply copy it to your working folder. In order to use the \textit{gCOV} document class, replace the command
-\verb"\documentclass{article}" at the beginning of your document with the command \verb"\documentclass{gCOV2e}".
-
-The following document-class options should \emph{not} be used with the \textit{gCOV} class file:
-\begin{itemize}
-  \item \texttt{10pt}, \texttt{11pt}, \texttt{12pt} -- unavailable;
-  \item \texttt{oneside}, \texttt{twoside} -- not necessary, oneside is the default;
-  \item \texttt{leqno}, \texttt{titlepage} -- should not be used;
-  \item \texttt{onecolumn} -- not necessary as it is the default style.
-\end{itemize}
-The \texttt{geometry} package and commands associated with it should also not be used to adjust the page dimensions.
-
-\section{Additional features}
-
-\subsection{Title, authors' names, abstract and keywords}
-
-The title should be generated at the beginning of your article using the \verb"\maketitle" command.
-In the final version, the author name(s) and affiliation(s) must be followed immediately by \verb"\maketitle" as shown below in order for them to be displayed in your PDF document.
-To prepare an anonymous version for peer review, you can put the \verb"\maketitle" between the \verb"\title" and the \verb"\author" in order to conceal the authors' identities from the reviewers.
-Next you should include an abstract, which should be enclosed within an \texttt{abstract} environment.
-For example, the titles for this guide begin as follows:
-\begin{verbatim}
-\title{\textit{Complex Variables and Elliptic Equations} \LaTeX\
-guide for authors (Style 2 + NLM reference style)}
-
-\author{
-\name{A.N. Author\textsuperscript{a}$^{\ast}$\thanks{$^\ast$Corresponding
-author. Email: latex.helpdesk@tandf.co.uk}
-and I.T. Consultant\textsuperscript{b}}
-\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton
-Park, Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik,
-Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany}
-\received{v4.0 released February 2015} }
-
-\maketitle
-
-\begin{abstract}
-This guide is for authors who are preparing papers for \textit{Complex
-Variables and Elliptic Equations} (\textit{gCOV}) using the \LaTeX\
-document preparation system and the class file \texttt{gCOV2e.cls},
-which is available via the journal's home page on the Taylor \&
-Francis website.
-\end{abstract}
-\end{verbatim}
-A list of keywords should follow the abstract, enclosed within a \texttt{keywords} environment, followed by subject classification codes enclosed within a \texttt{classcode} environment.
-
-\subsection{Additional footnotes to the title or authors' names}
-
-The \verb"\thanks" command may be used to produce additional footnotes to the title or authors' names if required.
-Footnote symbols for this purpose should be used in the order:
-$\dagger$ (coded as \verb"\dagger"), $\ddagger$ (\verb"\ddagger"), $\S$ (\verb"\S"), $\P$ (\verb"\P"), $\|$ (\verb"\|"),\break
-$\dagger\dagger$ (\verb"\dagger\dagger"), $\ddagger\ddagger$ (\verb"\ddagger\ddagger"), $\S\S$ (\verb"\S\S"),
-$\P\P$ (\verb"\P\P"), $\|\|$ (\verb"\|\|").
-
-Note that any \verb"footnote"s to the main text will automatically be assigned the superscript
- symbols 1, 2, 3, etc. by the class file.\footnote{If preferred, the \texttt{endnotes} package
- may be used to set the notes at the end of your text, before the bibliography.
- The symbols will be changed to match the style of the journal if necessary by the typesetter.}
-
-\subsection{Lists}
-
-The \textit{gCOV} class file provides numbered and unnumbered lists using the \texttt{enumerate} environment and bulleted
-lists using the \texttt{itemize} environment.
-
-The enumerated list will number each list item with arabic numerals by default. For example,
-\begin{enumerate}
-  \item first item
-  \item second item
-  \item third item
-\end{enumerate}
-was produced by
-\begin{verbatim}
-\begin{enumerate}
-  \item first item
-  \item second item
-  \item third item
-\end{enumerate}
-\end{verbatim}
-Alternative numbering styles can be achieved by inserting an optional argument in square brackets to each \verb"item", e.g.
-\verb"\item[(i)] first item"\, to create a list numbered with roman numerals.
-
-Unnumbered lists can also be produced using the \texttt{enumerate} environment, e.g.
-\begin{enumerate}
-  \item[] First unnumbered item
-  \item[] Second unnumbered item
-  \item[] Third unnumbered item
-\end{enumerate}
-was produced by
-\begin{verbatim}
-\begin{enumerate}
-  \item[] First unnumbered item
-  \item[] Second unnumbered item
-  \item[] Third unnumbered item
-\end{enumerate}
-\end{verbatim}
-
-Bulleted lists are provided using the \texttt{itemize} environment. For example,
-\begin{itemize}
-  \item First bulleted item
-  \item Second bulleted item
-  \item Third bulleted item
-\end{itemize}
-was produced by
-\begin{verbatim}
-\begin{itemize}
-  \item First bulleted item
-  \item Second bulleted item
-  \item Third bulleted item
-\end{itemize}
-\end{verbatim}
-
-\section{Some guidelines for using standard features}
-
-The following notes are intended to help you achieve the best effects with the \texttt{gCOV2e} class file.
-
-\subsection{Sections}
-
-\LaTeXe\ provides five levels of section heading, all of which are defined in the \texttt{gCOV2e} class file:
-\begin{enumerate}
-  \item[(A)] \verb"\section"
-  \item[(B)] \verb"\subsection"
-  \item[(C)] \verb"\subsubsection"
-  \item[(D)] \verb"\paragraph"
-  \item[(E)] \verb"\subparagraph"
-\end{enumerate}
-Section, subsection, subsubsection and paragraph headings are numbered automatically.
-If you need additional text styles in the headings, see the examples given in Section~\ref{headings}.
-
-\subsection{Illustrations (figures)}
-
-See `Instructions for Authors' in the journal's home page on the Taylor \& Francis website for how to submit artwork (note that requests to supply figures and tables separately from text are for the benefit of authors using Microsoft Word; authors using \LaTeX\ may incorporate these at the appropriate locations).
-The source files of any illustrations will be required when the final, revised version is submitted.
-Authors should ensure that their figures are suitable (in terms of lettering size, etc.) for the reductions they intend.
-
-The \textit{gCOV} class file will cope with most positioning of your illustrations and you should not normally need to use the optional placement specifiers of the \texttt{figure} environment.
-Figure captions should appear below the figure itself, therefore the \verb"\caption" command should appear after the figure.
-For example, Figure~\ref{sample-figure} with caption and sub-captions is produced using the following commands:
-\begin{verbatim}
-\begin{figure}
+\begin{figure}[htbp]
 \begin{center}
-\subfigure[An example of an individual figure sub-caption.]{
-\resizebox*{5cm}{!}{\includegraphics{senu_gr1.eps}}}\hspace{5pt}
-\subfigure[A slightly shorter sub-caption.]{
-\resizebox*{5cm}{!}{\includegraphics{senu_gr2.eps}}}
-\caption{Example of a two-part figure with individual sub-captions
- showing that captions are flush left and justified if greater
- than one line of text, otherwise centred below the figure.}
-\label{sample-figure}
-\end{center}
-\end{figure}
-\end{verbatim}
-
-\begin{figure}
-\begin{center}
-\subfigure[An example of an individual figure sub-caption.]{
-\resizebox*{5cm}{!}{\includegraphics{senu_gr1.eps}}}\hspace{5pt}
-\subfigure[A slightly shorter sub-caption.]{
-\resizebox*{5cm}{!}{\includegraphics{senu_gr2.eps}}}
-\caption{Example of a two-part figure with individual sub-captions
- showing that captions are flush left and justified if greater
- than one line of text, otherwise centred below the figure.}
-\label{sample-figure}
+\includegraphics[trim=0 670 155 0,clip,width=\textwidth]{resonator_bundle.eps}
+\caption{Quantum graph $\Gamma$, consisting of semi infinite edges $\Omega_L, \Omega_R$ 
+and a resonator $\Omega$, consisting of $W$ identical edges of length 1.}
+\label{fig:res_bundle}
 \end{center}
@@
 
-The \verb"\subfigure{}" and \verb"\includegraphics{}" commands require subfigure.sty and graphicx.sty.
-The former is called in the preamble of the \texttt{gCOVguide.tex} file (in order to allow your choice of an alternative package if preferred)
-and the latter by the \texttt{gCOV2e} class file; both are included with the \LaTeX\ style guide package for this journal for convenience.
-Please supply any additional figure macros you use with your article in the preamble of your .tex file before \verb"\begin{document}".
+Let's investigate the model on Figure~\ref{fig:res_bundle}.
+Schrodinger's operator is defined on the edges of the graph as  $-\frac{d^2 \psi}{dx^2}$.
+At the vertices $V_a$ and $V_b$ we require the wavefunction and its derivatives to be continuous:
 
-To ensure that figures are correctly numbered automatically, the \verb"\label{}" command should be inserted just
-after the \verb"\caption{}" command, or in its argument.
+\begin{equation}\label{eq:bundle_system}
+\begin{aligned}
+   \forall i: \psi_i(0) &= \psi_L(0)
+\\ \forall i: \psi_i(1) &= \psi_R(0)
+\\ \psi'_L(0) - \sum\limits_{i = 1}^W \psi'_i(0) &= 0
+\\ -\psi'_R(0) + \sum\limits_{i = 1}^W \psi'_i(1) &= 0
+\end{aligned}
+\end{equation}
 
-The \texttt{epstopdf} package can be used to incorporate Encapsulated PostScript (.eps) illustrations when using PDF\LaTeX, etc.
-Please provide the original .eps source files rather than the generated PDF images of those illustrations for production purposes.
+After solving (\ref{eq:bundle_system}) in conjunction with (\ref{eq:wlwl}), we get:
+\begin{equation*}
+\det S(k) = \frac{2 i \, W \cos\left(k\right) - {\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}
+\end{equation*}
 
-\subsection{Tables}
+\section{Proof of completeness of resonant states}
+Using the S-matrix obtained above, we get:
 
-The \textit{gCOV} class file will cope with most positioning of your tables and you should not normally need to use the optional
-placement specifiers of the \texttt{table} environment.
+\begin{equation}\label{eq:bundle_s}
+s(k) = \abs{\det S(k)} = \abs{\frac{2 i \, W \cos\left(k\right) - {\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}}
+\end{equation}
 
-The \texttt{tabular} environment can be used as illustrated here to produce tables with appropriately spaced single thick and thin
-horizontal rules, which are allowed, if desired. Thick rules should be used at the head and foot only, and thin rules elsewhere as appropriate.
-Commands to redefine quantities such as \verb"\arraystretch" should be omitted.
+To prove completeness, we have to show that the criterion (\ref{eq:critp}) holds for this function.
+We will treat the integral as a function of $R$ and give it an upper bound such that it vanishes as $r \to 1$ and $R \to \infty$, which means that the integral vanishes as well, hence the completeness of resonant states.
 
-The table caption appears above the body of the table in \textit{gCOV} style, therefore the \verb"\tbl" command should be used before the body of the table.
-For example, Table~\ref{sample-table} is produced using the following commands. Note that \verb"\rm" will produce a roman character in math mode.
-There are also \verb"\bf" and \verb"\it", which produce bold face and text italic in math mode.
+Now, let's fix $r$, and further, for the sake of readability, we define $C = C(r)$ and $R = R(r)$.
 
-\begin{table}
-\tbl{Example of a table showing that its caption is as wide as the
- table itself and justified.}
-{\begin{tabular}[l]{@{}lcccccc}\toprule
-  Class$^{\rm a}$ & $\gamma _1$ & $\gamma _2$$^{\rm b}$
-         & $\langle \gamma \rangle$
-         & $G$ & $|{\bm f}|$ & $\theta _{c}$ \\
-\colrule
-  BL Lacs & 5 & 36 & 7 & $-4.0$ & $1.0\times 10^{-2}$ & 10$^\circ$ \\
-  FSRQs & 5 & 40 & 11 & $-2.3$ & $0.5\times 10^{-2}$ & 14$^\circ$ \\
-\botrule
-\end{tabular}}
-\tabnote{$^{\rm a}$This footnote shows what footnote symbols to use.}
-\tabnote{$^{\rm b}$This footnote shows the text turning over when a long footnote is added.}
-\label{sample-table}
-\end{table}
+To estimate, we need the Cauchy-Schwarz's inequality:
+\[
+\big| \langle u,v \rangle \big| \leq \left\|u\right\| \left\|v\right\|
+\]
+, or to be precise, it's $\mathcal{L}^2[a, b]$ version:
+\[
+\abs{
+\int\limits_{t=a}^{b} f(t) g^*(t) dt
+}
+\le
+\sqrt{\int\limits_{t=a}^b \abs{f(t)}^2 dt }
+\sqrt{\int\limits_{t=a}^b \abs{g(t)}^2 dt }
+\]
+% 
+To use inequality, we are going to represent the integrand in (\ref{eq:critp}) as $f(t) g^*(t)$ as follows:
+\begin{equation}\label{eq:split}
+\begin{aligned}
+a      &= 0 \\
+b      &= 2 \pi \\
+f(t)   &= \ln s(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
+g^*(t) &= \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
+\end{aligned}
+\end{equation}
+Next, we will show that $\norm{g}$ (that is, $\sqrt{\int \abs{g(t)}^2}$) is bounded by a constant which does not depend on $r$, and $\norm{f}$ goes to $0$ as $r$ goes to $1$, hence (\ref{eq:critp}) converges.
 
-\begin{verbatim}
-\begin{table}
-\tbl{Example of a table showing that its caption is as wide as the
- table itself and justified.}
-{\begin{tabular}[l]{@{}lcccccc}\toprule
-  Class$^{\rm a}$ & $\gamma _1$ & $\gamma _2$$^{\rm b}$
-         & $\langle \gamma \rangle$
-         & $G$ & $|{\bm f}|$ & $\theta _{c}$ \\
-\colrule
-  BL Lacs & 5 & 36 & 7 & $-4.0$ & $1.0\times 10^{-2}$ & 10$^\circ$ \\
-  FSRQs & 5 & 40 & 11 & $-2.3$ & $0.5\times 10^{-2}$ & 14$^\circ$ \\
-\botrule
-\end{tabular}}
-\tabnote{$^{\rm a}$This footnote shows what footnote symbols to use.}
-\tabnote{$^{\rm b}$This footnote shows the text turning over when a
- long footnote is added.}
-\label{sample-table}
-\end{table}
-\end{verbatim}
+\subsection{Estimating $\norm{g}$}
 
-To ensure that tables are correctly numbered automatically, the \verb"\label{}" command should be inserted just before \verb"\end{table}".
+First, we evaluate the integrand:
+\begin{align*}
+\abs{g(t)}^2 = \abs{g^*(t)}^2
+&=   \frac{\sqrt{R}^2}{\abs{R \cos t + \iu R \sin t + \iu C + i}^2} \\
+&=   \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} \\
+&= \frac{R}{R^2 \cos^2 t + R^2 \sin^2 t + (C + 1)^2  + 2 R (C + 1) \sin t} \\
+&=   \frac{1}{R + \frac{(C + 1)^2}{R} + 2 (C + 1) \sin t} \\ 
+\end{align*}
 
-Tables produced using the \texttt{booktabs} package of macros for typesetting tables are also compatible with the \textit{gCOV} class file.
+We have to integrate this function on interval $[0, 2 \pi]$. Integral of such type is well-known: % REFTODO
+\[
+\int\limits_{0}^{2 \pi} \frac{dx}{a + b \sin x} = \frac{2 \pi}{\sqrt{a^2 - b^2}}
+\]
+, when $a > b$. In our case, $a = R + \frac{(C + 1)^2}{R}$, $b = 2 (C + 1)$).
 
-\subsection{Landscape pages}\label{landscape}
+First, we check that $a > b$:
+\begin{align*}
+   R + \frac{(C + 1)^2}{R} - 2 (C + 1)
+   &= \frac{R^2 + C^2 + 2C + 1 - 2 RC - 2 R}{R}
+\\ &= \frac{(C - R)^2 + 2(C - R) + 1}{R}
+\\ &= \frac{(C - R + 1)^2 }{R}
+\\ &> 0 && \text{,strictly greater since $C > R$} 
+\end{align*}
 
-If a table or illustration is too wide to fit the measure it will need to be turned, along with its caption, through 90$^{\circ}$ anticlockwise.
-Landscape illustrations and/or tables can be produced using the \verb"rotating" package, which is called by the \textit{gCOV} class file.
-The following commands (for example) can be used to produce such pages.
-\begin{verbatim}
-\setcounter{figure}{0}
-\begin{sidewaysfigure}
-\centerline{\epsfbox{figname.eps}}
-\caption{Example landscape figure caption.}
-\label{landfig}
-\end{sidewaysfigure}
-\end{verbatim}
+Next, we compute en estimate for $\sqrt{a^2 - b^2}$:
+\begin{align*}
+a^2 - b^2
+& =  (R + \frac{(C + 1)^2}{R})^2 - (2 (C + 1))^2\\
+& =  R^2 + \frac{(C+1)^4}{R^2} + 2 (C+1)^2 - 4 (C + 1)^2 \\
+& =  \left( \frac{(C + 1)^2}{R} - R \right)^2 \\
+& =  \left( \frac{(C + 1)^2 - R^2}{R}\right)^2 \\
+& =  \left( \frac{(C + 1 - R) (C + 1 + R)}{R}\right)^2 && \text{,since $C > R > 0$} \\
+&\ge \left( \frac{(1) (R + R)}{R}\right)^2  \\
+&\ge 4
+\end{align*}
 
-\begin{verbatim}
-\setcounter{table}{0}
-\begin{sidewaystable}
- \tbl{Example landscape table caption.}
-  {\begin{tabular}{@{}llllcll}
-    .
-    .
-    .
-  \end{tabular}}\label{landtab}
-\end{sidewaystable}
-\end{verbatim}
-Before any such float environment, use the \verb"\setcounter" command as above to fix the numbering of the caption.
-Subsequent captions will then be automatically renumbered accordingly.
-The \verb"\epsfbox{}" command requires epsfig.sty, which is called by the \texttt{gCOV2e} class file and included with the \LaTeX\ style guide package for this journal for convenience.
+Finally, since $\frac{2 \pi}{\sqrt{a^2 - b^2}} \le \frac{2 \pi}{2} = \pi$, and we just proved that $\norm{g}$ is bounded by a constant.
 
-\subsection{Theorem-like environments}
+\subsection{Estimating $\norm{f}$}
+Function $s(k)$ (\ref{eq:bundle_s}) is too complex for direct proof of the convergence.
 
-A predefined \verb"proof" environment is provided by the \texttt{amsthm} package (which is called by the \textit{gCOV} class file), as follows:
+We proceed as follows:
 
-\begin{proof}
-More recent algorithms for solving the semidefinite programming
-relaxation are particularly efficient, because they explore the
-structure of the MAX-CUT problem.
-\end{proof}
-\noindent This was produced by simply typing:
-\begin{verbatim}
-\begin{proof}
-More recent algorithms for solving the semidefinite programming
-relaxation are particularly efficient, because they explore the
-structure of the MAX-CUT problem.
-\end{proof}
-\end{verbatim}
-Other theorem-like environments (theorem, lemma, corollary, etc.) need to be defined as required, e.g. using \verb"\newtheorem{theorem}{Theorem}[section]"
-in the preamble of your .tex file before \verb"\begin{document}". Theorem-like structures in \textit{gCOV} are generally numbered as per the following examples:
+\begin{itemize}
+\item Since $s(k)$ is an absolute value of the determinant of the $S$ matrix, in the upper complex plane $0 \le s(k) \le 1$ holds.
+From here, we immediately know that the integral is bounded from above since $ln^2 1 = 0$.
+\item We replace $s(k)$ with a lower bound $l(k)$ such that: $0 \le l(k) \le s(k) \le 1$.
+\item By appling logarithm to the expression above, we get $\ln l(k) \le \ln s(k) \le 0$, and therefore, $\ln^2 s(k) \le \ln^2 l(k)$.
+\item Now, if we prove convergence for $l(k)$, this immediately proves the convergence of the original integral.
+\end{itemize}
 
-\begin{theorem}
-More recent algorithms for solving the semidefinite programming
-relaxation are particularly efficient, because they explore the
-structure of the MAX-CUT problem.
-\end{theorem}
-\begin{lemma}
-More recent algorithms for solving the semidefinite programming
-relaxation are particularly efficient, because they explore the
-structure of the MAX-CUT problem.
-\end{lemma}
-\begin{corollary}
-More recent algorithms for solving the semidefinite programming
-relaxation are particularly efficient, because they explore the
-structure of the MAX-CUT problem.
-\end{corollary}
-\begin{proposition}
-More recent algorithms for solving the semidefinite programming
-relaxation are particularly efficient, because they explore the
-structure of the MAX-CUT problem.
-\end{proposition}
-\begin{definition}
-More recent algorithms for solving the semidefinite programming
-relaxation are particularly efficient, because they explore the
-structure of the MAX-CUT problem.
-\end{definition}
-\begin{remark}
-More recent algorithms for solving the semidefinite programming
-relaxation are particularly efficient, because they explore the
-structure of the MAX-CUT problem.
-\end{remark}
+We are going to use this fact in our proof and do such function changes under the integral sign, replacing complicated function with simpler (in particular, piecewise linear) lower bounds, and then using well known facts to estimate the integral.
 
-\noindent These were defined as shown in detail in the preamble of the \texttt{gCOVguide.tex} file, and produced by typing, for example:
-\begin{verbatim}
-\begin{theorem}
-More recent algorithms for solving the semidefinite programming
-relaxation are particularly efficient, because they explore the
-structure of the MAX-CUT problem.
-\end{theorem}
-\end{verbatim}
-The format of the text in these environments may be changed if necessary to match the style of the journal by the typesetter during preparation of your proofs.
+\subsubsection{Simplifying $s(k)$}
+We build a simple estimate for $s(k)$ over the upper complex plane. This function will be independent of the complex part of its argument which will make the analysis way easier.
 
-\subsection{Typesetting mathematics}\label{maths}
+\begin{enumerate}
+\item
+  It is easy to spot that if we fix the complex part of the argument, $s(k)$ is periodic with respect to the real part of its argument.
+\item 
+  Function $s(k)$ has countably infinite set of zeros, and each of them has $\Im k = \atanh \frac{2 W}{W^2 + 1}$. For brewity, we define:
 
-\subsubsection{Displayed mathematics}
+  \begin{equation*}
+  \begin{aligned}
+     V &= \frac{2 W}{W^2 + 1}
+  \\ Z &= \atanh V
+  \end{aligned}
+  \end{equation*}
+\item
+  Notice that for each $x$, $s(x + \iu y) \le s(\iu y)$.
+\end{enumerate}
 
-The \textit{gCOV} class file will set displayed mathematics centred on the measure without equation numbers if the \LaTeX\ standard commands open (\verb"\[") and close (\verb"\]") square brackets are used as
-delimiters. The equation
+Given these facts, we can build a simple lower bound for $s(x + \iu y)$:
+\begin{align*}
+l(x + \iu y)
+   &= \abs{\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}}
+\\ &= \abs{\frac{\tanh y - V}{\tanh y + V}} && \text{(since $\cosh y > 0$)}
+\end{align*}
+
+It's pretty clear that $l(k)$ has a continuum of zeros over the line $\Im k = Z$, which implies that $\ln l(k)$ has continuum number of singularities over this line.
+Intuitively, it shouldn't spoil the convergence of integral since the contour of integration cound intersect the singularities of the original function anyway.
+And indeed, we will give a rigorous argument that we still can prove convergence in this case.
+Since the function is independent from the real part of the argument now, for brewity, we will omit it and defince $l(y) = l(\iu y)$.
+
+Now, we will simplify the integral using the bound we just constructed:
+\begin{align*}
+       \int\limits_{t=0}^{2 \pi} \abs{f(t)}^2 dt
+   = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R \eexp{\iu t} + \iu C) \frac{R}{\norm{R \eexp{\iu t} + \iu C + i}^2} dt
+\\ = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R \sin t + C) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dt
+\end{align*}
+
+First, notice that:
+
+\begin{equation*}
+\begin{aligned}
+   \sin(-\pi/2 + t)   &= \sin(-\pi/2 - t) = - \cos t
+\\ \cos^2(-\pi/2 + t) &= \cos^2(-\pi/2 = t) = \sin^2 t
+\end{aligned}
+\end{equation*}
+, that is, the integrand is symmetric with respect to $y$ and for proving convergence it is enough to prove convergence on the (half circle) contour defined by $-\pi/2 \le t \le \pi/2$.
+
+Next, we do a variable change:
+\begin{equation*}
+\begin{aligned}
+   y         &= R \sin t + C
+\\ t         &= \asin \frac{y - C}{R}
+\\ dt        &= \frac{1}{\sqrt{R^2 - (C - y)^2}} dy
+\\ \cos t    &= \frac{\sqrt{R^2 - (C - y)^2}}{R}
+\\ y(-\pi/2) &= C - R 
+\\ y(\pi/2)  &= C + R 
+\end{aligned}
+\end{equation*}
+, and after substitution:
+\begin{equation}\label{eq:int_f}
+\resizebox{0.9\hsize}{!}{$
+\begin{aligned}
+    & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dy \\
+=   & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 - (C - y)^2 + (y + 1)^2} \frac{1}{\sqrt{R^2 - (C - y)^2}} dy\\
+=   & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}  dy\\
+\end{aligned}
+$}
+\end{equation}
+
+On the integration path we cross singularities at $y = C - R$, $y = Z$, $y = C + R$, and the integrand is still too complex for direct estimation.
+Let's split the integration path in multiple segments and estimate them independently.
+
+\subsubsection{Case 1: $C - R \le y \le Z$}
+A crucial property of $s(k)$ is its convergence to 1 as $\Im k$ goes to 0 (which is because $s$ is the determinant of S-matrix), since then $\ln s(k)$ goes to zero, which is necessary to compensate the singularity of $\frac{1}{R - C + y}$ at $y = C - R$.
+This means that to prove convergence using lower bound for $s(k)$, we have to require that $s(k)$ also converges to $1$ as $\Im k$ goes to $0$.
+
+% TODO plot?
+Since $l$ is convex when $0 \le y \le Z$, we can estimate it from below using its first derivative at $0$.
+However, this is not enough, since it will this will violate the property of the estimate being positive (it is under the logarithm sign), so we have to be more careful and approximate the function at $Z$ with its first derivative as well, and then glue them together at some point $Z_0$:
+\begin{align*}
+f(y)
+& = 
+\begin{cases}
+l'(0) y + 1   &, 0 \le y < Z_0  \\
+l'(Z) (y - Z) &, Z_0 \le y < Z \\
+\end{cases}
+\\
+& =
+\begin{cases}
+\frac{-2}{V} y + 1   &, 0 \le y < Z_0  \\
+\frac{1}{2 V}(V^2 - 1) (y - Z) &, Z_0 \le y < Z \\
+\end{cases}
+\end{align*}
+
+Note that lower bound does not have to be a continuous function, so we can pick any number in $[C - R, Z)$ as $Z_0$. For the ease of calculations, let's take $Z_0 = \frac{V}{4}$.
+
+Next we compute upper bounds for the integral \ref{eq:int_f} on $[C - R, \frac{V}{4})$ and $[\frac{V}{4}, Z)$ separately.
+
+\paragraph{$C - R \le y < \frac{V}{4}$}
+
+Note that for $C - R \le y \le \frac{V}{4}$:
+\begin{align*}
+       & \int \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
+\\ \le & \int \ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
+\end{align*}
+
+Now, we use a well known inequality which holds for $x > -1$: % REFTODO
 \[
-  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
-  i\in {\mathbb R}
+\frac{x}{1 + x} \le \ln (1 + x)
 \]
-\normalfont was typeset using the commands
-\begin{verbatim}
+, where in our case $x = -\frac{2}{V} y$. Since the expression under logarithm is less than 1, we get $\ln^2 (1 + x) \le \frac{x^2}{(1 + x)^2}$:
+\begin{align*}
+       & \dots 
+\\ \le & \int \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V}y)^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
+\\ \le & \int \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V} \frac{V}{4})^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
+\\ =   & \frac{\frac{4}{V^2}}{(1 - \frac{2}{V} \frac{V}{4})^2} \frac{R}{\sqrt{R + C - Z}}  \int \frac{y^2}{R^2 - C^2 + 2 (C + 1) y + 1}  \frac{1}{\sqrt{R - C + y}}
+\end{align*}
+
+It's clear that the multiplier before the integral has order $\mcO(\sqrt{R})$ (we can ignore the terms dependent on $V$ only since $V$ is a constant independent of $r$).
+
+The first part of the integrand has the form $\frac{y^2}{a + b y}$, where $a = R^2 - C^2 + 1, b = 2 (C + 1)$; when $R$ and $C$ are big enough, $a > 0$ and $b > 0$.
+That means $\frac{y^2}{a + b y}$ will be nonnegative when $y > 0$, and non decreasing, since:
 \[
-  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
-  i\in {\mathbb R}
+  \left(\frac{y^2}{a + b y}\right)'
+= \frac{2y}{a + by} + y^2 \frac{-b}{(a + by)^2}
+= \frac{2y (a + by) - b y^2}{(a + by)^2}
+= \frac{y (2a + by)}{(a + by)^2}
+\ge 0
 \]
-\end{verbatim}
 
-For those of your equations that you wish to be automatically numbered sequentially throughout the text,
-use the \texttt{equation} environment, e.g.
-\begin{equation}
-  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
-  i\in {\mathbb R}
+This implies that we can estimate the function from above by using its value on the rightmost point of the interval at $\frac{V}{4}$.
+\[
+\frac{y^2}{a + b y} \le \frac{\frac{V^2}{16}}{R^2 - C^2 + 1 + 2 (C + 1) \frac{V}{4}} = \mcO\left(\frac{1}{R}\right)
+\]
+
+Interal of the second part of the integrand is:
+\[
+\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} = 2 \sqrt{\frac{V}{4} - (C - R)} < 2 \sqrt{\frac{V}{4}} = \mcO(1)
+\]
+
+And finally, after combining we get $\mcO(\sqrt{R}) \mcO\left(\frac{1}{R}\right) \mcO(1)  = \mcO\left(\frac{1}{\sqrt{R}}\right)$.
+
+\paragraph{$\frac{V}{4} \le y < Z$}
+
+Note that for $\frac{V}{4} \le y < Z$:
+\begin{align*}
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}} 
+\\ \le & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}}
+\\ \le &  \frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}} \int \ln^2 \left( \frac{1}{2 V}(V^2 - 1) (y - Z) \right)
+\end{align*}
+
+First, take a look at the multiplier before the integral, it's pretty clear it has order of growth $\mcO(\frac{1}{\sqrt{R}})$.
+
+As for the integral, $\ln^2(x)$ is integrable in the neighborhood of $x = 0$, and it is known that: %  REFTODO
+
+\[
+\int\limits_{x=x_0}^b \ln^2(a (x - b)) dx = (b - x_0) (\ln^2(a (x_0 - b)) - 2 \ln(a (x_0 - b)) + 2)
+\]
+
+In our case $x_0 = \frac{V}{4}$, $a = \frac{1}{2 V}(V^2 - 1)$, $b = Z$, and we can see that the integral is bounded by a constant independent of $R$ and $C$, hence the integral on this interval grows as $\mcO(\frac{1}{\sqrt{R}})$.
+
+\subsubsection{Case 2: $y > Z$}
+When $y > Z$, 
+\[
+l(x + \iu y) 
+ = \frac{\tanh y - V}{\tanh y + V}
+ = 1 - 2 \frac{V}{\tanh y + V}
+\]
+
+Since $l$ is concave, strictly increasing and for a fixed $r$, we are only interested at $y \le C + R$, we can estimate the function by a linear one: 
+\[
+f(y) = \frac{l(C + R)}{C + R - Z} (y - Z)
+\]
+
+Notice that when $y = C + R$, for a sufficiently big $r$, $l(y)$ is bounded from both sides by constants, independent from $C$ and $R$.
+This is because $\tanh y$ goes to $1$ as $y$ goes to infinity, therefore, $l(y)$ in the limit will be equal to $1 - \frac{2 V}{V + 1}$.
+This is an important property of this specific model, since if $l$ went to zero on infinity, this part of proof couldn't have been done.
+
+First, note that on $Z \le y \le R + C$ the function $\frac{1}{\sqrt{R - C + y}}$ has no singularities and we can estimate integral \ref{eq:int_f} as:
+\begin{equation}\label{eq:int_f_up}
+\begin{aligned}
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
+\\ \le & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}} 
+\end{aligned}
 \end{equation}
-was typeset using the commands
-\begin{verbatim}
-\begin{equation}
-  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})quad
-  i\in {\mathbb R}
-\end{equation}
-\end{verbatim}
 
-Part numbers for sets of equations may be generated using the \texttt{subequations} environment, e.g.
-\begin{subequations} \label{subeqnexample}
-\begin{equation}
-        \varepsilon \rho w_{tt}(s,t)
-        =
-        N[w_{s}(s,t),w_{st}(s,t)]_{s},
-        \label{subeqnpart}
-\end{equation}
-\begin{equation}
-        w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
-\end{equation}
-\end{subequations}
-which was generated using the commands
-\begin{verbatim}
-\begin{subequations} \label{subeqnexample}
-\begin{equation}
-        \varepsilon \rho w_{tt}(s,t)
-        =
-        N[w_{s}(s,t),w_{st}(s,t)]_{s},
-        \label{subeqnpart}
-\end{equation}
-\begin{equation}
-        w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
-\end{equation}
-\end{subequations}
-\end{verbatim}
-This is made possible by the \texttt{subeqn} package, which is called
-by the class file. If you put the \verb"\label{}" just after the
-\verb"\begin{subequations}" line, references will be to the
-collection of equations, `(\ref{subeqnexample})' in the example
-above. Or, like the example code above, you can reference each
-equation individually -- e.g. `(\ref{subeqnpart})'.
+To estimate this expression, let's split the integration path in three intervals: $[Z, Z + \frac{1}{R})$, $[Z + \frac{1}{R}, C)$, $[C, C + R]$.
 
-Displayed mathematics should be given end-of-line punctuation appropriate to the running text sentence of which it forms a part, if required.
+\paragraph{$Z \le y < Z + \frac{1}{R}$}
 
-\subsubsection{Bold math italic symbols}
+Let's estimate \ref{eq:int_f_up}, replacing functions under the integral sign by their extreme value at interval's ends:
+\begin{align*}
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+\\ \le & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}}
+\\ =   & \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}} \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \int \ln^2 f(y) 
+\end{align*}
 
-To get bold math italic you can use \verb"\bm", which works for all sizes, e.g.
-\begin{verbatim}
-\sffamily
-\begin{equation}
-  {\rm d}({\bm s_{t_{\bm u}}) = \langle{\bm\alpha({\sf{\textbf L}})}
-  [RM({\bm X}_y + {\bm s}_t) - RM({\bm x}_y)]^2 \rangle
-\end{equation}
-\normalfont
-\end{verbatim}
-produces\sffamily
-\begin{equation}
-  {\rm d}({\bm s_{t_{\bm u}}}) = \langle {\bm\alpha({\sf{\textbf L}})}[RM({\bm X}_y
-  + {\bm s}_t) - RM({\bm x}_y)]^2 \rangle
-\end{equation}\normalfont
-Note that subscript, superscript, subscript to subscript, etc.
-sizes will take care of themselves and are italic, not bold,
-unless coded individually. \verb"\bm" produces the same effect as
-\verb"\boldmath". \verb"\sffamily"...\verb"\normalfont" allows
-upright sans serif fonts to be created in math mode by using the
-control sequence `\verb"\sf"'.
+It's easy to see that the coefficient before the integral has order of growth $\mcO\left(\frac{1}{\sqrt{R}}\right)$.
 
-\subsubsection{Bold Greek}\label{boldgreek}
+% REFTODO
+As for the integral $\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy$, it can be computed explicitly, using:
+\[
+    \int\limits_b^{b + c} \ln^2 (a (x - b)) dx = c (\ln^2(a c) - 2 \ln (a c) + 2)
+\]
 
-Bold lowercase as well as uppercase Greek characters can be
-obtained by \verb"{\bm \gamma}", which gives ${\bm \gamma}$, and
-\verb"{\bm \Gamma}", which gives ${\bm \Gamma}$.
+Hence, $\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy = \frac{1}{R} ( \ln^2 (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) - 2 \ln (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) + 2)$.
+As we noted above, $l(C + R)$ is bounded by positive constants less than $1$ and independent of $r$, and we can see that the expression grows as $\mcO(\frac{\ln^2 R}{R})$.
 
-\subsubsection{Upright lowercase Greek characters and the upright partial derivative sign}\label{upgreek}
+By combining the estimates for the coefficient and the integral, we get $\mcO(\frac{\ln^2 R}{R \sqrt{R}})$.
 
-Upright lowercase Greek characters can be obtained with the \textit{gCOV} class file by inserting the letter `u' in the control
-code for the character, e.g. \verb"\umu" and \verb"\upi" produce $\umu$ (used, for example, in the symbol for the
-unit microns -- $\umu{\rm m}$) and $\upi$ (the ratio of the circumference to the diameter of a circle). Similarly,
-the control code for the upright partial derivative $\upartial$ is \verb"\upartial".
+\paragraph{$Z + \frac{1}{R} \le y < C$}
+Again, by picking extreme values for the parts of integrands, we can estimate \ref{eq:int_f_up} as:
+\begin{align*}
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+\\ \le & \int \ln^2 f(Z + \frac{1}{R}) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - C}} \frac{1}{\sqrt{R - C + Z}}
+\\  =  & \ln^2 f(Z + \frac{1}{R})  \frac{R}{\sqrt{R + C - C}} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{R^2 - C^2 + 2 (C + 1) y + 1}
+\end{align*}
 
-\subsection{Acknowledgements}
+As $R$ goes to infinity, $\ln^2 f(Z + \frac{1}{R})$ goes to infinity as well, so we have to compute the order of singularity.
+Since $\ln f(Z + \frac{1}{R}) = \ln \left( \frac{l(C + R)}{C + R - Z} \frac{1}{R} \right) = \ln l(C + R) - \ln (C + R - Z) - \ln R$, we can see that $\ln^2 f(Z + \frac{1}{R}) = \mcO (\ln^2 R)$.
 
-An unnumbered section, e.g.\ \verb"\section*{Acknowledgement(s)}", should be used for thanks, etc.
-and included \emph{in the non-anonymous version} before any Notes or References section.
+As for the integral, antiderivative for such a function is well known:
+\[
+\int \frac{1}{a x + b} = \frac{\ln (a x + b)}{a}
+\]
+, in our case $a = 2 (C + 1)$, $b = R^2 - C^2 + 1$. Substituting the ends of the interval $(Z + \frac{1}{R}, C)$, we get the definite integral:
+\[
+\frac{\ln \frac{2 (C + 1) C + R^2 - C^2 + 1}{2 (C + 1) (Z + \frac{1}{R}) + R^2 - C^2 + 1}}{2 (C + 1)} = \mcO\left( \frac{\ln R}{R} \right)
+\]
 
-\subsection{Disclosure}
+Finally, after combining, we get: $\mcO (\ln^2 R) \frac{R}{\sqrt{R}} \frac{1}{\sqrt{R - C + Z}} \mcO\left( \frac{\ln R}{R} \right)  = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)$.
 
-An unnumbered section, e.g.\ \verb"\section*{Disclosure}", should be used to state any potential conflict of interest
-and included \emph{in the non-anonymous version} before the References section, after any Acknowledgements and before any Funding statement.
+\paragraph{$C \le y \le C + R$}
 
-\subsection{Funding}
+Again, estimating \ref{eq:int_f_up} from above:
+\begin{align*}
+       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+\\ \le & \int \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
+\\ =   & \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{\sqrt{R + C - y}}
+% \\  = & \ln^2 f(y) \mcO()
+\end{align*}
 
-An unnumbered section, e.g.\ \verb"\section*{Funding}", should be used for grant details, etc.
-and included \emph{in the non-anonymous version} before any Notes or References section.
+Integral $\frac{1}{\sqrt{R + C - y}}$ from $C$ to $C + R$ is elementary and equals $2 \sqrt{R}$.
+Function $f$ at $C$ is bounded by constants not dependent on $r$, therefore, the square of its logarithm as well.
+Finally, we get an expression of order $\mcO \left( \frac{1}{R} \right) \mcO( \sqrt R ) = \mcO \left( \frac{1}{\sqrt{R}} \right)$.
 
-\subsection{Notes}
+\subsubsection{Final estimate of $\int \abs{f(t)}^2$}
+We split our integration path in five intervals, and the integral has order:
+\[
+\mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) +\mcO\left(\frac{\ln^2 R}{R \sqrt{R}}\right) + \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)
+\]
+, which means that integral converges to $0$ as $r$ goes to $1$ and $R$ goes to $\infty$.
 
-An unnumbered `Notes' section may be placed before the References section (if using the \verb"endnotes" package, use the command \verb"\theendnotes" where the notes are to appear instead of creating a \verb"\section").
-
-\subsection{Supplemental material}
-
-Supplemental material should be referenced within your article where appropriate.
-An unnumbered section, e.g.
-\verb"\section*{Supplemental material}", detailing the supplemental material available should be placed immediately before the list of references, and should include a brief description of each supplemental file.
-
-\subsection{References}\label{refs}
-
-\subsubsection{References cited in the text}
-
-References should be cited in accordance with US National Library of Medicine (NLM) style (please refer to the style guide in the journal's Instructions for Authors for details).
-References are cited in the text by a number in square brackets (e.g.
-[1], [2,4,10], [11--15], not [11]--[15]), in the order in which they first appear.
-
-Each bibliographical entry has a key, which is assigned by the author and used to refer to that entry in the text. In this document, the key \verb"neu83" in the citation form
-\verb"\cite{neu83}" produces `\cite{neu83}', and the keys \verb"ed84" and \verb"aiex00" in the citation form
-\verb"\cite{ed84,aiex00}" produce `\cite{ed84,aiex00}'. The citation for a range of bibliographic entries (e.g.
-`\cite{Eri1984,glov00,hk97,glov86,Agu95,Holl04,Shak78,Mil93}') will automatically be produced by
-\verb"\cite{Eri1984,glov00,hk97,glov86,Agu95,Holl04,Shak78,Mil93}".
-Optional notes may be included at the end of a citation by the use of square brackets, e.g.
-\verb"\cite[see][p.73-–77]{cwm73}" produces `\cite[see][p.73--77]{cwm73}'.
-
-\subsubsection{The list of references}
-
-References should be listed at the end of the main text in the order in which they are first cited in the text. The following list shows some references prepared in the style of the journal.
+\section*{Acknowledgements}
+TODO ????
 
@@
 
-\bibitem{neu83}%1
-Neumann M. Parallel GRASP with path-relinking for job shop scheduling. Mol
-  Phys. 1983;50:841--843.
-
-\bibitem{ed84}%2
-Edwards DMF, McDonald IR. Positive bases in numerical optimization. Comput
-  Optim Appl. 1984;21:169--175.
-
-\bibitem{aiex00}%3
-Aiex RM, Pierce IF, Donizetti G, von~Weber CM, Bizet G, Bach CPE, Strauss
-  R, van~Beethoven L, Mozart WA, Dukas P. Computing tools for modelling
-  orchestral performance. Cambridge (UK): University of Cambridge; 2000.
-  Report No.: DAMTP 2000/NA10.
-
-\bibitem{Eri1984}%4
-Ericsson KA, Simon HA. Protocol analysis: verbal reports as data. Cambridge
-  (MA): MIT Press; 1984.
-
-\bibitem{glov00}%5
-Glover F. Multi-start and strategic oscillation methods -- principles to exploit
-  adaptive memory. In: Laguna M, Gonz\'{a}les-Velarde JL, editors. Computing
-  tools for modeling, optimization and simulation: interfaces in computer
-  science and operations research. 2nd ed. Vol.~2. Boston (MA): Kluwer Academic;
-  2000. p. 1--24.
-
-\bibitem{hk97}%6
-Kern H. The resurgent Japanese economy and a Japan--United States free
-  trade agreement. In: Lambert C, Holst G, editors. 4th International
-  Conference on the Restructuring of the Economic and Political System in Japan
-  and Europe; 1996 May 21--25; Milan, Italy. Singapore: World Scientific;
-  1997. p. 147--156.
-
-\bibitem{glov86}%7
-Glover F. Hilbert modular forms and the Galois representations associated to
-  Hilbert--Blumenthal abelian varieties [dissertation]. Cambridge (MA): Harvard
-  University; 1986.
-
-\bibitem{Agu95}%8
-Agutter AJ. The linguistic significance of current British slang [unpublished
-  doctoral dissertation]. Edinburgh (UK): Edinburgh University; 1995.
-
-\bibitem{Holl04}%9
-Holland M. Guide to citing internet sources. 2004~[cited~2012 Nov 4].
-  Available from: http://www.bournemouth.ac.uk/library/using/guide\_to\_citing\_internet\_sourc.html.
-
-\bibitem{Shak78}%10
-Shakelford RT. Surgery of the alimentary tract. Philadelphia (PA): W.B.
-Saunders; 1978. Chapter 2, Esophagoscopy; p. 29--40.
-
-\bibitem{Mil93}%11
-Miller ME. The interactive tester (version 4.0) [computer software].
-  Westminster (CA): Psytek Services; 1993.
-
-\bibitem{cwm73}%12
-Misner CW. Efficient algorithms for layer assignment problems. In: Gottlob I,
-  editor. Gravitation in a collapsing Universe. 2nd ed. San Francisco (CA):
-  Freeman; 1973. p. 63--83. (Einstein's legacy; vol.~5).
+\bibitem{nikol2012treatise}%1
+Nikol'skii N. Treatise on the shift operator: spectral function theory. Springer Science \& Business Media; 2012
 
 \end{thebibliography}
-\bigskip
-\noindent This was produced by typing:
-\begin{verbatim}
-\begin{thebibliography}{99}
-
-\bibitem{neu83}%1
-Neumann M. Parallel GRASP with path-relinking for job shop
- scheduling. Mol Phys. 1983;50:841--843.
-
-\bibitem{ed84}%2
-Edwards DMF, McDonald IR. Positive bases in numerical optimization.
- Comput Optim Appl. 1984;21:169--175.
-
-\bibitem{aiex00}%3
-Aiex RM, Pierce IF, Donizetti G, von~Weber CM, Bizet G, Bach CPE,
- Strauss R, van~Beethoven L, Mozart WA, Dukas P. Computing tools
- for modelling orchestral performance. Cambridge (UK): University
- of Cambridge; 2000. Report No.: DAMTP 2000/NA10.
-
-\bibitem{Eri1984}%4
-Ericsson KA, Simon HA. Protocol analysis: verbal reports as data.
- Cambridge (MA): MIT Press; 1984.
-
-\bibitem{glov00}%5
-Glover F. Multi-start and strategic oscillation methods -- principles
- to exploit adaptive memory. In: Laguna M, Gonz\'{a}les-Velarde JL,
- editors. Computing tools for modeling, optimization and simulation:
- interfaces in computer science and operations research. 2nd ed.
- Vol.~2. Boston (MA): Kluwer Academic; 2000. p. 1--24.
-
-\bibitem{hk97}%6
-Kern H. The resurgent Japanese economy and a Japan--United States
- free trade agreement. In: Lambert C, Holst G, editors. 4th
- International Conference on the Restructuring of the Economic
- and Political System in Japan and Europe; 1996 May 21--25;
- Milan, Italy. Singapore: World Scientific; 1997. p. 147--156.
-
-\bibitem{glov86}%7
-Glover F. Hilbert modular forms and the Galois representations
- associated to Hilbert--Blumenthal abelian varieties [dissertation].
- Cambridge (MA): Harvard University; 1986.
-
-\bibitem{Agu95}%8
-Agutter AJ. The linguistic significance of current British slang
- [unpublished doctoral dissertation]. Edinburgh (UK): Edinburgh
- University; 1995.
-
-\bibitem{Holl04}%9
-Holland M. Guide to citing internet sources. 2004 [cited~2012 Nov 4].
- Available from:
- http://www.bournemouth.ac.uk/library/using/guide\_to\_citing\_internet\_sourc.html.
-
-\bibitem{Shak78}%10
-Shakelford RT. Surgery of the alimentary tract. Philadelphia (PA):
- W.B. Saunders; 1978. Chapter 2, Esophagoscopy; p. 29--40.
-
-\bibitem{Mil93}%11
-Miller ME. The interactive tester (version 4.0) [computer software].
- Westminster (CA): Psytek Services; 1993.
-
-\bibitem{cwm73}%12
-Misner CW. Efficient algorithms for layer assignment problems. In:
- Gottlob I, editor. Gravitation in a collapsing Universe. 2nd ed.
- San Francisco (CA): Freeman; 1973. p. 63--83. (Einstein's legacy;
- vol.~5).
-
-\end{thebibliography}
-\end{verbatim}
-\bigskip
-\noindent Each entry takes the form:
-\begin{verbatim}
-\bibitem{key} Bibliography entry
-\end{verbatim}
-where `\texttt{key}' is the tag that is to be used as an argument for the \verb"\cite{}" commands in the text of the article and \texttt{Bibliography entry} is the material that is to appear in the list of references, suitably formatted.
-
-Instead of typing the bibliography by hand, you may prefer to create the list of references using a \textsc{Bib}\TeX\ database. Include the lines
-\begin{verbatim}
-\bibliographystyle{gCOV}
-\bibliography{gCOVguide}
-\end{verbatim}
-where the list of references should appear, where \texttt{gCOV.bst} is the name of the \textsc{Bib}\TeX\ style file for this journal and \texttt{gCOVguide.bib} is the database of bibliographic details for the references section included with the \textit{gCOV} \LaTeX\ style guide package (to be replaced with the name of your own \textsc{Bib}\TeX\ database).
-The \LaTeX\ source file of your paper will extract from your .bib file only those references that are cited in that paper and list them in the References section of it.
-
-Please include a copy of your .bib file and/or the final generated .bbl file among your source files if your .tex file does not contain a reference list in a \texttt{thebibliography} environment.
-
-\subsection{Appendices}\label{appendices}
-
-Any appendices should be placed after the list of references, beginning with the
-command \verb"\appendices" followed by the command \verb"\section"
-for each appendix title, e.g.
-\begin{verbatim}
-\appendices
-\section{This is the title of the first appendix}
-\section{This is the title of the second appendix}
-\end{verbatim}
-
-\noindent produces:\medskip
-
-\noindent\textbf{Appendix A. This is the title of the first appendix}\medskip
-
-\noindent\textbf{Appendix B. This is the title of the second appendix}\medskip
-
-\noindent Subsections, equations, figures, tables, etc. within
-appendices will then be automatically numbered as appropriate.
-
-\section{Example of a section heading including {\fontencoding{T1}\scshape{small caps}},
-   \textit{italic}, and bold Greek such as ${\bm\kappa}$}\label{headings}
-
-The following code shows how to achieve this section heading:
-\begin{verbatim}
-\section{Example of a section heading including
- {\fontencoding{T1}\scshape{small caps}}, \textit{italic},
- and bold Greek such as ${\bm\kappa}$}\label{headings}
-\end{verbatim}
-
-\section{\textit{gCOV} journal style}
-
-The notes given here relate to common style errors found in manuscripts, but are \emph{not}
-intended to be exhaustive.
-
-\subsection{Hyphens, en rules, em rules and minus signs}\label{dashes}
-
-\begin{enumerate}
-\item[(i)] Hyphens (one dash in \TeX/\LaTeX). \textit{gCOV} uses hyphens for compound adjectives (e.g.\ low-density gas, least-squares fit,
-two-component model) but not for complex units or ranges, which could become cumbersome (e.g.\ 15~km~s$^{-1}$
-feature, 100--200~$\umu$m observations).
-
-\item[(ii)] en rules (two dashes in \TeX/\LaTeX). These are used (a) to denote a range (e.g.\ 1.6--2.2~$\umu$m);
-(b) to denote the joining of two words of equal standing (e.g.\ Kolmogorov--Smirnov test, Herbig--Haro object);
-(c) with spaces, as an alternative to parentheses (e.g.\ `the results -- assuming no temperature gradient -- are indicative of \ldots').
-
-\item[(iii)] The em rule (three dashes in \TeX/\LaTeX) has no specified use in \textit{gCOV}.
-
-\item[(iv)] The minus sign is produced automatically in math mode by the use of a single dash, e.g.
-\begin{equation}
-y_{i} \in \{-1, 1 \} \quad \forall i \in V,
-\end{equation}
-\noindent where $|-V|=A^2+B^2.$\medskip
-
-\noindent is produced by
-\begin{verbatim}
-\begin{equation}
-y_{i} \in \{-1, 1 \} \quad \forall i \in V,
-\end{equation}
-\noindent where $|-V|=A^2+B^2.$
-\end{verbatim}
-
-\end{enumerate}
-
-\subsection{References}
-
-It is important to use the correct reference style, details of which can be found in Section~\ref{refs}.
-
-\subsection{Maths fonts}
-
-Scalar variables should be mediumface italic (e.g.\ $s$ for speed);
-vectors should be bold italic (e.g.\ $\bm v$ for velocity);
-matrices should be bold roman (upright) (e.g.\ $\bf A$), and
-tensors should be bold upright sans serif (e.g.\ {\sffamily{\textbf L}}).
-Differential d, partial differential $\upartial$, complex i,
-exponential e, superscript T for `transpose', sin, cos, tan, log, etc.,
-should all be roman. Openface, or `blackboard', fonts can be used,
-for example, for the integers $\mathbb Z$ and the reals $\mathbb R$.
-Sub/superscripts that are physical variables should be italic,
-while those that are labels should be roman (e.g.\ $C_p$, $T_{\rm eff}$).
-
-\section{Troubleshooting}
-
-Authors may from time to time encounter problems with the preparation
-of a paper using \LaTeX\/. The appropriate action to take will depend
-on the nature of the problem -- the following is intended as a guide.
-
-\begin{enumerate}
-\item[(i)] If the problem is with \LaTeX\ itself, rather than with the
-actual macros, please refer to an appropriate handbook for
-initial advice. If the solution cannot be found, or if you
-suspect that the problem lies with the macros, then please contact
-Taylor \& Francis for assistance (\texttt{latex.helpdesk@tandf.co.uk}).
-
-\item[(ii)] Problems with page make-up (e.g.\ large spaces between paragraphs,
-above headings, or below figures; figures/tables appearing out of order):
-please do not attempt to remedy these using `hard' page make-up
-commands -- the typesetter will deal with such problems. (You may, if you
-wish, draw attention to particular problems when submitting the final version
-of your paper.)
-
-\item[(iii)] If a required font is not available at your site, allow \TeX\
-to substitute the font and specify which font you require in a covering letter
-accompanying your file(s).
-\end{enumerate}
-
-\section{Fixes for coding problems}
-
-This guide has been designed to minimize the need for user-defined macros to create special symbols. Authors
-are urged, wherever possible, to use the following coding rather than to create their own. This will minimize
-the danger of author-defined macros being accidentally `overridden' when the paper is typeset (see
-Section~\ref{maths}, `Typesetting mathematics'). In cases where it is essential to create your own macros,
-these should be displayed in the preamble of your \texttt{.tex} file before \verb"\begin{document}".
-
-\begin{enumerate}
-\item[(i)] Fonts in section headings and paper titles. The following are examples
-of styles that sometimes prove difficult to code.
-
-\subsection*{Paper titles:}
-
-\hsize380pt\bf{\noindent Generalized Flory theory at ${\bm\delta >
-{\bf 50}^\circ}$}\\
-
-    \noindent\normalfont is produced by
-\begin{verbatim}
-\title{Generalized Flory theory at
-        ${\bm\delta > {\bfseries 50}^\circ}$}
-\end{verbatim}
-\bigskip
-
-{\bf{\noindent Ion--ion correlations in H\,{\sc ii} regions}}\\
-
-\noindent\normalfont is produced by
-\begin{verbatim}
-\title{Ion--ion correlations in H\,{\sc ii} regions}
-\end{verbatim}
-
-\stepcounter{enumi}
-
-\item[(ii)] en rules, em rules, hyphens and minus signs (see Section~\ref{dashes} for
-correct usage). To create the correct symbols in the sentence
-\begin{quote}
-The high-resolution observations were made along a line at an
-angle of $-15^\circ$ (East from North) from the axis of the
-jet -- which runs North--South
-\end{quote}
-you would use the following code:
-\begin{verbatim}
-The high-resolution observations were made along a line at an
-angle of $-15^\circ$ (East from North) from the axis of the
-jet -- which runs North--South
-\end{verbatim}
-
-\item[(iii)] Fonts in superscripts and subscripts. Subscripts and superscripts will automatically come out in the correct font
-and size in a math environment (e.g. enclosed by `\verb"$"'
-delimiters in running text or within \verb"\[...\]" or the
-`\texttt{equation}' environment for displayed equations). You can create
-the output ${\bm k_x}$ by typing \verb"${\bm k_x}$". If the
-subscripts or superscripts need to be other than italic, they
-should be coded individually -- see (vi) below.
-
-\item[(iv)] Calligraphic letters ($\mathcal{UPPER\ CASE\ ONLY}$).
-Normal calligraphic can be produced with \verb"\mathcal" as usual (in math mode).
-
-\item[(v)] Automatic scaling of brackets. The codes \verb"\left" and
-\verb"\right" should  be used to scale brackets automatically to
-fit the equation being set. For example, to get
-\[
-   v = x \left( \frac{N+2}{N} \right)
-\]
-use the code
-\begin{verbatim}
-\[
-   v = x \left( \frac{N+2}{N} \right)
-\]
-\end{verbatim}
-
-\item[(vi)] Roman font in equations. It is often necessary to make some
-symbols roman in an equation (e.g.\ units, non-variable subscripts).
-For example, to get
-\[
-   \sigma \simeq (r/13~h^{-1}~{\rm Mpc})^{-0.9},
-   \qquad \omega = \frac{N-N_{\rm s}}{N_{\rm R}}
-\]
-\noindent use the code
-\begin{verbatim}
-\[
-   \sigma \simeq (r/13~h^{-1}
-   ~{\rm Mpc})^{-0.9}, \qquad \omega
-   =\frac{N-N_{{\rm s}}}{N_{{\rm R}}}
-\]
-\end{verbatim}
-The \texttt{SIunits} package of macros for typesetting units is also compatible with the \texttt{gCOV2e} class file.
-\end{enumerate}
-
-\section{Obtaining the gCOV2e class file}\label{FTP}
-
-\subsection{Via the Taylor \& Francis website}
-
-This Guide for Authors and the \texttt{gCOV2e} class file may be obtained via the Instructions for Authors
-on the Taylor \& Francis homepage for the journal.
-
-Please note that the class file calls up the following open-source \LaTeX\ packages, which will, for convenience,
-unpack with the downloaded Guide for Authors and class file: amsbsy.sty; amsfonts.sty; amsmath.sty; amssymb.sty; epsfig.sty; graphicx.sty; natbib.sty; rotating.sty.
-The Guide for Authors calls for subfigure.sty, which is also supplied for convenience.
-
-\subsection{Via e-mail}
-
-This Guide for Authors, the class file and the associated open-source \LaTeX\ packages are also available by e-mail.
-Requests should be addressed to \texttt{latex.helpdesk@tandf.co.uk} clearly stating for which journal you require the Guide for Authors and/or class file.
-
 \end{document}

### 2016-12-22 cvee_paper_gerasimovd.tex
Minor fixes

@@
 \newcommand{\eexp}[1]{e^{#1}}  % convenient exponent
-\renewcommand{\Re}{\operatorname{Re}} % default Re/Im is weird
-\renewcommand{\Im}{\operatorname{Im}}
 \newcommand\abs[1]{\left|#1\right|}
@@
 \author{
-\name{A.N. Author\textsuperscript{a}$^{\ast}$\thanks{$^\ast$Corresponding author. Email: latex.helpdesk@tandf.co.uk}
+\name{D.A. Gerasimov\textsuperscript{a}$^{\ast}$\thanks{$^\ast$Corresponding author. Email: the.dmitrii.g@gmail.com}
 and I.T. Consultant\textsuperscript{b}}
@@
 Cayley transform maps $\mathbb{H}$ to $\mathbb{D}$:
-\begin{equation}\label{eq:cayley}
+\[
 W(z) = \frac{z - \iu}{z + \iu}
-\end{equation}
+\]
 , whereas inverse Cayley transform maps $\mathbb{D}$ to $\mathbb{H}$:
@@
 Another important property we are going to use is that Cayley transform preserves circles.
-In particular, a circle with radius $r < 1$ centered in zero, under inverse Cayley transform maps into a circle with center $\iu C(r)$ and radius $R(r)$, where:
+In particular, a circle with radius $0 < r < 1$ centered in zero, under inverse Cayley transform maps into a circle with center $\iu C(r)$ and radius $R(r)$, where:
 
@@
 \begin{aligned}
-   C(r) &= \Im \frac{w(r) + w(-r)}{2} = \frac{1 + r^2}{1 - r^2}
-\\ R(r) &= \Im \frac{w(r) - w(-r)}{2} = \frac{2 r}{1 - r^2}
+   C(r) &= \operatorname{Im} \frac{w(r) + w(-r)}{2} = \frac{1 + r^2}{1 - r^2}
+\\ R(r) &= \operatorname{Im} \frac{w(r) - w(-r)}{2} = \frac{2 r}{1 - r^2}
 \end{aligned}
@@
 
-From these formulas it's easy to see that if we limit $r$ to $1$, $R(r)$ goes to infinity and $C(r)$ converges to $R(r)$.
+From these formulas it's easy to see that as $r$ approaches $1$, $R(r)$ goes to infinity and $C(r)$ converges to $R(r)$.
 
-Also, we'll note two useful facts:
+Also, we'll note two useful facts: TODO REFERENCE HERE FROM TEXT
 \begin{itemize}
-\item $C(r) - R(r) > 0$
+\item $C(r) - R(r) = \frac{(1 - r)^2}{1 - r^2} > 0$
 \item $C(r) - R(r) = \frac{1 - r}{1 + r} < \frac{1}{R(r)} = \frac{1 - r^2}{2 r}$, which means that $C - R$ is $\mcO(\frac{1}{R})$
@@
 \end{equation}
-, where $C_r$ is an image of $\abs{\zeta} = r$ under the inverse Cayley transform.
+, where $C_r$ is an image of $\abs{\zeta} = r$ under the inverse Cayley transform (\ref{eq:cayley_inverse}).
 It can be parameterised as $C_r = \{R(r) \eexp{\iu t} + \iu C(r) \mid t \in [0, 2 \pi)\}$ (see \ref{eq:c_and_r}).
@@
 
-Let's investigate the model on Figure~\ref{fig:res_bundle}.
+Let's analyse the model on Figure~\ref{fig:res_bundle}.
 Schrodinger's operator is defined on the edges of the graph as  $-\frac{d^2 \psi}{dx^2}$.
@@
 \item 
-  Function $s(k)$ has countably infinite set of zeros, and each of them has $\Im k = \atanh \frac{2 W}{W^2 + 1}$. For brewity, we define:
+  Function $s(k)$ has countably infinite set of zeros, and each of them has $\operatorname{Im} k = \atanh \frac{2 W}{W^2 + 1}$. For brewity, we define:
 
@@
 
-It's pretty clear that $l(k)$ has a continuum of zeros over the line $\Im k = Z$, which implies that $\ln l(k)$ has continuum number of singularities over this line.
+It's pretty clear that $l(k)$ has a continuum of zeros over the line $\operatorname{Im} k = Z$, which implies that $\ln l(k)$ has continuum number of singularities over this line.
 Intuitively, it shouldn't spoil the convergence of integral since the contour of integration cound intersect the singularities of the original function anyway.
@@
 \subsubsection{Case 1: $C - R \le y \le Z$}
-A crucial property of $s(k)$ is its convergence to 1 as $\Im k$ goes to 0 (which is because $s$ is the determinant of S-matrix), since then $\ln s(k)$ goes to zero, which is necessary to compensate the singularity of $\frac{1}{R - C + y}$ at $y = C - R$.
-This means that to prove convergence using lower bound for $s(k)$, we have to require that $s(k)$ also converges to $1$ as $\Im k$ goes to $0$.
+A crucial property of $s(k)$ is its convergence to 1 as $\operatorname{Im} k$ goes to 0 (which is because $s$ is the determinant of S-matrix), since then $\ln s(k)$ goes to zero, which is necessary to compensate the singularity of $\frac{1}{R - C + y}$ at $y = C - R$.
+This means that to prove convergence using lower bound for $s(k)$, we have to require that $s(k)$ also converges to $1$ as $\operatorname{Im} k$ goes to $0$.
 

### 2016-12-22 cvee_paper_gerasimovd.tex
Fix typos

@@
 
-We will use the criterion (\ref{eq:blaschke}) to analyse the completeness of the system of resonant states. In the space of the unit disk it looks like:
+We will use the criterion (\ref{eq:blaschke}) to analyze the completeness of the system of resonant states. In the space of the unit disk it looks like:
 \begin{equation}\label{eq:crit_cayley}
@@
 
-Since S-matrix is naturally defined on the complex plance, it makes sense to use the upper complex plane for the analysis of completeness.
+Since S-matrix is naturally defined on the complex plane, it makes sense to use the upper complex plane for the analysis of completeness.
 We change the variable in (\ref{eq:crit_cayley}), applying Cayley transform to the integral, which results in:
@@
 
-Let's analyse the model on Figure~\ref{fig:res_bundle}.
+Let's analyze the model on Figure~\ref{fig:res_bundle}.
 Schrodinger's operator is defined on the edges of the graph as  $-\frac{d^2 \psi}{dx^2}$.
@@
 \item We replace $s(k)$ with a lower bound $l(k)$ such that: $0 \le l(k) \le s(k) \le 1$.
-\item By appling logarithm to the expression above, we get $\ln l(k) \le \ln s(k) \le 0$, and therefore, $\ln^2 s(k) \le \ln^2 l(k)$.
+\item By applying logarithm to the expression above, we get $\ln l(k) \le \ln s(k) \le 0$, and therefore, $\ln^2 s(k) \le \ln^2 l(k)$.
 \item Now, if we prove convergence for $l(k)$, this immediately proves the convergence of the original integral.
@@
 \item 
-  Function $s(k)$ has countably infinite set of zeros, and each of them has $\operatorname{Im} k = \atanh \frac{2 W}{W^2 + 1}$. For brewity, we define:
+  Function $s(k)$ has countably infinite set of zeros, and each of them has $\operatorname{Im} k = \atanh \frac{2 W}{W^2 + 1}$. For brevity, we define:
 
@@
 It's pretty clear that $l(k)$ has a continuum of zeros over the line $\operatorname{Im} k = Z$, which implies that $\ln l(k)$ has continuum number of singularities over this line.
-Intuitively, it shouldn't spoil the convergence of integral since the contour of integration cound intersect the singularities of the original function anyway.
+Intuitively, it shouldn't spoil the convergence of integral since the contour of integration could intersect the singularities of the original function anyway.
 And indeed, we will give a rigorous argument that we still can prove convergence in this case.
-Since the function is independent from the real part of the argument now, for brewity, we will omit it and defince $l(y) = l(\iu y)$.
+Since the function is independent from the real part of the argument now, for brevity, we will omit it and define $l(y) = l(\iu y)$.
 
@@
 The first part of the integrand has the form $\frac{y^2}{a + b y}$, where $a = R^2 - C^2 + 1, b = 2 (C + 1)$; when $R$ and $C$ are big enough, $a > 0$ and $b > 0$.
-That means $\frac{y^2}{a + b y}$ will be nonnegative when $y > 0$, and non decreasing, since:
+That means $\frac{y^2}{a + b y}$ will be non-negative when $y > 0$, and non decreasing, since:
 \[
@@
 
-Interal of the second part of the integrand is:
+Integral of the second part of the integrand is:
 \[

### 2016-12-22 cvee_paper_gerasimovd.tex
Less macros

@@
 
-\newcommand{\mcO}{\mathcal{O}} % Big O
-\newcommand{\iu}{{i\mkern1mu}} % imaginary unit
-\newcommand{\eexp}[1]{e^{#1}}  % convenient exponent
-\newcommand\abs[1]{\left|#1\right|}
-\newcommand\norm[1]{\left\|#1\right\|}
-\DeclareMathOperator\asin{asin}
-\DeclareMathOperator\atanh{atanh}
 \begin{document}
@@
 \begin{itemize}
-\item $\mathbb{C}$: complex plane, $\mathbb{C} = \{ x + \iu y \mid x, y \in \mathbb{R} \}$ 
-\item $\mathbb{H}$: upper complex half-plane, $\mathbb{H} = \{ x + \iu y \mid y > 0, x, y \in \mathbb{R} \}$
-\item $\mathbb{D}$: unit disk, $\mathbb{D} = \{ z \mid \abs{z} < 1 \}$
-\item $\mathbb{T}$: unit circle, $\mathbb{T} = \partial \mathbb{D} =  \{z \mid \abs{z} = 1 \}$
+\item $\mathbb{C}$: complex plane, $\mathbb{C} = \{ x + \mathrm{i} y \mid x, y \in \mathbb{R} \}$ 
+\item $\mathbb{H}$: upper complex half-plane, $\mathbb{H} = \{ x + \mathrm{i} y \mid y > 0, x, y \in \mathbb{R} \}$
+\item $\mathbb{D}$: unit disk, $\mathbb{D} = \{ z \mid \left|z\right| < 1 \}$
+\item $\mathbb{T}$: unit circle, $\mathbb{T} = \partial \mathbb{D} =  \{z \mid \left|z\right| = 1 \}$
 \item $z$ denotes a complex argument on complex plane $\mathbb{C}$
@@
 \[
-W(z) = \frac{z - \iu}{z + \iu}
+W(z) = \frac{z - \mathrm{i}}{z + \mathrm{i}}
 \]
@@
 \begin{equation}\label{eq:cayley_inverse}
-w(\zeta) = \iu \frac{1 + \zeta}{1 - \zeta}
+w(\zeta) = \mathrm{i} \frac{1 + \zeta}{1 - \zeta}
 \end{equation}
@@
 Another important property we are going to use is that Cayley transform preserves circles.
-In particular, a circle with radius $0 < r < 1$ centered in zero, under inverse Cayley transform maps into a circle with center $\iu C(r)$ and radius $R(r)$, where:
+In particular, a circle with radius $0 < r < 1$ centered in zero, under inverse Cayley transform maps into a circle with center $\mathrm{i} C(r)$ and radius $R(r)$, where:
 
@@
 \item $C(r) - R(r) = \frac{(1 - r)^2}{1 - r^2} > 0$
-\item $C(r) - R(r) = \frac{1 - r}{1 + r} < \frac{1}{R(r)} = \frac{1 - r^2}{2 r}$, which means that $C - R$ is $\mcO(\frac{1}{R})$
+\item $C(r) - R(r) = \frac{1 - r}{1 + r} < \frac{1}{R(r)} = \frac{1 - r^2}{2 r}$, which means that $C - R$ is $\mathcal{O}(\frac{1}{R})$
 \end{itemize}
@@
 \begin{aligned}
-   \psi_L(x) &= A \eexp{\iu k x} + B \eexp{-\iu k x}
-\\ \psi_R(x) &= C \eexp{\iu k x} + D \eexp{-\iu k x}
+   \psi_L(x) &= A e^{\mathrm{i} k x} + B e^{-\mathrm{i} k x}
+\\ \psi_R(x) &= C e^{\mathrm{i} k x} + D e^{-\mathrm{i} k x}
 \end{aligned}
@@
 \begin{equation}\label{eq:blaschke}
-\lim\limits_{r = 1} \int\limits_{\mathbb{T}} \log \abs{\det S(r \zeta)} d m(\zeta) = 0
+\lim\limits_{r = 1} \int\limits_{\mathbb{T}} \log \left|\det S(r \zeta)\right| d m(\zeta) = 0
 \end{equation}
@@
 \begin{equation}\label{eq:crit_cayley}
-\lim\limits_{r = 1} \int\limits_{\abs{\zeta} = r} \log \abs{\det S(\zeta)} d \zeta = 0
+\lim\limits_{r = 1} \int\limits_{\left|\zeta\right| = r} \log \left|\det S(\zeta)\right| d \zeta = 0
 \end{equation}
@@
 \begin{equation}\label{eq:crit}
-\lim\limits_{r \to 1} \int\limits_{C_r} \ln \abs{\det S(k)} \frac{2 \iu}{(k + i)^2} dk = 0
+\lim\limits_{r \to 1} \int\limits_{C_r} \ln \left|\det S(k)\right| \frac{2 \mathrm{i}}{(k + i)^2} dk = 0
 \end{equation}
-, where $C_r$ is an image of $\abs{\zeta} = r$ under the inverse Cayley transform (\ref{eq:cayley_inverse}).
-It can be parameterised as $C_r = \{R(r) \eexp{\iu t} + \iu C(r) \mid t \in [0, 2 \pi)\}$ (see \ref{eq:c_and_r}).
+, where $C_r$ is an image of $\left|\zeta\right| = r$ under the inverse Cayley transform (\ref{eq:cayley_inverse}).
+It can be parameterised as $C_r = \{R(r) e^{\mathrm{i} t} + \mathrm{i} C(r) \mid t \in [0, 2 \pi)\}$ (see \ref{eq:c_and_r}).
 For brevity, define:
@@
 \[
-s(k) = \abs{\det S(k)}
+s(k) = \left|\det S(k)\right|
 \]
@@
 \begin{equation}\label{eq:critp}
-\lim\limits_{r \to 1} \int\limits_{0}^{2 \pi} \ln s(R(r) \eexp{\iu t} + \iu C(r)) \frac{R}{(R(r) \eexp{\iu t} + \iu C(r) + i)^2} dt = 0
+\lim\limits_{r \to 1} \int\limits_{0}^{2 \pi} \ln s(R(r) e^{\mathrm{i} t} + \mathrm{i} C(r)) \frac{R}{(R(r) e^{\mathrm{i} t} + \mathrm{i} C(r) + i)^2} dt = 0
 \end{equation}
@@
 \begin{equation}\label{eq:bundle_s}
-s(k) = \abs{\det S(k)} = \abs{\frac{2 i \, W \cos\left(k\right) - {\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}}
+s(k) = \left|\det S(k)\right| = \left|\frac{2 i \, W \cos\left(k\right) - {\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}\right|
 \end{equation}
@@
 \[
-\abs{
+\left|
 \int\limits_{t=a}^{b} f(t) g^*(t) dt
-}
+\right|
 \le
-\sqrt{\int\limits_{t=a}^b \abs{f(t)}^2 dt }
-\sqrt{\int\limits_{t=a}^b \abs{g(t)}^2 dt }
+\sqrt{\int\limits_{t=a}^b \left|f(t)\right|^2 dt }
+\sqrt{\int\limits_{t=a}^b \left|g(t)\right|^2 dt }
 \]
@@
 b      &= 2 \pi \\
-f(t)   &= \ln s(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
-g^*(t) &= \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
+f(t)   &= \ln s(R e^{\mathrm{i} t} + \mathrm{i} C) \frac{\sqrt{R}}{R e^{\mathrm{i} t} + \mathrm{i} C + i} \\
+g^*(t) &= \frac{\sqrt{R}}{R e^{\mathrm{i} t} + \mathrm{i} C + i}
 \end{aligned}
 \end{equation}
-Next, we will show that $\norm{g}$ (that is, $\sqrt{\int \abs{g(t)}^2}$) is bounded by a constant which does not depend on $r$, and $\norm{f}$ goes to $0$ as $r$ goes to $1$, hence (\ref{eq:critp}) converges.
+Next, we will show that $\|g\|$ (that is, $\sqrt{\int \left|g(t)\right|^2}$) is bounded by a constant which does not depend on $r$, and $\|f\|$ goes to $0$ as $r$ goes to $1$, hence (\ref{eq:critp}) converges.
 
-\subsection{Estimating $\norm{g}$}
+\subsection{Estimating $\|g\|$}
 
@@
 \begin{align*}
-\abs{g(t)}^2 = \abs{g^*(t)}^2
-&=   \frac{\sqrt{R}^2}{\abs{R \cos t + \iu R \sin t + \iu C + i}^2} \\
+\left|g(t)\right|^2 = \left|g^*(t)\right|^2
+&=   \frac{\sqrt{R}^2}{\left|R \cos t + \mathrm{i} R \sin t + \mathrm{i} C + i\right|^2} \\
 &=   \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} \\
@@
 
-Finally, since $\frac{2 \pi}{\sqrt{a^2 - b^2}} \le \frac{2 \pi}{2} = \pi$, and we just proved that $\norm{g}$ is bounded by a constant.
+Finally, since $\frac{2 \pi}{\sqrt{a^2 - b^2}} \le \frac{2 \pi}{2} = \pi$, and we just proved that $\|g\|$ is bounded by a constant.
 
-\subsection{Estimating $\norm{f}$}
+\subsection{Estimating $\|f\|$}
 Function $s(k)$ (\ref{eq:bundle_s}) is too complex for direct proof of the convergence.
@@
 \item 
-  Function $s(k)$ has countably infinite set of zeros, and each of them has $\operatorname{Im} k = \atanh \frac{2 W}{W^2 + 1}$. For brevity, we define:
+  Function $s(k)$ has countably infinite set of zeros, and each of them has $\operatorname{Im} k = \operatorname{arctanh} \frac{2 W}{W^2 + 1}$. For brevity, we define:
 
@@
      V &= \frac{2 W}{W^2 + 1}
-  \\ Z &= \atanh V
+  \\ Z &= \operatorname{arctanh} V
   \end{aligned}
@@
 \item
-  Notice that for each $x$, $s(x + \iu y) \le s(\iu y)$.
+  Notice that for each $x$, $s(x + \mathrm{i} y) \le s(\mathrm{i} y)$.
 \end{enumerate}
 
-Given these facts, we can build a simple lower bound for $s(x + \iu y)$:
+Given these facts, we can build a simple lower bound for $s(x + \mathrm{i} y)$:
 \begin{align*}
-l(x + \iu y)
-   &= \abs{\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}}
-\\ &= \abs{\frac{\tanh y - V}{\tanh y + V}} && \text{(since $\cosh y > 0$)}
+l(x + \mathrm{i} y)
+   &= \left|\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}\right|
+\\ &= \left|\frac{\tanh y - V}{\tanh y + V}\right| && \text{(since $\cosh y > 0$)}
 \end{align*}
@@
 And indeed, we will give a rigorous argument that we still can prove convergence in this case.
-Since the function is independent from the real part of the argument now, for brevity, we will omit it and define $l(y) = l(\iu y)$.
+Since the function is independent from the real part of the argument now, for brevity, we will omit it and define $l(y) = l(\mathrm{i} y)$.
 
@@
 \begin{align*}
-       \int\limits_{t=0}^{2 \pi} \abs{f(t)}^2 dt
-   = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R \eexp{\iu t} + \iu C) \frac{R}{\norm{R \eexp{\iu t} + \iu C + i}^2} dt
+       \int\limits_{t=0}^{2 \pi} \left|f(t)\right|^2 dt
+   = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R e^{\mathrm{i} t} + \mathrm{i} C) \frac{R}{\|R e^{\mathrm{i} t} + \mathrm{i} C + i\|^2} dt
 \\ = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R \sin t + C) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dt
@@
    y         &= R \sin t + C
-\\ t         &= \asin \frac{y - C}{R}
+\\ t         &= \arcsin \frac{y - C}{R}
 \\ dt        &= \frac{1}{\sqrt{R^2 - (C - y)^2}} dy
@@
 
-It's clear that the multiplier before the integral has order $\mcO(\sqrt{R})$ (we can ignore the terms dependent on $V$ only since $V$ is a constant independent of $r$).
+It's clear that the multiplier before the integral has order $\mathcal{O}(\sqrt{R})$ (we can ignore the terms dependent on $V$ only since $V$ is a constant independent of $r$).
 
@@
 \[
-\frac{y^2}{a + b y} \le \frac{\frac{V^2}{16}}{R^2 - C^2 + 1 + 2 (C + 1) \frac{V}{4}} = \mcO\left(\frac{1}{R}\right)
+\frac{y^2}{a + b y} \le \frac{\frac{V^2}{16}}{R^2 - C^2 + 1 + 2 (C + 1) \frac{V}{4}} = \mathcal{O}\left(\frac{1}{R}\right)
 \]
@@
 \[
-\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} = 2 \sqrt{\frac{V}{4} - (C - R)} < 2 \sqrt{\frac{V}{4}} = \mcO(1)
+\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} = 2 \sqrt{\frac{V}{4} - (C - R)} < 2 \sqrt{\frac{V}{4}} = \mathcal{O}(1)
 \]
 
-And finally, after combining we get $\mcO(\sqrt{R}) \mcO\left(\frac{1}{R}\right) \mcO(1)  = \mcO\left(\frac{1}{\sqrt{R}}\right)$.
+And finally, after combining we get $\mathcal{O}(\sqrt{R}) \mathcal{O}\left(\frac{1}{R}\right) \mathcal{O}(1)  = \mathcal{O}\left(\frac{1}{\sqrt{R}}\right)$.
 
@@
 
-First, take a look at the multiplier before the integral, it's pretty clear it has order of growth $\mcO(\frac{1}{\sqrt{R}})$.
+First, take a look at the multiplier before the integral, it's pretty clear it has order of growth $\mathcal{O}(\frac{1}{\sqrt{R}})$.
 
@@
 
-In our case $x_0 = \frac{V}{4}$, $a = \frac{1}{2 V}(V^2 - 1)$, $b = Z$, and we can see that the integral is bounded by a constant independent of $R$ and $C$, hence the integral on this interval grows as $\mcO(\frac{1}{\sqrt{R}})$.
+In our case $x_0 = \frac{V}{4}$, $a = \frac{1}{2 V}(V^2 - 1)$, $b = Z$, and we can see that the integral is bounded by a constant independent of $R$ and $C$, hence the integral on this interval grows as $\mathcal{O}(\frac{1}{\sqrt{R}})$.
 
@@
 \[
-l(x + \iu y) 
+l(x + \mathrm{i} y) 
  = \frac{\tanh y - V}{\tanh y + V}
@@
 
-It's easy to see that the coefficient before the integral has order of growth $\mcO\left(\frac{1}{\sqrt{R}}\right)$.
+It's easy to see that the coefficient before the integral has order of growth $\mathcal{O}\left(\frac{1}{\sqrt{R}}\right)$.
 
@@
 Hence, $\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy = \frac{1}{R} ( \ln^2 (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) - 2 \ln (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) + 2)$.
-As we noted above, $l(C + R)$ is bounded by positive constants less than $1$ and independent of $r$, and we can see that the expression grows as $\mcO(\frac{\ln^2 R}{R})$.
+As we noted above, $l(C + R)$ is bounded by positive constants less than $1$ and independent of $r$, and we can see that the expression grows as $\mathcal{O}(\frac{\ln^2 R}{R})$.
 
-By combining the estimates for the coefficient and the integral, we get $\mcO(\frac{\ln^2 R}{R \sqrt{R}})$.
+By combining the estimates for the coefficient and the integral, we get $\mathcal{O}(\frac{\ln^2 R}{R \sqrt{R}})$.
 
@@
 As $R$ goes to infinity, $\ln^2 f(Z + \frac{1}{R})$ goes to infinity as well, so we have to compute the order of singularity.
-Since $\ln f(Z + \frac{1}{R}) = \ln \left( \frac{l(C + R)}{C + R - Z} \frac{1}{R} \right) = \ln l(C + R) - \ln (C + R - Z) - \ln R$, we can see that $\ln^2 f(Z + \frac{1}{R}) = \mcO (\ln^2 R)$.
+Since $\ln f(Z + \frac{1}{R}) = \ln \left( \frac{l(C + R)}{C + R - Z} \frac{1}{R} \right) = \ln l(C + R) - \ln (C + R - Z) - \ln R$, we can see that $\ln^2 f(Z + \frac{1}{R}) = \mathcal{O} (\ln^2 R)$.
 
@@
 \[
-\frac{\ln \frac{2 (C + 1) C + R^2 - C^2 + 1}{2 (C + 1) (Z + \frac{1}{R}) + R^2 - C^2 + 1}}{2 (C + 1)} = \mcO\left( \frac{\ln R}{R} \right)
+\frac{\ln \frac{2 (C + 1) C + R^2 - C^2 + 1}{2 (C + 1) (Z + \frac{1}{R}) + R^2 - C^2 + 1}}{2 (C + 1)} = \mathcal{O}\left( \frac{\ln R}{R} \right)
 \]
 
-Finally, after combining, we get: $\mcO (\ln^2 R) \frac{R}{\sqrt{R}} \frac{1}{\sqrt{R - C + Z}} \mcO\left( \frac{\ln R}{R} \right)  = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)$.
+Finally, after combining, we get: $\mathcal{O} (\ln^2 R) \frac{R}{\sqrt{R}} \frac{1}{\sqrt{R - C + Z}} \mathcal{O}\left( \frac{\ln R}{R} \right)  = \mathcal{O}\left( \frac{\ln^3 R}{\sqrt{R}} \right)$.
 
@@
 \\ =   & \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{\sqrt{R + C - y}}
-% \\  = & \ln^2 f(y) \mcO()
+% \\  = & \ln^2 f(y) \mathcal{O}()
 \end{align*}
@@
 Function $f$ at $C$ is bounded by constants not dependent on $r$, therefore, the square of its logarithm as well.
-Finally, we get an expression of order $\mcO \left( \frac{1}{R} \right) \mcO( \sqrt R ) = \mcO \left( \frac{1}{\sqrt{R}} \right)$.
+Finally, we get an expression of order $\mathcal{O} \left( \frac{1}{R} \right) \mathcal{O}( \sqrt R ) = \mathcal{O} \left( \frac{1}{\sqrt{R}} \right)$.
 
-\subsubsection{Final estimate of $\int \abs{f(t)}^2$}
+\subsubsection{Final estimate of $\int \left|f(t)\right|^2$}
 We split our integration path in five intervals, and the integral has order:
 \[
-\mcO \left( \frac{1}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) +\mcO\left(\frac{\ln^2 R}{R \sqrt{R}}\right) + \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right) + \mcO \left( \frac{1}{\sqrt{R}} \right) = \mcO\left( \frac{\ln^3 R}{\sqrt{R}} \right)
+\mathcal{O} \left( \frac{1}{\sqrt{R}} \right) + \mathcal{O} \left( \frac{1}{\sqrt{R}} \right) +\mathcal{O}\left(\frac{\ln^2 R}{R \sqrt{R}}\right) + \mathcal{O}\left( \frac{\ln^3 R}{\sqrt{R}} \right) + \mathcal{O} \left( \frac{1}{\sqrt{R}} \right) = \mathcal{O}\left( \frac{\ln^3 R}{\sqrt{R}} \right)
 \]

### 2016-12-22 cvee_paper_gerasimovd.tex
Appropriate references

@@
 
-Also, we'll note two useful facts: TODO REFERENCE HERE FROM TEXT
-\begin{itemize}
-\item $C(r) - R(r) = \frac{(1 - r)^2}{1 - r^2} > 0$
-\item $C(r) - R(r) = \frac{1 - r}{1 + r} < \frac{1}{R(r)} = \frac{1 - r^2}{2 r}$, which means that $C - R$ is $\mathcal{O}(\frac{1}{R})$
-\end{itemize}
+Also, we'll note two useful facts:
+\begin{subequations}
+\begin{equation}
+C(r) - R(r) = \frac{(1 - r)^2}{1 - r^2} > 0
+\label{eq:cr_positive}
+\end{equation}
+\begin{equation}
+C(r) - R(r) = \frac{1 - r}{1 + r} < \frac{1}{R(r)} = \frac{1 - r^2}{2 r} \implies C - R \text{\ is\ } \mathcal{O}\left(\frac{1}{R}\right)
+\label{eq:cr_small}
+\end{equation}
+\end{subequations}
 
@@
 Integral of the second part of the integrand is:
-\[
-\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} = 2 \sqrt{\frac{V}{4} - (C - R)} < 2 \sqrt{\frac{V}{4}} = \mathcal{O}(1)
-\]
+\begin{align*}
+\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} 
+   & = 2 \sqrt{\frac{V}{4} - (C - R)} 
+\\ & < 2 \sqrt{\frac{V}{4}} && \text{, since $C - R > 0$, see (\ref{eq:cr_positive})}
+\\ & = \mathcal{O}(1)
+\end{align*}
 
@@
 
-First, take a look at the multiplier before the integral, it's pretty clear it has order of growth $\mathcal{O}(\frac{1}{\sqrt{R}})$.
+First, take a look at the multiplier before the integral, using (\ref{eq:cr_small}) it is pretty clear it has order of growth $\mathcal{O}\left(\frac{1}{\sqrt{R}}\right)$.
 
@@
 
-It's easy to see that the coefficient before the integral has order of growth $\mathcal{O}\left(\frac{1}{\sqrt{R}}\right)$.
+Using (\ref{eq:cr_small}), it is easy to see that the coefficient before the integral has order of growth $\mathcal{O}\left(\frac{1}{\sqrt{R}}\right)$.
 
@@
 \\ =   & \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{\sqrt{R + C - y}}
-% \\  = & \ln^2 f(y) \mathcal{O}()
 \end{align*}
@@
 Integral $\frac{1}{\sqrt{R + C - y}}$ from $C$ to $C + R$ is elementary and equals $2 \sqrt{R}$.
-Function $f$ at $C$ is bounded by constants not dependent on $r$, therefore, the square of its logarithm as well.
+Function $f$ at $C$ is bounded by constants not dependent on $r$, therefore, the square of its logarithm is bounded as well.
 Finally, we get an expression of order $\mathcal{O} \left( \frac{1}{R} \right) \mathcal{O}( \sqrt R ) = \mathcal{O} \left( \frac{1}{\sqrt{R}} \right)$.
@@
 \subsubsection{Final estimate of $\int \left|f(t)\right|^2$}
-We split our integration path in five intervals, and the integral has order:
+We have split our integration path in five intervals, and the integral has order:
 \[

### 2016-12-22 cvee_paper_gerasimovd.tex
No need for index

@@
 \begin{classcode}F1.1; F4.3 \textbf{(... for example; authors are encouraged to provide two to six 2010 Mathematics Subject Classification codes)}\end{classcode}
-
-{\abstractfont\centerline{\bfseries Index to information contained in this guide}\vspace{12pt}
-\hbox to \textwidth{\hsize\textwidth\vbox{\hsize17pc
-\hspace*{-12pt} {1.}    Introduction\\
-\hspace*{7pt} {1.1.}  The \textit{gCOV} document class\\
-\hspace*{7pt} {1.2.}  Submission of \LaTeX\ articles\\
-\hspace*{24pt}        to the journal\\
-{2.}    Using the \textit{gCOV} class file\\
-{3.}    Additional features\\
-\hspace*{10pt}{3.1.}  Title, authors' names, abstract\\
-\hspace*{24pt}        and keywords\\
-\hspace*{10pt}{3.2.}  Additional footnotes to the\\
-\hspace*{24pt}        title or authors' names\\
-\hspace*{10pt}{3.3.}  Lists\\
-{4.}    Some guidelines for using\\
-\hspace*{6pt}        standard features\\
-\hspace*{10pt}{4.1.}  Sections\\
-\hspace*{10pt}{4.2.}  Illustrations (figures)\\
-\hspace*{10pt}{4.3.}  Tables\\
-\hspace*{10pt}{4.4.}  Landscape pages\\
-\hspace*{10pt}{4.5.}   Theorem-like environments\\
-\noindent \hspace*{7pt} {4.6.}   Typesetting mathematics\\
-\hspace*{24pt} {4.6.1.}  Displayed mathematics\\
-\hspace*{24pt} {4.6.2.}  Bold math italic symbols\\
-\hspace*{24pt} {4.6.3.}  Bold Greek\\
-\hspace*{24pt} {4.6.4.}  Upright Greek characters \\
-\hspace*{47pt}            and the upright partial \\
-\hspace*{47pt}            derivative sign }
-\hspace{-24pt}\vbox{\noindent\hsize17pc
-\hspace*{7pt} {4.7.}   Acknowledgements \\
-\hspace*{7pt} {4.8.}   Disclosure \\
-\hspace*{7pt} {4.9.}   Funding \\
-\hspace*{7pt} {4.10.}   Notes \\
-\hspace*{7pt} {4.11.}   Supplemental material \\
-\hspace*{7pt} {4.12.}   References \\
-\hspace*{24pt} {4.12.1.}  References cited in the \\
-\hspace*{52pt}            text\\
-\hspace*{24pt} {4.12.2.}  The list of references\\
-\hspace*{7pt} {4.13.}   Appendices \\
-{5.}    Example of a section heading \\*
-\hspace*{6pt}   including {\fontencoding{T1}\scshape{small caps}}, \textit{italic}, \\
-\hspace*{6pt}   and bold Greek such as ${\bm\kappa}$ \\
-{6.}    \textit{gCOV} journal style \\
-\hspace*{10pt}{6.1.}   Hyphens, en rules, em rules \\ \hspace*{27pt}and minus signs\\
-\hspace*{10pt}{6.2.}   References \\
-\hspace*{10pt}{6.3.}   Maths fonts\\
-{7.}    Troubleshooting\\
-{8.}    Fixes for coding problems\\
-{9.}    Obtaining the \texttt{gCOV2e} class file\\
-\hspace*{10pt}{9.1}  Via the Taylor \& Francis \\
-\hspace*{24pt}       website\\
-\hspace*{10pt}{9.2}  Via e-mail\\}}}
 
@@
 \\ &= \frac{(C - R + 1)^2 }{R}
-\\ &> 0 && \text{,strictly greater since $C > R$} 
+\\ &> 0 && \text{,\ strictly greater since $C > R$} 
 \end{align*}
@@
 & =  \left( \frac{(C + 1)^2 - R^2}{R}\right)^2 \\
-& =  \left( \frac{(C + 1 - R) (C + 1 + R)}{R}\right)^2 && \text{,since $C > R > 0$} \\
+& =  \left( \frac{(C + 1 - R) (C + 1 + R)}{R}\right)^2 && \text{,\ since $C > R > 0$} \\
 &\ge \left( \frac{(1) (R + R)}{R}\right)^2  \\
@@
    &= \left|\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}\right|
-\\ &= \left|\frac{\tanh y - V}{\tanh y + V}\right| && \text{(since $\cosh y > 0$)}
+\\ &= \left|\frac{\tanh y - V}{\tanh y + V}\right| && \text{,\ since $\cosh y > 0$}
 \end{align*}
@@
 
-First, note that on $Z \le y \le R + C$ the function $\frac{1}{\sqrt{R - C + y}}$ has no singularities and we can estimate integral \ref{eq:int_f} as:
+First, note that on $Z \le y \le R + C$ the function $\frac{1}{\sqrt{R - C + y}}$ has no singularities and we can estimate the integral (\ref{eq:int_f}) as:
 \begin{equation}\label{eq:int_f_up}
@@
 
-Let's estimate \ref{eq:int_f_up}, replacing functions under the integral sign by their extreme value at interval's ends:
+Let's estimate (\ref{eq:int_f_up}), replacing functions under the integral sign by their extreme value at interval's ends:
 \begin{align*}
@@
 \paragraph{$Z + \frac{1}{R} \le y < C$}
-Again, by picking extreme values for the parts of integrands, we can estimate \ref{eq:int_f_up} as:
+Again, by picking extreme values for the parts of integrands, we can estimate (\ref{eq:int_f_up}) as:
 \begin{align*}
@@
 
-Again, estimating \ref{eq:int_f_up} from above:
+Again, estimating (\ref{eq:int_f_up}) from above:
 \begin{align*}

### 2017-02-01 complet_wires_cvee1.tex
Paper from Popov

% gCOVguide.tex
% v4.0 released February 2015

\documentclass{gCOV2e}

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables

\theoremstyle{plain}% Theorem-like structures
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\begin{document}

%\jvol{00} \jnum{00} \jyear{2015} \jmonth{February}

%\articletype{GUIDE}

\title{\textit{Completeness of resonance states for quantum
graph with two semi-infinite edges}}

\author{
\name{D.A. Gerasimov\textsuperscript{a}\thanks{Email:
the.dmitrii.g@gmail.com} and
I.Y.Popov\textsuperscript{a}}\thanks{$^\ast$Corresponding author.
Email: popov1955@gmail.com} \affil{\textsuperscript{a}ITMO
University, Kronverkskiy, 49, Saint Petersburg, 197101, Russia}
\received{v4.0 released February 2015} }

\maketitle

\begin{abstract}
Scattering problem for quantum graph with two semi-infinite leads
is considered. Completeness of the system of resonance states in
$L_2$ on finite subgraph is proved. A relation with the
factorization of the characteristic function in Sz-Nagy functional
model is discussed.
\end{abstract}

\begin{keywords}
scattering; resonance; completeness; functional model
\end{keywords}

\begin{classcode}     81U20; 46N50 %\textbf{(... for example; authors are encouraged to provide two to six 2010 Mathematics Subject Classification codes)}
\end{classcode}

\section{Introduction}
\subsection{Model description}

The paper is devoted to investigation of resonance states for
scattering system. The problem of resonances is intensively
studied due to its importance for physical applications (see,
e.g., \cite{ELT,APV,DEM,E,EK,Ch} and references in \cite{Pav})
There is an interesting question concerning to the completeness of
the system of such states. An example of such problem is related
to scattering by bounded obstacle
\cite{BG,HM,Gad,P90,P92,PP93,PP93a}. First, let us consider
bounded resonator $\Omega$ with smooth boundary, i.e. the Neumann
or Dirichlet Laplacian in this domain. It has the discrete
spectrum and the system of it's eigenstates is complete in
$L_2(\Omega)$. Then, consider an analogous resonator coupled with
the outer space ${\mathbb R}^3\setminus\Omega$ through a small
window. In this case the spectrum changes drastically. The
discrete spectrum disappears, in general. More precisely,
eigenvalues converge to quasi-eigenvalues (resonances) and
eigenstates - to resonance states which are similar to eigenstates
(i.e. satisfy the equation ant the boundary conditions bur do not
belong to  $L_2(\Omega\cup ({\mathbb R}^3\setminus\Omega))$).
Nevertheless, restrictions of the resonance states on $\Omega$
belong to $L_2(\Omega)$, and one can pose a question: Is the
system of the resonance states complete in $L_2(\Omega)$? At
present, there is no general answer. Our hypothesis (see
\cite{PP17}) is that the maximal appropriate domain is the convex
hull of the scatterer. In the present paper we deal with a quantum
graph (see Fig. \ref{fig:res_bundle}) having some common features
with the scattering system described above. The role of resonator
$\Omega$ is played by a number of edges connected two vertices.
Quantum graphs with included resonators were considered in a few
papers (see, e.g., \cite{BG,GEIP,EIP}). Although the number of
works concerning to resonances is very large, the problem of
resonance states completeness were considered rarely
\cite{Sh,pops,VP}. We can mention a few works in which the problem
of resonance states completeness was not declared but, really, it
was investigated (see, e.g., \cite{AIR,AI,MAAE,MM} and references
therein). As for completeness of resonance states for quantum
graph, we do not no other works dealing with this problem.

\begin{figure}[htbp]
\begin{center}
\includegraphics[trim=0 670 155 0,clip,width=\textwidth]{resonator_bundle.eps}
\caption{Quantum graph $\Gamma$, consisting of semi infinite edges
$\Omega_L, \Omega_R$ and a resonator $\Omega$, consisting of $W$
identical edges of length 1.} \label{fig:res_bundle}
\end{center}
\end{figure}

The operator $H$ on the quantum graph $\Gamma$ is defined as
follows. Schr\"{o}dinger's operator is defined on the Sobolev
space $W_2^2$ on the edges of the graph and acts as  $-\frac{d^2
\psi}{dx^2}$. At the vertices $V_a$ and $V_b$ we require the
wavefunction to be continuous. As for its derivatives, the
Kirchhoff condition takes place:

\begin{equation}\label{eq:bundle_system}
\begin{aligned}
   \forall i: \psi_i(0) &= \psi_L(0)
\\ \forall i: \psi_i(1) &= \psi_R(0)
\\ \psi'_L(0) - \sum\limits_{i = 1}^W \psi'_i(0) &= 0
\\ -\psi'_R(0) + \sum\limits_{i = 1}^W \psi'_i(1) &= 0
\end{aligned}
\end{equation}

For our purposes, it is convenient to consider the scattering in
the framework of Lax-Phillips approach \cite{Lax,Lax1}. Let us
briefly describe the approach. Consider the Cauchy problem for the
wave equation
\begin{equation}
\label{1a} \left\{
\begin{array}{ll}
u''_{tt} = H u,  \\
u(x,0)= u_0(x), u'_t(x,0)= u_1(x), x \in \Gamma.
\end{array} \right.
\end{equation}

Let $\mathcal{E}$ be the Hilbert space of two-component functions
$(u_0,u_1)$ on the graph $\Gamma$ with finite energy
$$
\| (u_0,u_1) \|_{\mathcal{E}}^2 = 2^{-1}\int_{\Gamma} (|u'_0|^2 +
|u_1|^2)dx.
$$
The pair $(u_0,u_1)$ is called the Cauchy data. Operator giving
the solution for problem (\ref{1a}), $U(t)$, $U(t) (u_0,u_1) =
(u(x,t),u'_t(x,t))$, is unitary in $\mathcal{E}$. Unitary group
$U(t)|_{t \in \mathbb{R}}$ has two orthogonal (in $\mathcal{E}$)
subspaces, $D_-$ and $D_+$, called, correspondingly, incoming and
outgoing subspaces, which are defined as follows.

\begin{definition}. Outgoing subspace $D_+$ is a subspace of
$\mathcal{E}$ having the following properties:

(a) $U(t)D_+ \subset D_+$, $t>0$;

(b) $\cap_{t>0} U(t)D_+ =\{ 0 \}$,

(c) $\overline{\cup_{t<0} U(t)D_+} = \mathcal{E}$.

 $D_-$ is defined analogously (with the natural replacement $t>0
\leftrightarrow t<0$).
\end{definition}

The following three lemmas are analogous to the corresponding
lemmas in \cite{pops}.

\begin{lemma}. Unitary group $U(t)|_{t \in \mathbb{R}}$ has a
pair of subspaces $D_{\pm}$. Particularly, one can choose
$D_{\pm}$ by the following way:
$$
D_+ = \{(u_0,u_1): -u_1=u'_0, x \in \Omega_L; u_1=u'_0, x \in
\Omega_R; u_1=u_0=0, x \in \Omega \},
$$
$$
D_- = \{(u_0,u_1): u_1=u'_0, x \in \Omega_L; -u_1=u'_0, x \in
\Omega_R; u_1=u_0=0, x \in \Omega \}.
$$
\end{lemma}
For the proof, one should directly check properties a,b,c (see
\cite{PP17}).

\begin{lemma}. There is a pair of isometric maps $T_{\pm}: \mathcal{E} \rightarrow L_2(\mathbb{R},\mathbb{C}^2)$ having the following properties:
$$
T_{\pm} U(t) = \exp{ikt} T_{\pm}, \quad T_+ D_+ =
H^2_+(\mathbb{C}^2), \quad T_- D_- = H^2_-(\mathbb{C}^2),
$$
where $H^2_{\pm}$ is the Hardy space in upper (lower) half-plane.
\end{lemma}

It is said that $T_+(T_-)$ gives one the outgoing (incoming)
spectral representation of the unitary group $U(t), U(t) =
\exp{iAt}$. Let $K= \mathcal{E}\ominus(D_+\oplus D_-).$ Consider a
semigroup $Z(t)=P_K U(t)|_K, \quad t>0$, $P_K$  is a projector to
$K$. Let $B$ be the generator of the semigroup  $Z(t): Z(t) =
\exp{iBt}, t>0$. Data which are eigenvectors of $B$ are called
resonance states \cite{Lax}. Operator $T_-T_+^{-1}$ is called the
scattering operator. It acts as a multiplication by a
matrix-function $S(k)$ which is the boundary value at the real
axis of analytic matrix-function in the upper half-plane $k$ such
that $\| S(k) \| \leq 1$ for $\Im k > 0$ and $S^* S = I$ almost
everywhere on the real axis. This analytic matrix-function $S(k)$
is called the scattering matrix.

\begin{lemma}. Map $T_-$ gives one a spectral representation for
the unitary group $U(t)$. The following relations take place.
$$
T_-D_- = H^2_-(\mathbb{C}^2), \quad T_-D_+ = S
H^2_+(\mathbb{C}^2), \quad T_- U(t) = \exp{(ikt)}T_-.
$$
Matrix-function $S$ is an inner function in $\mathbb{C}_+$ and
$$
K_- = T_- K = H^2_+\ominus S H^2_+, \quad T_- Z(t)|_K = P_{K_-}
\exp{(ikt)}T_-.
$$
\end{lemma}

As an inner function, $S$ can be  represented in the form $S = \Pi
\Theta$, where $\Pi$ is the Blaschke-Potapov product and $\Theta$
is a singular inner function \cite{Sz-N,Nik,KNP,Peller,AA}. We are
interesting in the completeness of the system of resonant states.
It is related with the factorization of the scattering matrix.

\begin{theorem}[ (Completeness criterion), \cite{Nik},
Lecture 4]\label{Nik}. Let $S$ be an inner function, $H^2_+(N)
\ominus S H^2_+(N)$, $B=P_K A \vert _K$. The following statements
are equivalent:

1. Operator $B$ is complete;

2. Operator $B^*$ is complete;

3. $S$ is a Blaschke-Potapov  product.
\end{theorem}

Here $N$ is an auxiliary space (in our case it is $\mathbb{C}^2$).

To describe the situation in more details, we will give some
preliminary remarks. We will use the following notations.

\begin{itemize}
\item $\mathbb{C}$: complex plane, $\mathbb{C} = \{ x + \mathrm{i}
y \mid x, y \in \mathbb{R} \}$
\item $\mathbb{H}$: upper complex half-plane, $\mathbb{H} =
\{ x + \mathrm{i} y \mid y > 0, x, y \in \mathbb{R} \}$
\item $\mathbb{D}$: unit disk, $\mathbb{D} = \{ z \mid
\left|z\right| < 1 \}$
\item $\mathbb{T}$: unit circle, $\mathbb{T} = \partial \mathbb{D}
=  \{z \mid \left|z\right| = 1 \}$
\item $z$ denotes a complex argument on complex plane $\mathbb{C}$
\item $\zeta$ denotes a complex argument on unit disk $\mathbb{D}$
\end{itemize}

\subsection{Cayley transform}

Cayley transform maps $\mathbb{H}$ to $\mathbb{D}$:
\[
W(z) = \frac{z - \mathrm{i}}{z + \mathrm{i}},
\]
whereas inverse Cayley transform maps $\mathbb{D}$ to
$\mathbb{H}$:
\begin{equation}\label{eq:cayley_inverse}
w(\zeta) = \mathrm{i} \frac{1 + \zeta}{1 - \zeta}.
\end{equation}

One notable property of the Cayley transform  is that it
injectively maps $\mathbb{R}$ into unit circle $\mathbb{T}$.

Another important property  we are going to use is that Cayley
transform preserves circles. In particular, a circle of radius $r,
0 < r < 1$, centered at zero, under inverse Cayley transform maps
into a circle with center at point $\mathrm{i} C(r)$ and having
the radius $R(r)$, where:

\begin{equation}\label{eq:c_and_r}
\begin{aligned}
   C(r) &= \operatorname{Im} \frac{w(r) + w(-r)}{2} =
   \frac{1 + r^2}{1 - r^2},
\\ R(r) &= \operatorname{Im} \frac{w(r) - w(-r)}{2} =
\frac{2 r}{1 - r^2}.
\end{aligned}
\end{equation}

From these formulas,  it is easy to see that if $r$ approaches
$1$, then $R(r)$ goes to infinity and $C(r)$ converges to $R(r)$.

Also, we'll note two useful facts:
\begin{subequations}
\begin{equation}
C(r) - R(r) = \frac{(1 - r)^2}{1 - r^2} > 0,
\label{eq:cr_positive}
\end{equation}
\begin{equation}
C(r) - R(r) = \frac{1 - r}{1 + r} < \frac{1}{R(r)} = \frac{1 -
r^2}{2 r} \implies C - R \text{\ is\ }
\mathcal{O}\left(\frac{1}{R}\right).
\label{eq:cr_small}
\end{equation}
\end{subequations}

\subsection{S-matrix}\label{sec:smatrix}
Our quantum graph $\Gamma$ has two semi-infinite leads
$\Omega_L,\Omega_R$. To construct the scattering matrix, we
consider two scattering problems for plane waves coming from
$\Omega_L$ and $\Omega_R$, correspondingly:
\begin{equation}\label{eq:wlwl}
\begin{aligned}
   \psi_L(x) &= A e^{\mathrm{i} k x} + B e^{-\mathrm{i} k x}
\\ \psi_R(x) &= C e^{\mathrm{i} k x} + D e^{-\mathrm{i} k x}
\end{aligned}
\end{equation}
The scattering matrix relates the final and the initial states of
the system:
\begin{equation}\label{eq:smatrix}
\begin{pmatrix} B \\ C \end{pmatrix} = S \begin{pmatrix} A \\
D \end{pmatrix},
\end{equation}
and describes scattering properties of the obstacle. In our case
the obstacle is the subgraph $\Omega$. Given $A,D$, one obtains
$B,C$ by substitution of (\ref{eq:wlwl}) into the coupling
conditions at the graph vertices (\ref{eq:bundle_system}). It
gives us the S-matrix $S(k)$.

\subsection{Completeness criterion}
There is simple criterion for absence of the singular inner factor
for the case  $\dim  N < \infty$ (for general operator case there
is no simple criterion):

\begin{theorem}[\cite{Nik}, Lecture 4 ] Let $\dim  N < \infty$. The following
statements are equivalent:

1.  $S$ is a Blaschke-Potapov  product;

2. \begin{equation}\label{eq:crit} \lim\limits_{r \to 1}
\int\limits_{C_r} \ln \left|\det S(k)\right| \frac{2
\mathrm{i}}{(k + i)^2} dk = 0,
\end{equation}
where $C_r$ is an image of $\left|\zeta\right| = r$ under the
inverse Cayley transform (\ref{eq:cayley_inverse}).
\end{theorem}

The integration curve can be parameterized as $C_r = \{R(r)
e^{\mathrm{i} t} + \mathrm{i} C(r) \mid t \in [0, 2 \pi)\}$ (see
\ref{eq:c_and_r}). For brevity, define:
\[
s(k) = \left|\det S(k)\right|,
\]
and after throwing away constants which are irrelevant for
convergence, we get the final form of the criterion, which is
convenient for us and will be used afterwards:
\begin{equation}\label{eq:critp}
\lim\limits_{r \to 1} \int\limits_{0}^{2 \pi} \ln s(R(r)
e^{\mathrm{i} t} + \mathrm{i} C(r)) \frac{R}{(R(r) e^{\mathrm{i}
t} + \mathrm{i} C(r) + i)^2} dt = 0.
\end{equation}

After solving (\ref{eq:bundle_system}) in conjunction with
(\ref{eq:wlwl}), we get the S-matrix. The expression for $S(k)$ is
rather large. We will not present it here because in the following
consideration we need only its determinant which has essentially
more simple form:
\begin{equation}\label{det-s}
\det S(k) = \frac{2 i \, W \cos\left(k\right) -
{\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \,
W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}
\end{equation}

\begin{theorem}[Main theorem] The system of resonance states for
the operator $H$ is complete in $L_2(\Omega)$.
\end{theorem}

\section{Proof of the main theorem}

Using expression (\ref{det-s}), we get:
%
\begin{equation}\label{eq:bundle_s}
s(k) = \left|\det S(k)\right| = \left|\frac{2 i \, W
\cos\left(k\right) - {\left(W^{2} + 1\right)}
\sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} +
1\right)} \sin\left(k\right)}\right|.
\end{equation}
%
To prove completeness, we should show that the criterion
(\ref{eq:critp}) holds for this function. We will treat the
integral as a function of $R$ and give it an upper bound such that
it vanishes as $r \to 1$ and $R \to \infty$, which means that the
integral vanishes as well, hence the completeness of resonant
states takes place.

Now, let us fix $r$, and further, for the sake of readability, we
define $C = C(r)$ and $R = R(r)$. To estimate the integral, we use
Cauchy-Schwarz's inequality:
\[
\big| \langle u,v \rangle \big| \leq \left\|u\right\|
\left\|v\right\|,
\]
or to be precise, it's $\mathcal{L}^2[a, b]$ version:
\[
\left| \int\limits_{t=a}^{b} f(t) g^*(t) dt \right| \le
\sqrt{\int\limits_{t=a}^b \left|f(t)\right|^2 dt }
\sqrt{\int\limits_{t=a}^b \left|g(t)\right|^2 dt }.
\]
%
To use the inequality, we are going to represent the integrand in
(\ref{eq:critp}) as $f(t) g^*(t)$ as follows ($a = 0, b = 2 \pi$):
\begin{equation}\label{eq:split}
f(t)   = \ln s(R e^{\mathrm{i} t} + \mathrm{i} C)
\frac{\sqrt{R}}{R e^{\mathrm{i} t} + \mathrm{i} C + i},\quad
g^*(t) = \frac{\sqrt{R}}{R e^{\mathrm{i} t} + \mathrm{i} C + i}
\end{equation}
Next, we will show that $\|g\|$ (that is, $\sqrt{\int_0^{2\pi}
\left|g(t)\right|^2}$) is bounded by a constant which does not
depend on $r$, and $\|f\|$ goes to $0$ as $r$ goes to $1$, hence
(\ref{eq:critp}) tends to zero.

\subsection{Estimating of $\|g\|$}

First, we evaluate the integrand:
\begin{align*}
\left|g(t)\right|^2 = \left|g^*(t)\right|^2 =
\frac{\sqrt{R}^2}{\left|R \cos t + \mathrm{i} R \sin t +
\mathrm{i} C + i\right|^2}
&=   \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} \\
= \frac{R}{R^2 \cos^2 t + R^2 \sin^2 t + (C + 1)^2  + 2 R (C + 1)
\sin t}
&=   \frac{1}{R + \frac{(C + 1)^2}{R} + 2 (C + 1) \sin t} \\
\end{align*}
%
We integrate this function over interval $[0, 2 \pi]$. Integral of such type is well-known: % REFTODO
\[
\int\limits_{0}^{2 \pi} \frac{dx}{a_1 + a_2 \sin x} = \frac{2
\pi}{\sqrt{a_1^2 - a_2^2}},
\]
if $a_1 > a_2$. In our case, $a_1 = R + \frac{(C + 1)^2}{R}$, $a_2
= 2 (C + 1)$). First, we check that $a_1 > a_2$:
\begin{align*}
   R + \frac{(C + 1)^2}{R} - 2 (C + 1)
   &= \frac{R^2 + C^2 + 2C + 1 - 2 RC - 2 R}{R}
\\ = \frac{(C - R)^2 + 2(C - R) + 1}{R}
 &= \frac{(C - R + 1)^2 }{R}
> 0 \quad \text{,\ strictly greater since $C > R$}
\end{align*}
Next, we compute an estimate for $\sqrt{a_1^2 - a_2^2}$:
\begin{align*}
a_1^2 - a_2^2
 =  (R + \frac{(C + 1)^2}{R})^2 - (2 (C + 1))^2
& =  R^2 + \frac{(C+1)^4}{R^2} + 2 (C+1)^2 - 4 (C + 1)^2 \\
=  \left( \frac{(C + 1)^2}{R} - R \right)^2
& =  \left( \frac{(C + 1)^2 - R^2}{R}\right)^2 \\
=  \left( \frac{(C + 1 - R) (C + 1 + R)}{R}\right)^2 &\ge \left(
\frac{(1) (R + R)}{R}\right)^2  \ge 4 \quad \text{,\ since $C > R
> 0$}.
\end{align*}
Finally, since $\frac{2 \pi}{\sqrt{a_1^2 - a_2^2}} \le \frac{2
\pi}{2} = \pi$, we just proved that $\|g\|$ is bounded by a
constant.

\subsection{Estimating of $\|f\|$}
To proof the convergence, we will take into account the following
facts concerning to function $s(k)$ (\ref{eq:bundle_s}):

\begin{itemize}
\item Since $s(k)$ is an absolute value of the determinant of
the $S$ matrix, in the upper complex plane $0 \le s(k) \le 1$
holds. From here, we immediately know that the integral is bounded
from above since $ln^2 1 = 0$.
\item We replace $s(k)$ with a lower bound $l(k)$ such that:
$0 \le l(k) \le s(k) \le 1$.
\item By applying logarithm to the expression above, we get
$\ln l(k) \le \ln s(k) \le 0$, and therefore,
$\ln^2 s(k) \le \ln^2 l(k)$.
\item Now, if we prove convergence for $l(k)$, this immediately
proves the convergence of the original integral.
\end{itemize}

We are going to use this fact in our proof and do such function
changes under the integral sign, replacing complicated function
with simpler (in particular, piecewise linear) lower bounds, and
then using well known facts to estimate the integral.

\subsubsection{Simplifying of $s(k)$}

We build a simple estimate for $s(k)$ over the upper complex
plane. This function will be independent of the complex part of
its argument which will make the analysis way easier.

\begin{enumerate}
\item
  It is easy to spot that if we fix the complex part of the
  argument, $s(k)$ is periodic with respect to the real part of
  its argument.
\item
  Function $s(k)$ has countably infinite set of zeros, and each
  of them has $\operatorname{Im} k = \operatorname{arctanh}
  \frac{2 W}{W^2 + 1}$. For brevity, we define:
  \begin{equation*}
V = \frac{2 W}{W^2 + 1}, \quad Z = \operatorname{arctanh} V
  \end{equation*}
\item
  Notice that for each $x$, $s(x + \mathrm{i} y) \le
  s(\mathrm{i} y)$.
\end{enumerate}

Given these facts, we can build a simple lower bound for $s(x +
\mathrm{i} y)$:
$$
l(x + \mathrm{i} y) = \left|\frac{(W^2 + 1) \sinh y - 2 W \cosh
y}{(W^2 + 1) \sinh y + 2 W \cosh y}\right| = \left|\frac{\tanh y -
V}{\tanh y + V}\right|,
$$
since $\cosh y > 0$. It's pretty  clear that $l(k)$ has an
infinite number of zeros over the line $\operatorname{Im} k = Z$,
which implies that $\ln l(k)$ has an infinite number of
singularities over this line. Intuitively, it shouldn't spoil the
convergence of integral since the contour of integration could
intersect the singularities of the original function anyway. And
indeed, we will give a rigorous argument that we still can prove
convergence in this case. Since the function is independent from
the real part of the argument now, for brevity, we will omit it
and define $l(y) = l(\mathrm{i} y)$.

Now, we will simplify the integral  using the bound we just
constructed:
\begin{align*}
       \int\limits_{t=0}^{2 \pi} \left|f(t)\right|^2 dt
   = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R e^{\mathrm{i} t} +
   \mathrm{i} C) \frac{R}{\|R e^{\mathrm{i} t} +
   \mathrm{i} C + i\|^2} dt
\\ = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R \sin t + C)
\frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dt
\end{align*}
%
First, note that:
%
\begin{equation*}
\begin{aligned}
   \sin(-\pi/2 + t)   &= \sin(-\pi/2 - t) = - \cos t,
\\ \cos^2(-\pi/2 + t) &= \cos^2(-\pi/2 = t) = \sin^2 t,
\end{aligned}
\end{equation*}
that is, the integrand is symmetric with respect to $y$ and for
proving convergence, it is enough to prove convergence on the
(half circle) contour defined by $-\pi/2 \le t \le \pi/2$.

Next, we do a variable change:
\begin{equation*}
\begin{aligned}
   y         = R \sin t + C, \quad
t      = \arcsin \frac{y - C}{R}, \quad dt        &=
\frac{1}{\sqrt{R^2 - (C - y)^2}} dy,
\\ \cos t    = \frac{\sqrt{R^2 - (C - y)^2}}{R}, \quad
y(-\pi/2) = C - R, \quad y(\pi/2)  &= C + R.
\end{aligned}
\end{equation*}
After substitution, one has:
\begin{equation}\label{eq:int_f}
\resizebox{0.9\hsize}{!}{$
\begin{aligned}
    & \int\limits_{y = C - R}^{C + R} \ln^2 l(y)
    \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dy \\
=   & \int\limits_{y = C - R}^{C + R} \ln^2 l(y)
\frac{R}{R^2 - (C - y)^2 + (y + 1)^2} \frac{1}{\sqrt{R^2 -
(C - y)^2}} dy\\
=   & \int\limits_{y = C - R}^{C + R} \ln^2 l(y)
\frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}}
\frac{1}{\sqrt{R - C + y}}  dy\\
\end{aligned}
$}
\end{equation}

On the integration path  we cross singularities at $y = C - R$, $y
= Z$, $y = C + R$, and the integrand is still too complex for
direct estimation. Let's split the integration path in multiple
segments and estimate them independently.

\subsubsection{Case 1: $C - R \le y \le Z$}
A crucial property of $s(k)$ is  its convergence to 1 as
$\operatorname{Im} k$ goes to 0 (which is because $s$ is the
determinant of S-matrix), since then $\ln s(k)$ goes to zero,
which is necessary to compensate the singularity of $\frac{1}{R -
C + y}$ at $y = C - R$. This means that to prove convergence using
lower bound for $s(k)$, we have to require that $s(k)$ also
converges to $1$ as $\operatorname{Im} k$ goes to $0$.

% TODO plot?
Since $l$ is convex when $0 \le y \le Z$,  we can estimate it from
below using its first derivative at $0$. However, this is not
enough, since this will violate the property of the estimate being
positive (it is under the logarithm sign), so we have to be more
careful and approximate the function at $Z$ with its first
derivative as well, and then glue them together at some point
$Z_0$:
\begin{align*}
f(y)
& =
\begin{cases}
l'(0) y + 1   &, 0 \le y < Z_0  \\
l'(Z) (y - Z) &, Z_0 \le y < Z \\
\end{cases}
\\
& =
\begin{cases}
\frac{-2}{V} y + 1   &, 0 \le y < Z_0  \\
\frac{1}{2 V}(V^2 - 1) (y - Z) &, Z_0 \le y < Z \\
\end{cases}
\end{align*}

Note that the lower bound does not have to be a continuous
function, so we can pick any number in $[C - R, Z)$ as $Z_0$. For
the ease of calculations, let's take $Z_0 = \frac{V}{4}$.

Next, we compute upper bounds for the integral \ref{eq:int_f} on
$[C - R, \frac{V}{4})$ and $[\frac{V}{4}, Z)$ separately.

%\paragraph{$C - R \le y < \frac{V}{4}$}

Note that for $C - R \le y \le \frac{V}{4}$, one has:
\begin{align*}
     A  &= \int \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1}
       \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}dy
\\ \le & \int \ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 +
2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C +
y}}dy
\end{align*}

Now, we use a well known inequality which holds for $x > -1$:
\[
\frac{x}{1 + x} \le \ln (1 + x),
\]
where in our case $x = -\frac{2}{V} y$. Since the expression under
logarithm is less than 1, we get $\ln^2 (1 + x) \le \frac{x^2}{(1
+ x)^2}$:
\begin{align*}
       A \le & \int \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V}y)^2}
       \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R +
       C - Z}} \frac{1}{\sqrt{R - C + y}}dy
\\ \le & \int \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V}
\frac{V}{4})^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1}
\frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}dy
\\ =   & \frac{\frac{4}{V^2}}{(1 - \frac{2}{V} \frac{V}{4})^2}
\frac{R}{\sqrt{R + C - Z}}  \int \frac{y^2}{R^2 - C^2 + 2 (C + 1)
y + 1}  \frac{1}{\sqrt{R - C + y}}dy
\end{align*}

It's clear that the multiplier before the integral has order
$\mathcal{O}(\sqrt{R})$ (we can ignore the terms dependent on
$V$ only since $V$ is a constant independent of $r$).

The first part of the integrand has the form $\frac{y^2}{a + b
y}$, where $a = R^2 - C^2 + 1, b = 2 (C + 1)$; when $R$ and $C$
are large enough, $a > 0$ and $b > 0$. That means $\frac{y^2}{a +
b y}$ will be non-negative when $y > 0$, and non decreasing,
since:
\[
  \left(\frac{y^2}{a + b y}\right)'
= \frac{2y}{a + by} + y^2 \frac{-b}{(a + by)^2} = \frac{2y (a +
by) - b y^2}{(a + by)^2} = \frac{y (2a + by)}{(a + by)^2} \ge 0.
\]
This implies that we can estimate the function from above by using
its value on the rightmost point of the interval at $\frac{V}{4}$.
\[
\frac{y^2}{a + b y} \le \frac{\frac{V^2}{16}}{R^2 - C^2 + 1 + 2 (C
+ 1) \frac{V}{4}} = \mathcal{O}\left(\frac{1}{R}\right).
\]

Integral of the second part of the integrand is:
$$
\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}}dy
    = 2 \sqrt{\frac{V}{4} - (C - R)}
< 2 \sqrt{\frac{V}{4}}  = \mathcal{O}(1),
$$
since $C - R > 0$, see (\ref{eq:cr_positive}). Finally, after
combining, we get $\mathcal{O}(\sqrt{R})
\mathcal{O}\left(\frac{1}{R}\right) \mathcal{O}(1)  =
\mathcal{O}\left(\frac{1}{\sqrt{R}}\right)$.

%\paragraph{$\frac{V}{4} \le y < Z$}

Note that for $\frac{V}{4} \le y < Z$:
\begin{align*}
       & \int \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1}
       \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}dy
\\ \le & \int \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4}
+ 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C +
\frac{V}{4}}}dy
\\ \le &  \frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1}
\frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}}
\int \ln^2 \left( \frac{1}{2 V}(V^2 - 1) (y - Z) \right)dy.
\end{align*}

First, take a look  at the multiplier before the integral, using
(\ref{eq:cr_small}) it is pretty clear, it has order of growth
$\mathcal{O}\left(\frac{1}{\sqrt{R}}\right)$.

As for the integral, $\ln^2(x)$ is integrable in the neighborhood
of $x = 0$, and it is known that:
\[
\int\limits_{x=x_0}^b \ln^2(a (x - b)) dx = (b - x_0) (\ln^2(a
(x_0 - b)) - 2 \ln(a (x_0 - b)) + 2).
\]
In our case $x_0 = \frac{V}{4}$, $a = \frac{1}{2 V}(V^2 - 1)$, $b
= Z$, and we can see that the integral is bounded by a constant
independent of $R$ and $C$, hence, the integral on this interval
grows as $\mathcal{O}(\frac{1}{\sqrt{R}})$.

\subsubsection{Case 2: $y > Z$}
If $y > Z$ then
\[
l(x + \mathrm{i} y)
 = \frac{\tanh y - V}{\tanh y + V}
 = 1 - 2 \frac{V}{\tanh y + V}
\]
Since $l$ is concave, strictly increasing and for a fixed $r$, we
are only interested at $y \le C + R$, we can estimate the function
by a linear one:
\[
f(y) = \frac{l(C + R)}{C + R - Z} (y - Z)
\]
Note that when $y = C + R$, for a sufficiently big $r$, $l(y)$ is
bounded from both sides by constants, independent from $C$ and
$R$. This is because $\tanh y$ goes to $1$ as $y$ goes to
infinity, therefore, $l(y)$ in the limit will be equal to $1 -
\frac{2 V}{V + 1}$. This is an important property of this specific
model, since if $l$ went to zero at infinity, this part of the
proof couldn't have been done.

First, note that for $Z \le y \le R + C$ the function
$\frac{1}{\sqrt{R - C + y}}$ has no singularities, and we can
estimate the integral (\ref{eq:int_f}) as:
\begin{equation}\label{eq:int_f_up}
\begin{aligned}
       & \int \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1}
       \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}dy
\\ \le & \int \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1}
\frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}dy
\end{aligned}
\end{equation}

To estimate  this expression, let's split the integration path in
three intervals: $[Z, Z + \frac{1}{R})$, $[Z + \frac{1}{R}, C)$,
$[C, C + R]$.
%
%\paragraph{$Z \le y < Z + \frac{1}{R}$}

Consider the case $Z \le y < Z + \frac{1}{R}$.
%
Let's estimate (\ref{eq:int_f_up}), replacing functions  under the
integral sign by their extreme value at interval's ends:
\begin{align*}
       & \int \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1}
       \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}dy
\\ \le & \int \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1}
\frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C +
Z}}dy
\\ =   & \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}}
\frac{1}{\sqrt{R - C + Z}} \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1}
\int \ln^2 l(y)dy.
\end{align*}

Using (\ref{eq:cr_small}), it is easy to see  that the coefficient
before the integral has order of growth
$\mathcal{O}\left(\frac{1}{\sqrt{R}}\right)$.

As for the integral $\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 l(y)
dy$, it can be computed explicitly, using:
\[
    \int\limits_b^{b + c} \ln^2 (a (x - b)) dx = c (\ln^2(a c) - 2 \ln (a c) + 2)
\]
Hence,
$$
\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 l(y) dy = \frac{1}{R} (
\ln^2 (\frac{l(C + R)}{C + R - Z} \frac{1}{R}) - 2 \ln (\frac{l(C
+ R)}{C + R - Z} \frac{1}{R}) + 2).
$$
As we noted
above, $l(C + R)$ is bounded by positive constants less than $1$
and independent of $r$, and we can see that the expression grows
as $\mathcal{O}(\frac{\ln^2 R}{R})$.

By combining the estimates for the coefficient and the integral,
we get $\mathcal{O}(\frac{\ln^2 R}{R \sqrt{R}})$.

%\paragraph{$Z + \frac{1}{R} \le y < C$}
The next case is $Z + \frac{1}{R} \le y < C$.

Again, by picking extreme  values for the parts of integrands, we
can estimate (\ref{eq:int_f_up}) as:
\begin{align*}
       & \int \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1}
       \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}dy
\\ \le & \int \ln^2 l(Z + \frac{1}{R}) \frac{R}{R^2 - C^2 +
2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - C}} \frac{1}{\sqrt{R - C +
Z}}dy
\\  =  & \ln^2 l(Z + \frac{1}{R})  \frac{R}{\sqrt{R + C - C}}
\frac{1}{\sqrt{R - C + Z}} \int \frac{1}{R^2 - C^2 + 2 (C + 1) y +
1}dy
\end{align*}
As $R$ goes to infinity, $\ln^2 l(Z + \frac{1}{R})$ goes to
infinity as well, so we have to compute the order of singularity.
Since $\ln l(Z + \frac{1}{R}) = \ln \left( \frac{l(C + R)}{C + R -
Z} \frac{1}{R} \right) = \ln l(C + R) - \ln (C + R - Z) - \ln R$,
we can see that $\ln^2 l(Z + \frac{1}{R}) = \mathcal{O} (\ln^2
R)$.

As for the integral, it is well known that:
\[
\int \frac{1}{a x + b}dx = \frac{\ln (a x + b)}{a} +c.
\]
In our case $a = 2 (C + 1)$, $b = R^2 - C^2 + 1$. Substituting the
ends of the interval $(Z + \frac{1}{R}, C)$, we get the value of
our integral over interval $(Z + \frac{1}{R}, C)$:
\[
\frac{\ln \frac{2 (C + 1) C + R^2 - C^2 + 1}{2 (C + 1) (Z +
\frac{1}{R}) + R^2 - C^2 + 1}}{2 (C + 1)} = \mathcal{O}\left(
\frac{\ln R}{R} \right).
\]

Finally, after combining, we  get:
$$
\mathcal{O} (\ln^2 R) \frac{R}{\sqrt{R}} \frac{1}{\sqrt{R - C +
Z}} \mathcal{O}\left( \frac{\ln R}{R} \right)  = \mathcal{O}\left(
\frac{\ln^3 R}{\sqrt{R}} \right).
$$

%\paragraph{$C \le y \le C + R$}
The last case is $C \le y \le C + R$.

Again, estimating (\ref{eq:int_f_up}) from above, one obtains:
\begin{align*}
       & \int \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1}
       \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}dy
\\ \le & \int \ln^2 l(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1}
\frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}dy
\\ =   & \ln^2 l(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1}
\frac{1}{\sqrt{R - C + Z}} \int \frac{1}{\sqrt{R + C - y}}dy
\end{align*}

Integral of $\frac{1}{\sqrt{R + C - y}}$ from $C$ to $C + R$ is
elementary and equals $2 \sqrt{R}$. Function $f$ at $C$ is bounded
by constants not dependent on $r$, therefore, the square of its
logarithm is bounded as well. Finally, we get an expression of
order $\mathcal{O} \left( \frac{1}{R} \right) \mathcal{O}( \sqrt R
) = \mathcal{O} \left( \frac{1}{\sqrt{R}} \right)$.

\subsubsection{Final estimate of $\int_0^{2\pi} \left|f(t)\right|^2 dt$}
We have split our integration path in five intervals, and the
integral has the order:
\[
\mathcal{O} \left( \frac{1}{\sqrt{R}} \right) + \mathcal{O} \left(
\frac{1}{\sqrt{R}} \right) + \mathcal{O}\left(\frac{\ln^2 R}{R
\sqrt{R}}\right) + \mathcal{O}\left( \frac{\ln^3 R}{\sqrt{R}}
\right) + \mathcal{O} \left( \frac{1}{\sqrt{R}} \right) =
\mathcal{O}\left( \frac{\ln^3 R}{\sqrt{R}} \right),
\]
which means that the integral converges to $0$ as $r$ goes to $1$
and $R$ goes to $\infty$. Correspondingly, the proof of the main
theorem is complete.

\section*{Acknowledgements}

This work was partially financially supported by  the Government
of the Russian Federation (grant 074-U01), by grant MK-5161.2016.1
of the President of the Russian Federation, DFG Grant NE~1439/3-1,
by grant 16-11-10330 of Russian Science Foundation.

\begin{thebibliography}{99}

\bibitem{ELT} P. Exner, V. Lotoreichik, M. Tater On resonances and bound
states of Smilansky Hamiltonian. Nanosystems: Phys. Chem. Math.
{\bf 7} (2016), 789-802.

\bibitem{APV} A.Aslanyan, L.Parnovski and D.Vassiliev. Complex resonances
in acoustic waveguides. Q. J. Mech. Appl. Math. 53 (3) (2000),
429-447.

\bibitem{DEM} P.Duclos, P.Exner, B.Meller. Open quantum dots: Resonances
from perturbed symmetry and bound states in strong magnetic
fields. Rep. Math. Phys. 47 (2) (2001), 253-267.

\bibitem{E} J.Edward. On the resonances of the Laplacian on waveguides. J.
Math. Anal. Appl. 272 (1) (2002), 89-116.

\bibitem{EK} P.Exner, H.Kovarik. Quantum waveguides. Springer, Ber;in (2015).

\bibitem{Ch} T.Christiansen. Some upper bounds on the number of resonances
for manifolds with infinite cylindrical ends. Ann. Henri Poincare,
3 (2002), 895--920.

\bibitem{Pav} I.Y.Popov, P.A. Kurasov, S.N. Naboko, A.A. Kiselev,
A.E. Ryzhkov, A.M. Yafyasov, G.P. Miroshnichenko, Yu.E.
Karpeshina, V.I. Kruglov, T.F. Pankratova, A.I. Popov. A
distinguished mathematical physicist Boris S. Pavlov. Nanosystems:
Phys. Chem. Math. {\bf 7} (2016), 782--788.

\bibitem{HM}
 P.D.Hislop,  A.Martinez, Scattering  resonances of Helmholtz
resonator, Indiana Univ. Math. J. 40 (1991), 767--788.

\bibitem{Gad}
R.R.Gadyl'shin,  Existence and asymptotics  of poles with small
imaginary part for the Helmholtz resonator, Russian Mathematical
Surveys, 52 (1) (1997), 1--72.

\bibitem{P90}
I.Y.Popov,  Extension theory and localization of resonances for
domains of trap type,  Mathematics of the USSR-Sbornik, 71 (1)
(1992), 209--234. DOI: 10.1070/SM1992v071n01ABEH001394

\bibitem{P92}
 I.Y.Popov, The resonator with narrow slit and the model based on
the operator extensions theory, J. Math. Phys., 33 (11) (1992),
3794--3801.

\bibitem{PP93}
I.Y.Popov, S.L. Popova,  Zero-width slit model and resonances in
mesoscopic systems, Europhysics Letters, 24 (5) (1993), 373--377.

\bibitem{PP93a}
I.Y.Popov, S.L. Popova,  The extension theory and resonances for a
quantum waveguide, Physics Lett. A. 173 (1993), 484-- 488.

\bibitem{BG} J.~Bruning, V.~A.~Geyler, Scattering on compact manifold
with infinitely thin horns, J. Math. Phys. 44 (2003), 371--405.

\bibitem{PP17} I.Y.Popov, A.I.Popov. Line with attached segment as a model of
Helmholtz resonator: Resonant states completeness. Journal of King
Saud University – Science. {\bf 29} (2017), 133--136.

\bibitem{GEIP} E. N. Grishanov, D. A. Eremin, D. A. Ivanov,
and I. Yu. Popov. Dirac operator on the sphere with attached
wires. Chin. Phys. B  {\bf 25} (4) (2016), 047303/1-4.

\bibitem{EIP} D.A.Eremin,  D.A.Ivanov, I.Y.Popov. Model of
tunnelling through nanosphere in a magnetic field. Physica E, {\bf
44} (2012), 1598-1601.

\bibitem{Sh}
A.A.Shushkov.  Structure of resonances for symmetric scatterers.
Theor. Math. Phys. {\bf 64} (1985), 944 -- 949.

\bibitem{pops} I.Yu. Popov, A.V. Strepetov. On the completeness
of eigenfunctions for bilateral Regge problem. Leningrad Univ.
Vestnik. Mathematics. No 13 (1983), 25--31.

\bibitem{VP}
A.M.Vorobiev, I. Y.Popov,  2015.  Model of quantum dot and
resonant states for the Helmholtz resonator. J. Phys.: Conf.
Series. {\bf 643} (2015), 012097.

\bibitem{AIR} S. A. Avdonin, S. A. Ivanov, D. L. Russell,
Exponential bases in Sobolev spaces in control and observation
problems for the wave equation. Proc. Roy. Soc. Edinburgh Sect. A
{\bf 130} (2000), 947–-970.

\bibitem{AI} S. Avdonin, S. A. Ivanov. {\it Families of exponentials.
The method of moments in controllability problems for distributed
parameter systems}. Cambridge Univ. Press, Cambridge, 1995.

\bibitem{MAAE} F. Al-Musallam, S. Avdonin, N. Avdonina, J.
Edward. Control and inverse problems for networks of vibrating
strings with attached masses. Nanosystems: Phys. Chem. Math. {\bf
7} (2016), 835--841.

\bibitem{MM} A. S. Mikhaylov, V. S. Mikhaylov. Dynamical inverse
problem for the discrete Schr\"{o}dinger operator. Nanosystems:
Phys. Chem. Math. {\bf 7} (2016), 842--853.

\bibitem{Lax} P.D.Lax  and R.S.Phillips.  {\it Scattering theory}.
Academic Press, New York (1967)

\bibitem{Lax1} P.D.Lax  and R.S.Phillips.  {\it Scattering theory for
automorphic functions}. Princeton Univ. Press, Princeton, N. J.,
and Univ. of Tokyo Press, Tokyo (1976).

\bibitem{Sz-N} B.Sz.-Nagy, C.Foias, H.Bercovici, L.Kerchy.
{\it Harmonic Analysis of Operators on Hilbert Space}, 2nd
edition. Springer, Berlin (2010).

\bibitem{Nik}
N.Nikol'skii. {\it Treatise on the shift operator: spectral
function theory}. Springer Science \& Business Media; Berlin,
(2012).

\bibitem{KNP} S. V.Khrushchev, N.K.Nikol'skii, B.S.Pavlov.
Unconditional bases of exponentials and of reproducing kernels,
Complex Analysis and Spectral Theory (Leningrad, 1979/1980),
Lecture Notes in Math., vol. 864, Springer-Verlag, Berlin–New
York, 214–-335 (1981).

\bibitem{Peller} V. V.Peller. {\it Hankel Operators and Their Applications.
 Springer Monographs in Mathematics}. Springer-Verlag, New York (2003).

\bibitem{AA}  V.M.Adamyan ,  D.Z.Arov. On a class of scattering operators
and characteristic operator-functions of contractions. Dokl. Akad.
Nauk SSSR, {\bf 160} (1965), 9-12.

\end{thebibliography}
\end{document}

### 2017-02-01 complet_wires_cvee1.tex
Fixed typos

@@
 or Dirichlet Laplacian in this domain. It has the discrete
-spectrum and the system of it's eigenstates is complete in
+spectrum and the system of its eigenstates is complete in
 $L_2(\Omega)$. Then, consider an analogous resonator coupled with
@@
 eigenvalues converge to quasi-eigenvalues (resonances) and
-eigenstates - to resonance states which are similar to eigenstates
+eigenstates converge to resonance states which are similar to eigenstates
 (i.e. satisfy the equation ant the boundary conditions bur do not
@@
 Nevertheless, restrictions of the resonance states on $\Omega$
-belong to $L_2(\Omega)$, and one can pose a question: Is the
+belong to $L_2(\Omega)$, and one can pose a question: is the
 system of the resonance states complete in $L_2(\Omega)$? At
@@
 therein). As for completeness of resonance states for quantum
-graph, we do not no other works dealing with this problem.
+graph, we are not aware of other works dealing with this problem.
 
@@
 \]
-or to be precise, it's $\mathcal{L}^2[a, b]$ version:
+or to be precise, its $\mathcal{L}^2[a, b]$ version:
 \[
@@
 
-\subsection{Estimating of $\|g\|$}
+\subsection{Estimate of $\|g\|$}
 
@@
 
-\subsection{Estimating of $\|f\|$}
+\subsection{Estimate of $\|f\|$}
 To proof the convergence, we will take into account the following
@@
 
-\subsubsection{Simplifying of $s(k)$}
+\subsubsection{Simplifying $s(k)$}
 
-We build a simple estimate for $s(k)$ over the upper complex
-plane. This function will be independent of the complex part of
+We are going to build a simple estimate for $s(k)$ over the upper complex
+plane. This estimate will be independent of the complex part of
 its argument which will make the analysis way easier.
